### 2020-08-06 Manuscript/Conclusion.tex
add manuscript

\section*{Discussion and Conclusions}

A computationally efficient and highly parallelizable k-space domain pTx pulse design method was proposed.
The method adapts the k-space domain formulism proposed by Katscher et al \cite{katscher2003transmit}, which does not require the computationally expensive iterative processes in the conventional spatial domain design methods. The method advances the work of Katscher et al \cite{katscher2003transmit} by finely parallelizing the process of finding the system matrix. Furthermore, a technique inspired by a rapid GRAPPA calibration method \cite{luo2019grappa} is also included to further speed up the computation of each instance. The proposed k-space domain design method was evaluated through simulation upon an inner volume pulse design problem for MR Corticography, which can in turn enable submillimeter whole-cortex and cortex-specific imaging. The optimal parallelization parameters: thread number, patch width, and inclusion width, were found for this design problem. The proposed method reduced the computation time by 97\% compared to the conventional spatial domain design method, while producing equal inner volume suppression performance. And the abilities of the proposed method to accommodate k-space undersampling and correct off-resonance were also demonstrated to be equal to conventional spatial domain design method.

### 2020-08-06 Manuscript/Introduction.tex
add manuscript

\section* {Introduction}

\par Multidimensional RF pulses have been widely used in many applications such as reduced field-of-view imaging \cite{rieseberg2002two}, transmit field inhomogeneity correction \cite{saekho2005small}, and susceptibility artifacts correction \cite{stenger2000three}. Parallel transmission (pTx) \cite{katscher2003transmit,zhu2004parallel} further strengthens the multidimensional pulses by providing extra spatial encoding power, shortening pulse duration, and reducing  specific absorption rate (SAR). However, current multidimensional pTx pulse design methods are based on a spatial domain formulation \cite{Grissom:2006:MRM,setsompop2008magnitude} that has prohibitive memory and computational requirements when the number of coils and the number of dimensions both become larger in current designs. 
Particularly, current spatial domain design methods map any given RF pulse $\mathbf{b}$ to its spatial excitation pattern $\mathbf{d}$ with a large system matrix $\mathbf{A}$, as:
\begin{equation*}
	\mathbf{d}=\mathbf{Ab}
\end{equation*}
The size of $\mathbf{A}$ is $N_s$ by $N_cN_t$, where $N_s$ is the number of spatial locations, $N_c$ is the number of coils, and $N_t$ is the number of RF samples. Since $N_s$ becomes unbearably large in designs such as 2D plus spectral and 3D problems, and $N_c$ increases with more advance hardware designs, this $\mathbf{A}$ matrix is typically too large to find the inverse in terms of memory. Therefore, such design problems need to be solved by iterative conjugate-gradient (CG) methods which avoid matrix inversion. However, even if no matrix inversions are performed, the large system matrix may still be memory-inefficient when used in many matrix multiplications over a large number of iterations, making the solving process very slow. Furthermore, the NUFFT-based pulse design methods can also be slow due to all the gridding steps. Although these can be eliminated in NUFFT-based image reconstruction using Toeplitz formulation, in RF pulse design the Toeplitz formulation does not exist since the inner product is over space. 
These slow design methods are especially undesirable when tailored pulses are needed to be designed for each subject during one's examination in the scanner. Typically, the subject-tailored pulse design has to be done within one minute in the pre-scan stage, so that the incorporation of subject-tailored pulses into currently used workflow is practical and desirable.

\par One application of subject-tailored multidimensional pTx pulses that is of particular interest of this dissertation is the 3D inner volume suppression (IVS) pulses for MR Corticography (MRCoG).MRCoG is a developing imaging technique which aims for submillimeter isotropic resolution whole-cortex and cortex-specific imaging. 
It is a promising technique to enable whole-brain functional and diffusion studies of the columnar and laminar subcortical structures, which are the fundamentals of higher-order brain functions. 
%The current columnar and laminar fMRI methods all use a small field of view in order to achieve sub-millimeter resolution. This does not allow studies to be performed across the whole cerebral cortex. On the other hand, current whole brain fMRI methods typically have spatial resolution greater than 1 mm, which is not sufficient for the studies of columnar and laminar structures. 
MRCoG will use IVS to enable highly accelerated imaging of the cortex, by reducing g-factor and suppressing physiological noise from ventricle CSF. Therefore, subject-tailored IVS pTx pulses are needed, which could be applied before each excitation and readout. Thanks to the high performance gradient system an the 24-channel transmit system of the developing MRCoG scanner, good IVS with 3D selective excitation pulses becomes feasible. However, this IVS pulse design problem is challenging due to its 3D nature and the large number of transmit channels.

\par Here we propose a k-space-based approach to pTx pulse design that has low memory and computational requirements, and is highly parallelizable. Specifically, we build a sparse system matrix $\mathbf{W}$ that relates the Fourier transform of the spatial domain desired pattern and the desired RF pulse, so that the RF pulse can be instantaneously solved by a sparse matrix multiplication with no matrix inversion or iterative CG method. We advance the work by Katscher et al \cite{katscher2003transmit} by solving the columns of the system matrix in a parallelized fashion. This is done by utilizing the independence between columns of the system matrix which comes from the compactness of sensitivity maps in k-space. In the following text, we will derive the independent solution to each column and show a patch-wise parallelization that allows the control of the size and accuracy of each instance problem. We further accelerate the solution of each instance problem by proposing an efficient method to construct a key matrix needed while maintaining accuracy. Off-resonance correction is also incorporated into this k-space domain design. Then we apply this k-space domain design method to the 3D IVS pulse design problem, and demonstrate its striking acceleration to the computation speed by comparing its performance to the conventional spatial domain design method through simulations. We show how the computation speed and accuracy can be traded off through controlling the parameters of the patch-wise parallelization. We also demonstrate the k-space domain design's ability to accommodate excitation k-space undersampling and correct off-resonance.

### 2020-08-06 Manuscript/Method.tex
add manuscript

\section*{Methods}
RF pulses were designed for the 24-channel loop transmit array (Figure \ref{fig:Coil}) that will be built for the MRCoG scanner  and compressed to 16 channels using array compressed parallel transmission \cite{cao2016array}. $B_1^+$ maps used in the pulse design were simulated in a human head model using Ansys High Frequency Structure Simulator (Canonsburg, PA, USA) with 1.5 mm isotropic resolution. A SPINS  trajectory \cite{malik2012tailored} (Figure \ref{fig:Target}a\&b) with 5 mm max resolution was empirically designed for the pulse. The gradient duration was minimized to 10 ms through time-optimal design \cite{lustig2008fast} subject to the proposed MRCoG scanner’s gradient amplitude and slew rate constraints of 200 mT/m and 700T/m/s, respectively.

\begin{figure}
	\centering
	\includegraphics[width=3cm]{kspace_PTX_Coil}
	\caption{24-channel loop Tx array. The array has diameter 32 cm and height 28 cm. The 16 cm $times$ 11 cm loops are arranged in 3 rows of 8.}
	\label{fig:Coil}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{kSpace_PTX_Pattern_Trajectory}
	\caption{(a) Target excitation pattern for the IVS pulses. (b) 10 ms SPIN trajectory used in the designs. (c) Gradient waveforms of the excitation trajectory.}
	\label{fig:Target}
\end{figure}
Figure \ref{fig:Target}a shows the target pattern for the pulse design shaped as an ellipse centered on the ventricles with AP/HF/LR semi-axes of 4.8/3.2/3.2 cm. The target pattern was smoothed by a Fermi filter. Pulses were designed to excite the entire ellipse and achieve zero excitation in voxels in the cerebrum but outside the ellipse. Both the smoothed target pattern and the $B_1^+$ maps were undersampled from 128$\times$128$\times$96 grids (1.5mm iso-resolution) into 64$\times$64$\times$48 grids (3mm iso-resolution). The RF designs were done with the 64$\times$64$\times$48 grid size. The resulted pulses were evaluated against the target pattern with the 128$\times$128$\times$96 grid in order to expose Gibbs ringing. The normalized root-mean-square error (NRMS) was calculated against the voxels within the cerebrum.

With conventional spatial domain design, RF pulses were solved using an iterative least-squares conjugate-gradient decent method \cite{Grissom:2006:MRM}. With the proposed k-space domain design, RF pulses were solved with different parallelization parameters: thread number, patch width, and inclusion width. In order to study the computational acceleration provided by parallel computing, the design problem was solved with thread numbers ranging from 1 to 32, while the patch width and inclusion width were both set to 4. In order to study the computation time and error with respect to different patch widths and inclusion widths, we then held the computing threads constant at 16 while varying the patch and inclusion widths. The computation was done on a computer with a 512 GB RAM and two 24-core 2.1 GHz Intel Xeon CPUs which provides maximum 94 threads. For each design case, the computation was run 5 times, and the mean computation time and the NRMSE were recorded.

In order to demonstrate the k-space domain design’s robustness to Gibbs ringing, the target pattern and $B1^+$ maps were down-sampled into 32$\times$32$\times$24 (6mm iso-resolution)  and 64$\times$64$\times$48 grids (3mm iso-resolution). The outer sections of the excitation trajectory, equaling 2.1 ms, was excluded so that the maximum excitation resolution matched with the chosen 6 mm iso-resolution. All three designs were evaluated against the target pattern with the fully sampled 128$\times$128$\times$96 grid for validation.

The k-space domain design method's performance regarding k-space undersampling, which is desired for shorter pulse duration, was also examined and compared against the spatial domain design. The undersampling was achieved by reducing the numbers of the previously specified SPIN trajectory's polar and azimuthal rotations proportionally by a factor called acceleration factor, as shown in the third row of Figure \ref{fig:kspace_PTX_Acceleration}.

In order to show the k-space domain design method's ability to compensate moderate off-resonance and compare it against the spatial domain method. We incorporated a normalized field map with Gaussian inhomogeneity centered above the frontal sinus (Figure \ref{fig:kspace_PTX_B0}a), mimicking a characteristic susceptibility induced $B_0$ inhomogeneity. The field maps were than scaled so that the maximum off-resonance reached +100 Hz, +200 Hz, and +300 Hz. Off-resonance corrected spatial domain designs were done with system matrices whose field maps were also incorporated through time segmentation approximation \cite{fessler2005toeplitz}. k-space domain design were done with or without off-resonance correction.

### 2020-08-06 Manuscript/Result.tex
add manuscript

\section*{Results}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{kspace_PTX_ComputationTime}
	\caption{Studies of different parallelization parameters, where patch width is the square root of the number of $\mathbf{W}$ columns solved for simultaneously and inclusion width is the assumed range of influence of each excitation k-space location. \textbf{(a)} Computation time vs. thread numbers. Patch width and inclusion with were kept at 4 cycle/FOV. \textbf{(b\&c)} Computation time (blue axis) and NRMSE (red axis) vs. patch widths (b) and inclusion widths (c). Thread number were kept at 16 of for both design. Inclusion width was constant at 4 in (b) and patch widths were constant at 4 (solid line) and 8 (dashed line).}
	\label{fig:ComputationTime}
\end{figure}
Figure \ref{fig:ComputationTime}a shows the mean computation time versus different thread numbers. The k-space design problem held the patch and inclusion width constant at 4. The mean computation time decreases with increasing thread numbers before 12 threads, and then plateaus due to overhead. The thread number was conservatively chosen to be 16 for the following studies to ensure timely solutions. 
Figure \ref{fig:ComputationTime}b shows the mean computation time and the NRMSE with different patch widths. The computation time increases and the NRMSE decreases as the patch width increases. This was because when patch width increases, there are more excitation trajectory points included in one instance problem, even with the same inclusion width. As a result, each instance problem becomes bigger and more time consuming, which cancels the advantageous fact that there are fewer instance problems in total, especially in cases with parallel computing. Furthermore, increasing the patch width is equivalently increasing the inclusion widths for the center target points within each patch, which makes the solutions more accurate. Here, we chose patch widths 4 and 8 (labeled $2^2$ and $2^3$) to balance time and accuracy for further evaluation.
Figure \ref{fig:ComputationTime}c shows the mean computation time and the NRMSE with different inclusion widths. The solid lines and dashed lines were obtained with patch width 4 and 8, respectively. Computation time increases and error decreases with increasing inclusion width. Particularly, increasing inclusion width is equivalent to utilizing more accurate $B_1^+$ information by truncating the $B_1^+$ map Fourier transforms to zero further out from DC. For both patch widths 4 and 8, 4 is the optimal inclusion width, which confirms the result in \ref{fig:ComputationTime}a , previously. Using an inclusion width of 4, the computation time and error are acceptable for both patch width numbers. Following these results,  we chose patch width 4 for the further designs.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{kspace_PTX_ErrorMap2}
	\caption{Normalized excitation patterns (top row) and error maps (bottom row) for k-space domain design (left column) and spatial domain design (right column), with NRMSE and design time indicated.}
	\label{fig:ErrorMap}
\end{figure}
The normalized excitation patterns and error maps are shown in Fig \ref{fig:ErrorMap} for both k-space domain design (left) and spatial domain design (right), where the k-space domain design was solved with 16 parallel computing threads, patch width 4, and inclusion width 4. 
Both designs were done with the 64$\times$64$\times$48 grid size (3mm iso-resolution), and the excitation patterns were evaluated against the target pattern with the 128$\times$128$\times$96 grid size (1.5mm iso-resolution).  grid size. 
The calculated NRMSE from the k-space domain design and the spatial domain design were 5.02\% and 4.94\%, respectively, which were practically equal. For both design methods, most of the errors appeared at the edges of the transition band, with other errors lower than 5\% of the target flip angle. This indicates uniform inner volume suppression while maintaining the outer volume intact, which can in turn decrease g-factor in highly accelerated imaging. In practice, error near the transition band can be mitigated by ensuring the region of interest (ROI) of the cortex falls completely in the stop-band and assuming zero signal within the pass-band during undersampled reconstruction. More significantly, the parallelized k-space domain design method drastically reduced the mean computation time from 100.9 seconds to 2.9 seconds compared to the spatial domain design, which was a 97\% decrease.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{kspace_PTX_GibbsRinging}
	\caption{Normalized error maps and NRMSE for \textbf{(a)} spatial domain design and \textbf{(c)} k-space domain design with 6 mm iso-resolution, 32$\times$32$\times$24 design grid. Red arrows indicate the Gibbs ringing in low-resolution spatial domain design. \textbf{(b)} Normalized error map for spatial domain design with 3 mm iso-resolution, 64$\times$64$\times$48 design grid.}
	\label{fig:GibbsRing}
\end{figure}

Figure \ref{fig:GibbsRing}a\&c show the results of the  low-resolution designs using k-space domain method and the spatial domain method. The result of the high-resolution design of the spatial domain is also shown in Figure \ref{fig:GibbsRing}b. All three designed were done with a excitation trajectory that matches the 6 mm iso-resolution. The red arrows indicate the Gibbs ringing in the low-resolution spatial domain design, that can only be suppressed with high-resolution spatial domain design. However, the k-space domain design, although also low-resolution, is insensitive to this problem. Furthermore, the ripple pattern in the low resolution k-space design matches the high-resolution spatial design. Looking from a spatial domain point of view, the Gibbs ringing was caused by the lack of ability to observe the ringing with low-resolution. Looking from a k-space domain point of view, the Gibbs ringing was due to "wrap back" of the k-space FOV. When the spatial resolution is low the k-space FOV is small, and therefore the RF samples at one end of the trajectory can incorrectly "reach" and affect the k-space points at the other end of the k-space FOV in a circulation shift fashion. However, for the k-space domain design, even with low resolution, there is no k-space "wrap back" because the incorporated trajectory points are explicitly specified. Particularly, for the instance problems whose patches are at the edges of the k-space FOV, the excitation trajectory points at the other ends of the k-space FOV will not be incorporated into the design.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{kspace_PTX_Acceleration}
	\caption{ Normalized error maps and RMSE for spatial domain design (first row) and k-space domain design (second row), with excitation trajectories undersampled by different acceleration factors (third row).}
	\label{fig:kspace_PTX_Acceleration}
\end{figure}

Figure \ref{fig:kspace_PTX_Acceleration} shows a comparison between the performance of spatial domain design (first row) and k-space domain design (second row) regarding undersampled excitation trajectories (third row) with different acceleration factors. Both design methods had larger errors when the excitation k-space was less densely traversed. The k-space domain design provided similar error maps and practically equal NRMSE. The k-space domain design had slightly larger NRMSE because of the interpolation and truncation of the k-space sensitivity when building the $\mathbf{S}^{H}\mathbf{S}$ matrix, and can be improved by increasing the inclusion width.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{kspace_PTX_B0}
	\caption{\textbf{(a)} Normalized off-resonance map with Gaussian distortion centered above the frontal sinus, mimicking a characteristic susceptibility induced $B_0$ inhomogeneity. \textbf{(b)} Normalized excitation maps and RMSE for spatial domain design with off-resonance correction (first row), k-space domain design with and without off-resonance correction (second \& third rows).}
	\label{fig:kspace_PTX_B0}
\end{figure}

Regarding 3D off-resonance patterns with the shape shown in Figure \ref{fig:kspace_PTX_B0}a and different scaling, Figure \ref{fig:kspace_PTX_B0}b shows the excitation maps of three types of designs: spatial domain design with off-resonance correction (first row), k-space domain design with and without off-resonance correction (second \& third row). As shown in the second row of Figure \ref{fig:kspace_PTX_B0}b, off-resonance caused false excitation outside the designated suppression region, and must be corrected. k-space domain design with correction was able to correct off-resonance artifacts and provide excitation patterns comparable to spatial domain design, for maximum off-resonance up to 200 Hz, which is the typical range of off-resonance observed in clinical studies. The k-space domain design has a weaker performance with higher off-resonance due to the fact that the time segmentation approximation in Ref \cite{fessler2005toeplitz} was meant to approximate forward models from RF to excitation patterns and does not serve as an accurate approximation to the backward model as we need in the k-space domain design.

### 2020-08-06 Manuscript/Theory.tex
add manuscript

\section*{Theory}

\subsection*{k-space domain parallel-transmit pulse design}
\par Here we describe the derivation of the highly parallelizable k-sapce domain design method. We propose to find a system matrix $\mathbf{W}$ that directly maps a desired excitation pattern in k-space $\mathcal{F}(\mathbf{d})$, which is the Fourier transform of the spatial domain desired pattern $\mathbf{d}$, to the corresponding desired RF pulse $\mathbf{b}$, as:
\begin{equation*}
\mathbf{b}=\mathbf{W}\mathcal{F}(\mathbf{d})
\end{equation*}
$\mathcal{F}(\mathbf{d})$ is the vectorized k-space excitation pattern with length of $N_s$, which is the number of spatial/k-space locations.  $\mathbf{b}$ is the concatenated multi-channel RF samples with length of $N_tN_c$, where $N_t$ and $N_c$ are the numbers of time points and coils, respectively. $\mathbf{W}$ is the $N_tN_c$ by $N_s$ system matrix, which will latter be shown sparse.
Therefore, once the $\mathbf{W}$ matrix is found, the RF design problem can be instantaneously solved by a sparse matrix multiplication, and there is no matrix inversion or iterative CG method needed. Furthermore, in design problems involved iterative procedures, such as the phase updates in magnitude-least-squares pulse designs \cite{setsompop2008magnitude} and the regularization factor updates in power/roughness constrained pulse design, the sparsity of the $\mathbf{W}$ matrix makes the iterative process much more efficient in terms of memory and speed. In the work of Katscher et al \cite{katscher2003transmit}, parallel transmit pulse design was also formulated in the k-space domain. However, in Ref \cite{katscher2003transmit}, the matrix $\mathbf{W}$ was solved as a whole, which required constructing and inverting a large $\mathbf{S}^H\mathbf{S}$ matrix, which will be explained in the following text. Our proposed method finely divides the process of finding $\mathbf{W}$ into many independent instances, which allows the use of parallel computing to largely accelerate the computation. Furthermore, the $\mathbf{S}^H\mathbf{S}$ matrices of different instances are each small, and our proposed method efficiently constructs these matrices, which further accelerates the computation.

\par We can solve for the columns of the $\mathbf{W}$ matrix independently to each other, based on the key observation that if the desired k-space pattern is a delta function at a given k-space location $\vec{k}_i$ ($1\leq i \leq N_s$), then only the $i$-th column $\mathbf{w}_i$ of $\mathbf{W}$ relates the desired k-space pattern to the desired RF pulse. In this case, the vector $\mathbf{w}_i$ is identical to the desired RF. Therefore, the question of finding the $i$-th column $\mathbf{w}_i$ of $\mathbf{W}$ can be restated as the following: what should the RF pulse samples be in order to generate a unit delta function at the location $\vec{k}_i$ in k-space, and zeros elsewhere. Mathematically, the relationship that should be satisfied by the weights in column $\mathbf{w}_i$  can be expressed as \cite{katscher2003transmit}:   
\begin{equation}\label{eq:ScalerForm}
\mathbf{\delta}(\vec{k}-\vec{k}_i)=\sum_{t=1}^{N_t}\sum_{c=1}^{N_c}w_c(\vec{k}_t)\mathbf{s}_c(\vec{k}-\vec{k}_t)
\end{equation}
where $t$ indexes RF samples on the pulse’s excitation k-space trajectory, and $c$ indexes coils. $w_c(\vec{k}_t)$ is the $((c-1)Nt+t)$-th element of the $\mathbf{w}_i$ vector. $s_c(\vec{k}-\vec{k}_t)$ is the Fourier transform of coil-$c$'s $B_1^+$ map , shifted to be centered at excitation k-space location $\vec{k}_t$. 
This relationship can be restated in a matrix-vector form as:                                       
\begin{equation}\label{eq:MatrixForm}
\mathbf{Sw}_i=\mathbf{\delta}_i
\end{equation}
and the regularized pseudoinverse solution for the weight $\mathbf{w}_i$ is                       
\begin{equation}\label{eq:Solution}
\mathbf{w}_i=\left( \mathbf{S}^{H} \mathbf{S} + \lambda \mathbf{I} \right) ^{-1} \mathbf{s}_i^{H}
\end{equation}
where $\mathbf{S}$ is the $N_s$ by $N_cN_t$ sensitivity matrix consisting of horizontally stacked $\mathbf{s}_c(\vec{k}-\vec{k}_t)$ vectors for all $c$ and $t$, and $\mathbf{s}_i^{H}$ is the conjugate transpose of the $i$-th row of $\mathbf{S}$. Since k-space sensitivity maps are localized around DC, only few elements in $\mathbf{s}_i^{H}$ and $\mathbf{w}_i$ corresponding to $\vec{k}_t$s near $\vec{k}_i$ are non-zero. In order words, only few RF samples on the excitation trajectory near the target $\vec{k}_i$ can and should contribute energy to the unit delta function at this location, and all other RF samples on the excitation trajectory should automatically be zero. Therefore, in Equation \ref{eq:ScalerForm}, only few subscript $t$s are needed in the summation, and in Equation \ref{eq:MatrixForm} and \ref{eq:Solution}, the size of matrix $\mathbf{S}$ is much smaller than it was defined in Ref \cite{katscher2003transmit}. It also indicates the system matrix $\mathbf{W}$ is sparse. Techniques for efficient parallelization of the computation of the column $\mathbf{w}_i$s and efficient construction of the $\mathbf{S}^{H}\mathbf{S}$ matrices are also developed and will be discussed in the following text.

\subsection*{Parallelization}
\par A key advantage of the proposed pulse design formalism is that it can be broken down into many small problems and finely parallelized, because the process of solving each column of $\mathbf{W}$ is independent of other columns. The columns can be solved fully independently, or patchwise for target locations in neighborhoods, wherein all points in the neighborhood share the same $\mathbf{S}^{H}\mathbf{S}$ matrix. 
\begin{figure}
	\centering
	\includegraphics[width=6cm]{kspace_PTX_Patch}
	\caption{Illustration of one instance within the palatalization of a 2D k-space domain design problem. The totally design problem is divided into patches of width 4 cycle/FOV, and the 16 yellow points are the target points in this instance. With inclusion width of 4 cycle/FOV, the 46 green excitation trajectory points within the 12 cycle/FOV wide green square (4 cycle/FOV extended outside of the patch) are considered in this instance. The excitation within the 20 cycle/FOV wide red patch is constrained to zero except the point where the delta function is.}
	\label{fig:Patch}
\end{figure}
An example of this concept is shown in Figure \ref{fig:Patch}. For simplicity of visualization, it is demonstrated in a 2D problem, but the concept is easily extended to 3D. The figure depicts the solution of the $\mathbf{W}$ matrix 16 columns at a time, whose corresponding delta functions live within a patch of width 4 cycle/FOV (yellow points in Figure \ref{fig:Patch}). In this instance where the inclusion width is also 4 cycle/FOV, we truncate the $B_1^+$ map Fourier transforms to zero outside a 4 by 4 cycle/FOV square centered at DC. As a result, we must consider all the excitation trajectory points within a 12 by 12 cycle/FOV square, which is 4 cycle/FOV extended outside of the patch width 4 square, since they may contribute energy to the target locations corresponding to the 16 $\mathbf{W}$ matrix columns. For a single instance of the 16-point target patch shown in Figure \ref{fig:Patch}, the 46 green points on the excitation trajectory may contribute significant energy and are considered in the weight design. Furthermore, we must constrain the total excitation to zero at all k-space locations within a 20 by 20 cycle/FOV red patch in Figure \ref{fig:Patch}. This is because any energy deposited at each considered excitation trajectory points will affect not only the target points in the yellow square, but also the whole 2$\times$4 wide patch around that trajectory point. And the 20 by 20 cycle/FOV red patch is the total of the points that can be affected by all the excitation trajectory points considered in this instance. Therefore, in the solution for this instance, $\mathbf{w}$ is a 46$N_c\times$16 matrix, $\mathbf{S}$ is a 400$N_c\times$46$N_c$ matrix, $\mathbf{S}^{H}\mathbf{S}$ is a 46$N_c\times$46$N_c$ matrix, and $\mathbf{s}_i^{H}$ is a 46$N_c\times$16 matrix. 
%Since $\mathbf{s}_i^{H}$ is no longer related to the $i$th row of $\mathbf{S}$ and $i$th column of $\mathbf{W}$ only, it will be denoted as $\mathbf{S_{targ}}$ in later discussions. 
In the next instance, another 16 columns centered around another 4 points by 4 points patch will be solved. It should be noted that in different instances, the number of neighboring excitation trajectory points (the 46 green points in the previous instance) can vary. We will denote this number of points by $N_n$. $N_n$ can be zero when a patch is at the corners where no excitation trajectory point is adjacent. 
%For patches near edges of the excitation k-space FOV, the solution neighborhood and area may wrap back in a circulant shift fashion, depending on the resolution of the final spatial grid on which the user will evaluate the pulse. In Figure \ref{fig:Patch}), denoted by the red area to the right of Figure \ref{fig:Patch}).

\par The patch width determines the total number of instances to be solved. The inclusion width determines the accuracy of $B_1^+$ information utilized in the design. Together, the patch width and the inclusion width determine how many excitation trajectory points are included in each instance, which further determines the size of $\mathbf{S}^{H}\mathbf{S}$ whose construction is most computationally burdensome within an instance. Therefore, increasing patch width reduces the number of $\mathbf{S}^{H}\mathbf{S}$ matrices to be constructed but increases the burden of constructing each of them. An optimal patch width should be decided case by case for different excitation trajectories.

\subsection*{Efficient construction of $\mathbf{S}^{H}\mathbf{S}$ matrix}
\par Constructing $\mathbf{S}^{H}\mathbf{S}$ by finding $\mathbf{S}$ is computationally expensive. As described previously, the $((c-1)N_c+t)$-th column of the  $\mathbf{S}$ matrix, $\mathbf{S}_c(\vec{k}-\vec{k}_t)$, is the k-space sensitivity map of the $c$-th coil $\mathbf{S}_c(\vec{k})$ shifted to excitation k-space trajectory location $\vec{k}_t$. These shifts for each column of $\mathbf{S}$ are achieved by applying a linear phase modulation to the spatial domain $B_1^+$ map, followed by a fast Fourier transform (FFT). This process becomes computationally overwhelming when there are many RF samples, which is often the case. Furthermore, the matrix multiplication between $\mathbf{S}^{H}$ and $\mathbf{S}$ is also computationally intensive due to the large row dimension of $\mathbf{S}$ (400$Nt$ in the above example in Figure \ref{fig:Patch}).

\par Inspired by a rapid GRAPPA calibration method for arbitrary 2D/3D non-Cartesian trajectories proposed in Ref \cite{luo2019grappa}, we have developed a fast and memory-efficient algorithm to solve this problem. A key innovation of Ref \cite{luo2019grappa} is that the algorithm constructs the Hermitian $\mathbf{S}^{H}\mathbf{S}$ matrix directly by finding each of the matrix's lower triangle elements through interpolation, instead of building the $\mathbf{S}$ matrix explicitly followed by matrix multiplication. Conceptually, each element in the Hermitian matrix $\mathbf{S}^{H}\mathbf{S}$ is the vector sum of two shifted k-space sensitivity maps, which is also one single point of their convolution. With the multiplication property of Fourier transform, this convolution in k-space can be calculated from the Fourier transform of the dot product of the two spatial domain $B_1^+$ maps. For a more detailed derivation, please refer to Ref \cite{luo2019grappa}.
In practice, $\mathbf{S}^{H}\mathbf{S}$ is constructed in the following way. We first represent the $\mathbf{S}^{H}\mathbf{S}$ matrix with block matrices. Each block matrix $\mathbf{S}_i^{H}\mathbf{S}_j$ is of size $N_n$ by $N_n$, and $\mathbf{S}_i$ and $\mathbf{S}_j$ are the columns of $\mathbf{S}$ related to the k-space sensitivity maps of the $i$-th and $j$-th coils respectively.

\begin{equation}
\mathbf{S}^{H}\mathbf{S} = 
\begin{pmatrix}
\mathbf{S}_1^{H}\mathbf{S}_1 & \cdots & \mathbf{S}_1^{H}\mathbf{S}_{N_c} \\
\vdots  &  \ddots & \vdots  \\
\mathbf{S}_{N_c}^{H}\mathbf{S}_1 & \cdots & \mathbf{S}_{N_c}^{H}\mathbf{S}_{N_c} 
\end{pmatrix}
\end{equation}

Since $\mathbf{S}^{H}\mathbf{S}$ is Hermitian, we only need to find the values within the lower triangle of the matrix, which are the lower triangle blocks $\mathbf{S}_i^{H}\mathbf{S}_j$ with $i>j$. For a given lower triangle block $\mathbf{S}_i^{H}\mathbf{S}_j$  ($i>j$), all of its elements are interpolated from the densely sampled Fourier transform of the dot product of the spatial domain $B_1^+$ maps of the $i$-th and $j$-th coils. The $(m,n)$-th element is the value interpolated at $(\vec{k}_m-\vec{k}_n)$ away from DC. Therefore, to solve all the columns of $\mathbf{W}$, the total number of FFT operations needed in this efficient method is only $N_c(N_c+1)/2$, instead of ${N_t}{N_c}$, and the storage size is also much smaller. In addition to the efficiency related to FFT, this algorithm saves a large matrix multiplication between $\mathbf{S}^{H}$ and $\mathbf{S}$ for the solving of every single column of $\mathbf{W}$. 
Although an alternative strategy of determining each column of $\mathbf{S}$ explicitly by interpolating the $N_s$ sample points from unshifted $B_1^+$ Fourier transforms can also reduce the number of FFT operations, it still has the problem of large multiplications between $\mathbf{S}^{H}$ and $\mathbf{S}$ matrices. Furthermore, to calculate each element of $\mathbf{S}^{H}\mathbf{S}$, there are $2N_s$ number of interpolations involved with this sub-optimal strategy. While with the efficient algorithm there is only one interpolation from the densely sampled Fourier Transform of the dot product of two spatial domain $B_1^+$ maps needed. The extra interpolations involved in the sub-optimal strategy would introduce a larger error to $\mathbf{S}^{H}\mathbf{S}$.

\subsection*{ Off-Resonance correction}
\par As shown in Equation \ref{eq:SpatialDomainEquation} when we introduced spatial domain design in Chapter \ref{chap:SpatialDesign}, the equation connecting a pTx pulse to its excitation pattern has an off-resonance dependent term 
$e^{\imath \gamma \Delta B_0(\mathbf{x})(t-T)}$. In order to model this off-resonance dependent term in our k-space domain design, we adapted a fast implementation of the off-resonance compensation with time segmentation approximation and weighted least-squares interpolators \cite{fessler2005toeplitz}. 
By segmenting the RF pulse into multiple segments, this method disentangles the space-and-time dependent phase accrual induced by main field inhomogeneity into either space- or time- dependent terms, and therefore a same system matrix can be applied within each segment. Mathematically, it is
\begin{equation*}
e^{\imath \Delta\omega_j (t_i-T) }=\sum_{l=1}^{L} b_{l}(t_i) e^{\imath \theta_{l}(\Delta\omega_j)}
\end{equation*}
where $i=1\dots Nt$ indexes the RF samples, $j=1\dots Ns$ indexes the spatial locations, and $l$ indexes the time segments. The left term is the problematic space-and-time dependent term, with $\Delta\omega_j$ representing the off-resonance at the location-$j$ obtained from a field map and $T$ being the pulse duration. $b_{il}=b_{l}(t_i)$ are the time-dependent-only weights called temporal interpolators applied upon RF samples. $c_{lj}=e^{\imath \theta_{l}(\Delta\omega_j)}$ are the space-dependent-only phase accrual called spatial interpolators, applied upon the excitation pattern of each weighted RF segment. 
Therefore, the off-resonance correcting RF can be obtained by 
\begin{equation*}
\mathbf{b}=\sum_{l=1}^{L}diag\{\mathbf{b}_l\}\mathbf{W}\mathcal{F}(diag\{\mathbf{c}_l\}\mathbf{d})
\end{equation*}
where $\mathbf{b}_l$ and $\mathbf{c}_l$ are the vectorized interpoloators for the $l$-th segment.

### 2020-08-06 Manuscript/kPtx_paper.tex
add manuscript

\documentclass[11pt]{article}
% Command line: pdflatex -shell-escape compulse.tex
\usepackage{geometry} 
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{times}
\usepackage{bm}
\usepackage{fixltx2e}
\usepackage[outerbars]{changebar}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{color}
\usepackage{tabularx}
\usepackage{ulem}
\usepackage{verbatim}

\epstopdfsetup{suffix=} % to remove 'eps-to-pdf' suffix from converted images
%\usepackage{todonotes} % use option disable to hide all comments

\usepackage[sort&compress]{natbib}
\bibpunct{[}{]}{,}{n}{,}{,}

\usepackage[noend]{algpseudocode}

\usepackage{dsfont}
\usepackage{relsize}

\usepackage{todonotes}

\graphicspath{{Figure/}}

%changing the Eq. tag to use [] when numbering. use \eqref{label} to reference equations in text.
\makeatletter
  \def\tagform@#1{\maketag@@@{[#1]\@@italiccorr}}
\makeatother

\linespread{1.5}
%\setlength{\parindent}{0in}

% the following command can be used to mark changes made due to reviewers' concerns. Use as \revbox{Rx.y} for reviewer x, concern y.
\newif\ifmarkedup
\markeduptrue

\ifmarkedup
	\newcommand{\revbox}[1]{\marginpar{\framebox{\textcolor{blue}{#1}}}}
\else
	\newcommand{\revbox}[1]{}
	\renewcommand{\textcolor}[1]{}
	\renewcommand{\sout}[1]{}
\fi

%\newcommand{\bop}{$\vert B_1^+ \vert$}
\newcommand{\kt}{$k_\textrm{T}$}
\newcommand{\bmap}{$B_1^+$}
\newcommand{\mytilde}{\raise.17ex\hbox{$\scriptstyle\mathtt{\sim}$}}  % tilde symbol
\mathchardef\mhyphen="2D

\begin{document}

\title{Tailored Spiral In-Out Spectral-Spatial Water Suppression Pulses for 
Magnetic Resonance Spectroscopic Imaging}
\author{Jun Ma$^{1,3}$, Carrie Wismans$^{2}$, Zhipeng Cao$^{1}$, Dennis W.J. Klomp$^{2}$, Jannie P. Wijnen$^{2}$\\ and William A. Grissom$^{*1,3}$}
\maketitle
\begin{flushleft}
$^1$Vanderbilt University Institute of Imaging Science, Nashville, TN, United States\\
$^2$Department of Radiology, University Medical Centre Utrecht, Utrecht, the Netherlands \\   
$^3$Department of Biomedical Engineering, Vanderbilt University, Nashville, TN, United States\\

\par
--------------------------

\par
Word Count: Approximately 3550 \\
*Corresponding author: \\
Will Grissom\\
Department of Biomedical Engineering\\
Vanderbilt University\\
5824 Stevenson Center\\
Nashville, TN 37235 USA \\
E-mail: will.grissom@vanderbilt.edu \\
Twitter: @wgrissom

\par Submitted to Magnetic Resonance in Medicine for consideration as a Full Paper.

\par
Acknowledgment: This work was supported by NIH R01 EB016695.

\end{flushleft}
\thispagestyle{plain}

\pagebreak

%%%%%%%%%%%%%%%%%%%%%%% Abstract %%%%%%%%%%%%%%%%%%%%%%%

\section*{\underline{Abstract}} 
{\bf Purpose:}
something
\\[1em]
{\bf Methods:}
something
\\[1em]
{\bf Results:}
something
\\[1em]
{\bf Conclusion:}
something
\\[1em]
{\bf \noindent Key words:} Spectroscopy; RF pulses; Ultra-high field MRI; RF pulse design; Selective excitation; Optimization.

\pagebreak

%%%%%%%%%%%%%%%%%%%%%%% Main Text %%%%%%%%%%%%%%%%%%%%%%%

\input{Introduction}

\input{Theory}

\input{Method}

\input{Result}

\input{Conclusion}

\pagebreak

\bibliographystyle{unsrt}  % cse doesn't work
\bibliography{kPtx_paper}

\pagebreak

\end{document}

### 2020-08-06 Manuscript/Result.tex
WAG comments

@@
 	\includegraphics[width=\textwidth]{kspace_PTX_ComputationTime}
-	\caption{Studies of different parallelization parameters, where patch width is the square root of the number of $\mathbf{W}$ columns solved for simultaneously and inclusion width is the assumed range of influence of each excitation k-space location.
+	\caption{\textcolor{red}{WAG: Can you also run $2^0$ (most importantly) and $2^5$ patch width here?
+It would be good to show that the NRMSE levels off at some point.
+Also can you change the NRMSE axis to go from 0 to 6?
+That will help emphasize that even though the error is decreasing with increasing patch width,
+	the difference between patch width = 2 and patch width = something large is quite small. }
+	Studies of different parallelization parameters, where patch width is the square root of the number of $\mathbf{W}$ columns solved for simultaneously and inclusion width is the assumed range of influence of each excitation k-space location.
 \textbf{(a)} Computation time vs.
@@
 	\includegraphics[width=\textwidth]{kspace_PTX_ErrorMap2}
-	\caption{Normalized excitation patterns (top row) and error maps (bottom row) for k-space domain design (left column) and spatial domain design (right column), with NRMSE and design time indicated.}
+	\caption{\textcolor{red}{WAG: I think this is the figure that your example in Github should replicate.}
+	Normalized excitation patterns (top row) and error maps (bottom row) for k-space domain design (left column) and spatial domain design (right column), with NRMSE and design time indicated.}
 	\label{fig:ErrorMap}
@@
 	\includegraphics[width=\textwidth]{kspace_PTX_Acceleration}
-	\caption{ Normalized error maps and RMSE for spatial domain design (first row) and k-space domain design (second row), with excitation trajectories undersampled by different acceleration factors (third row).}
+	\caption{ \textcolor{red}{We should talk about this; I don't think reviewers will like the fact that the scale starts at 0.2. Also we should probably call it `Reduction Factor' since it is 
+	really the factor by which the pulse duration is reduced, and not exactly a k-space undersampling factor, is that right?}
+	Normalized error maps and RMSE for spatial domain design (first row) and k-space domain design (second row), with excitation trajectories undersampled by different acceleration factors (third row).}
 	\label{fig:kspace_PTX_Acceleration}
@@
 	\includegraphics[width=\textwidth]{kspace_PTX_B0}
-	\caption{\textbf{(a)} Normalized off-resonance map with Gaussian distortion centered above the frontal sinus, mimicking a characteristic susceptibility induced $B_0$ inhomogeneity.
+	\caption{\textcolor{red}{WAG: Update with new correction method; include compute times and errors versus number of segments}
+	\textbf{(a)} Normalized off-resonance map with Gaussian distortion centered above the frontal sinus, mimicking a characteristic susceptibility induced $B_0$ inhomogeneity.
 \textbf{(b)} Normalized excitation maps and RMSE for spatial domain design with off-resonance correction (first row), k-space domain design with and without off-resonance correction (second \& third rows).}

### 2020-08-06 Manuscript/Theory.tex
WAG comments

@@
 	\includegraphics[width=6cm]{kspace_PTX_Patch}
-	\caption{Illustration of one instance within the palatalization of a 2D k-space domain design problem.
+	\caption{\textcolor{red}{WAG: I think you should make two subfigures here: one that illustrates a single target location, and one that illustrates a patch of target locations.
+Also you should annotate the different widths, in the figures, with arrows.
+Also add a legend for the dots}
+	Illustration of one instance within the palatalization of a 2D k-space domain design problem.
 The totally design problem is divided into patches of width 4 cycle/FOV, and the 16 yellow points are the target points in this instance.

### 2020-08-14 Manuscript/Introduction.tex
edited wording

@@
 The size of $\mathbf{A}$ is $N_s$ by $N_cN_t$, where $N_s$ is the number of spatial locations, $N_c$ is the number of coils, and $N_t$ is the number of RF samples.
-Since $N_s$ becomes unbearably large in designs such as 2D plus spectral and 3D problems, and $N_c$ increases with more advance hardware designs, this $\mathbf{A}$ matrix is typically too large to find the inverse in terms of memory.
+Since $N_s$ becomes unbearably large in designs such as 2D plus spectral and 3D problems, and $N_c$ increases with more advance hardware designs,
+This $\mathbf{A}$ matrix is typically too large to find the inverse in terms of memory.
 Therefore, such design problems need to be solved by iterative conjugate-gradient (CG) methods which avoid matrix inversion.
@@
 These slow design methods are especially undesirable when tailored pulses are needed to be designed for each subject during one's examination in the scanner.
-Typically, the subject-tailored pulse design has to be done within one minute in the pre-scan stage, so that the incorporation of subject-tailored pulses into currently used workflow is practical and desirable.
+Typically, the subject-tailored pulse design has to be done within one minute in the pre-scan stage, so that the incorporation of fast design of subject-tailored pulses into currently used workflow is desirable.
 
-\par One application of subject-tailored multidimensional pTx pulses that is of particular interest of this dissertation is the 3D inner volume suppression (IVS) pulses for MR Corticography (MRCoG).MRCoG is a developing imaging technique which aims for submillimeter isotropic resolution whole-cortex and cortex-specific imaging.
+\par One application of subject-tailored multidimensional pTx pulses that is of particular interest of this paper is the 3D inner volume suppression (IVS) pulses for MR Corticography (MRCoG).MRCoG is a developing imaging technique which aims for submillimeter isotropic resolution whole-cortex and cortex-specific imaging.
 It is a promising technique to enable whole-brain functional and diffusion studies of the columnar and laminar subcortical structures, which are the fundamentals of higher-order brain functions. 

### 2020-08-14 Manuscript/Theory.tex
edited wording

@@
 
-\begin{equation}
+\begin{equation}\label{eq:SHS_blocks}
 \mathbf{S}^{H}\mathbf{S} = 
@@
 \subsection*{ Off-Resonance correction}
-\par As shown in Equation \ref{eq:SpatialDomainEquation} when we introduced spatial domain design in Chapter \ref{chap:SpatialDesign}, the equation connecting a pTx pulse to its excitation pattern has an off-resonance dependent term
+%\par As shown in Equation \ref{eq:SpatialDomainEquation} when we introduced spatial domain design in Chapter \ref{chap:SpatialDesign}, the equation connecting a pTx pulse to its excitation pattern has an off-resonance dependent term
 $e^{\imath \gamma \Delta B_0(\mathbf{x})(t-T)}$. 
-In order to model this off-resonance dependent term in our k-space domain design, we adapted a fast implementation of the off-resonance compensation with time segmentation approximation and weighted least-squares interpolators \cite{fessler2005toeplitz}.
+In order to model the off-resonance into our k-space domain design, we adapted a fast implementation of the off-resonance compensation with time segmentation approximation and weighted least-squares interpolators \cite{fessler2005toeplitz}.
 By segmenting the RF pulse into multiple segments, this method disentangles the space-and-time dependent phase accrual induced by main field inhomogeneity into either space- or time- dependent terms, and therefore a same system matrix can be applied within each segment.
@@
 \begin{equation*}
-e^{\imath \Delta\omega_j (t_i-T) }=\sum_{l=1}^{L} b_{l}(t_i) e^{\imath \theta_{l}(\Delta\omega_j)}
+e^{\imath \Delta\omega_j (t_i-T) }\approx\sum_{l=1}^{L} g_{l}(t_i) e^{\imath \theta_{l}(\Delta\omega_j)}
 \end{equation*}
@@
 The left term is the problematic space-and-time dependent term, with $\Delta\omega_j$ representing the off-resonance at the location-$j$ obtained from a field map and $T$ being the pulse duration.
-$b_{il}=b_{l}(t_i)$ are the time-dependent-only weights called temporal interpolators applied upon RF samples.
-$c_{lj}=e^{\imath \theta_{l}(\Delta\omega_j)}$ are the space-dependent-only phase accrual called spatial interpolators, applied upon the excitation pattern of each weighted RF segment.
-Therefore, the off-resonance correcting RF can be obtained by 
+$g_{il}=b_{l}(t_i)$ are the time-dependent-only weights called temporal interpolators applied upon RF samples.
+$h_{lj}=e^{\imath \theta_{l}(\Delta\omega_j)}$ are the space-dependent-only phase accrual called spatial interpolators, applied upon the excitation pattern of each weighted RF segment.
+Therefore, the spatial domain formulation becomes
 \begin{equation*}
-\mathbf{b}=\sum_{l=1}^{L}diag\{\mathbf{b}_l\}\mathbf{W}\mathcal{F}(diag\{\mathbf{c}_l\}\mathbf{d})
+\mathbf{d}=\sum_{l=1}^{L}diag\{\mathbf{h}_l\}\mathbf{A}(diag\{\mathbf{g}_l\}\mathbf{b})
 \end{equation*}
-where $\mathbf{b}_l$ and $\mathbf{c}_l$ are the vectorized interpoloators for the $l$-th segment.
+The spatial interpolators can be absorbed into the sensitivity maps. The $\mathbf{S}$ matrix in Equation \ref{eq:MatrixForm} will then become 
+\begin{equation*}
+\mathbf{S_{offres}}=\sum_{l=1}^{L}\mathbf{S}_l diag\{\mathbf{g}_l\}
+\end{equation*}
+where the columns of the $\mathbf{S}_l$ matrix, instead of being the aforementioned k-space sensitivity maps, are now the Fourier transform of the dot products of the spatial $B_1^+$ maps and the spatial interpolatros of the $l$-th segment, shifted to corresponding excitation k-space locations.
+The efficient construction of $\mathbf{S_{offres}}^{H}\mathbf{S_{offres}}$ follows the same concept mentioned before. 
+But with off-resonance, for the elements within an element matrix $\mathbf{S}_i^{H}\mathbf{S}_j$ in Equation \ref{eq:SHS_blocks}, instead of being interpolated from one densely sampled Fourier transform map, which is of the dot product of the spatial domain $B_1^+$ maps of the $i$-th and $j$-th coils, now they are interpolated from $L(L+1)/2$ different Fourier transform maps, each of which has underlying spatial $B_1^+$ maps with two sets of spatial interpolators absorbed into them.
+For the $(m,n)$-th element within the element matrix $\mathbf{S}_i^{H}\mathbf{S}_j$, the $L(L+1)/2$ interpolated values were then summed with weights $g_{l_i}(t_m)g_{l_j}(t_n)$, where $l_i$ and $l_j$ are the two segment numbers of the spatial interpolators observed into the corresponding $B_1^+$ maps.
+Compared to the efficient construction method without off-resonance, taking off-resonance into account increases the total number of FFT operations form $N_c(N_c+1)/2$ to $N_cL(N_cL+1)/2$, and increased the number of interpolations needed for each element from 1 to $L(L+1)/2$.

### 2020-08-16 Manuscript/Introduction.tex
wag starting edits

@@
 
-\par Multidimensional RF pulses have been widely used in many applications such as reduced field-of-view imaging \cite{rieseberg2002two}, transmit field inhomogeneity correction \cite{saekho2005small}, and susceptibility artifacts correction \cite{stenger2000three}.
-Parallel transmission (pTx) \cite{katscher2003transmit,zhu2004parallel} further strengthens the multidimensional pulses by providing extra spatial encoding power, shortening pulse duration, and reducing  specific absorption rate (SAR).
-However, current multidimensional pTx pulse design methods are based on a spatial domain formulation \cite{Grissom:2006:MRM,setsompop2008magnitude} that has prohibitive memory and computational requirements when the number of coils and the number of dimensions both become larger in current designs.
+\par Multidimensional parallel transmission \cite{Katscher:2003:Magn-Reson-Med:12509830,zhu2004parallel} has been widely investigated for applications including
+reduced field-of-view imaging \cite{malik:mrm:2015,mooiweer:2016},
+transmit field ($B_1^+$) inhomogeneity compensation \cite{Zhang:2007:Magn-Reson-Med:16526012,cloos:kpstd:2012},
+and compensation of susceptibility-induced signal loss \cite{deng:2009}.
+One of the first algorithms developed to demonstrate the concept of parallel transmission was formulated in the k-space domain \cite{Katscher:2003:Magn-Reson-Med:12509830}.
+In that method, a dense system matrix was constructed by Fourier transforming each transmit coil's $B_1^+$ map,
+forming a 2D convolution matrix for each coil, and then concatenating the coils' convolution matrices.
+The target pattern was also Fourier transformed and the pulses were solved by regularized pseudoinverse of the system matrix. 
+A spatial domain formulation \cite{Grissom:2006:MRM} was proposed soon after,
+wherein a non-uniform discrete Fourier transform matrix is constructed, 
+duplicated for each transmit coil, and weighted by that coil's $B_1^+$ map.
+The weighted matrices are concatenated and the pulses are solved by regularized pseudoinverse of the system matrix
+or using an iterative method.
+The spatial domain method is mathematically straightforward 
+and enables flexible system modeling, 
+incorporation of regions of interest and off-resonance compensation,
+and the use of non-uniform fast Fourier transforms to accelerate matrix multiplies.
+Since its introduction, nearly all parallel transmit studies have used the spatial domain method.
+
+\par Despite the spatial domain method's strengths, 
+it can have prohibitive computational requirements when the number of coils and the number of dimensions become large, 
+for example in three-dimensional and spectral-spatial pulse designs, and when off-resonance compensation is used.  
+The computation is multiplied further when the method is applied iteratively in magnitude least-squares \cite{setsompop2008magnitude} or constrained pulse designs \cite{brunner2010optimal,hoyos:tmi:2014}.
 Particularly, current spatial domain design methods map any given RF pulse $\mathbf{b}$ to its spatial excitation pattern $\mathbf{d}$ with a large system matrix $\mathbf{A}$, as:
@@
 The size of $\mathbf{A}$ is $N_s$ by $N_cN_t$, where $N_s$ is the number of spatial locations, $N_c$ is the number of coils, and $N_t$ is the number of RF samples. 
-Since $N_s$ becomes unbearably large in designs such as 2D plus spectral and 3D problems, and $N_c$ increases with more advance hardware designs,
-This $\mathbf{A}$ matrix is typically too large to find the inverse in terms of memory.
+Since $N_s$ becomes unbearably large in designs such as 2D plus spectral and 3D problems, 
+and $N_c$ increases with more advance hardware designs, 
+$\mathbf{A}$ is typically too large to store explicitly or directly invert. 
 Therefore, such design problems need to be solved by iterative conjugate-gradient (CG) methods which avoid matrix inversion. 
@@
 Furthermore, the NUFFT-based pulse design methods can also be slow due to all the gridding steps.
-Although these can be eliminated in NUFFT-based image reconstruction using Toeplitz formulation, in RF pulse design the Toeplitz formulation does not exist since the inner product is over space.
+Although these can be eliminated in NUFFT-based image reconstruction using Toeplitz formulation \cite{fessler2005toeplitz}, 
+in RF pulse design the Toeplitz formulation does not exist since the inner product is over space. 
 These slow design methods are especially undesirable when tailored pulses are needed to be designed for each subject during one's examination in the scanner.

### 2020-08-16 Manuscript/Introduction.tex
wording

@@
 The spatial domain method is mathematically straightforward 
-and enables flexible system modeling, 
-incorporation of regions of interest and off-resonance compensation,
+and enables flexible modeling and compensation of effects such as off-resonance, 
+incorporation of regions of interest,
 and the use of non-uniform fast Fourier transforms to accelerate matrix multiplies.
-Since its introduction, nearly all parallel transmit studies have used the spatial domain method.
+Since its introduction, nearly all parallel transmission studies have used the spatial domain method.
 

### 2020-08-17 kspace_PTX_clean/kPtx.m
Changed figures

@@ -103,7 +103,7 @@ if ifOffRes
             calib=reshape(calib,dimb1(1),dimb1(2),dimb1(3),nCoils*Lseg);
             nCoilsLseg=nCoils*Lseg;
 
-
+    disp 'Building FT maps'
     tic
             nComb = nCoilsLseg*(nCoilsLseg+1)/2;
             calib = single(calib);
@@ -117,6 +117,7 @@ if ifOffRes
 
 
 else
+    disp 'Building FT maps'
     tic
             nComb = nCoils*(nCoils+1)/2; % number of coil combinations
             calib = single(b1); % input B1 maps has to be single
@@ -139,7 +140,7 @@ else
 end
 
 %%  
-tic
+
 
 shift_c_mex=cell(1,length(segCenters(:)));
 kTrajInds_ii=cell(1,length(segCenters(:)));
@@ -170,7 +171,7 @@ for ii = 1:length(segCenters(:))
       % point of the target segment. It is needed for the interpolation.
       % shift_c_mex has to be cell of single matrices due to data handling of mex function.
 end
-toc
+
 
 
 

### 2020-08-17 kspace_PTX_clean/spins_kspace_clean.m

@@ -11,7 +11,9 @@ end
 %end
 
 if ~exist('blochsim_optcont_mex')
-    mex blochsim_optcont_mex.c
+    cd utils/
+    mex -largeArrayDims -lmwlapack blochsim_optcont_mex.c
+    cd ../
 end
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@ -29,9 +31,13 @@ kTrajSelect = 'spins';
 
 dPatternSelect = 'midSelect';
 
-ifOffRes=true;
+if_kpsce_MLS=false;
 
-%ifOpenMP=false; % IN OpemMP, number of thread has to be change in the .c file and then re-compile
+ifOffRes=false;
+
+ifOpenMP=false; % IN OpemMP, number of thread has to be change in the .c file and then re-compile
+
+ifDoSpatialDesign=false;
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % Load b1 maps, k-space trajectory, target pattern
@@ -43,10 +49,12 @@ switch(b1MapSelect)
 
         %load('~/Dropbox/kspacePTX_data/MGH24loop_head1_128_2.mat')
         load('MGH24loop_head1_128_2.mat')
+        load('Mask3dxyz128_ring.mat')
         
-        undersamp=4;  %Important parameter undersampling factor for b1 maps
+        undersamp=2;  %Important parameter undersampling factor for b1 maps
         b1 = B1p3dxyz128;
         mask = logical(Mask3dxyz128);
+        
         b1 = b1(1:undersamp:end,1:undersamp:end,1:undersamp:end,:);
         mask = mask(1:undersamp:end,1:undersamp:end,1:undersamp:end);
         
@@ -194,7 +202,11 @@ Tik = 3; %Regulerizer used in solving for W matrix.
 % Whether excitation energy deposites across FOV to the other end through kspace wrap back. 
 kWrapBack=false; 
 
+if ifOpenMP
 nThreads = 8; %=0 means no OpenMP
+else
[…]

### 2020-08-17 Manuscript/kPtx_paper.tex
WAG comments

@@
 
-\title{Tailored Spiral In-Out Spectral-Spatial Water Suppression Pulses for 
-Magnetic Resonance Spectroscopic Imaging}
-\author{Jun Ma$^{1,3}$, Carrie Wismans$^{2}$, Zhipeng Cao$^{1}$, Dennis W.J. Klomp$^{2}$, Jannie P. Wijnen$^{2}$\\ and William A. Grissom$^{*1,3}$}
+\title{k-Space Domain Parallel Transmit Pulse Design}
+\author{Jun Ma$^{1,2}$ and William A. Grissom$^{*1,2}$}
 \maketitle
@@
 $^1$Vanderbilt University Institute of Imaging Science, Nashville, TN, United States\\
-$^2$Department of Radiology, University Medical Centre Utrecht, Utrecht, the Netherlands \\   
-$^3$Department of Biomedical Engineering, Vanderbilt University, Nashville, TN, United States\\
+$^2$Department of Biomedical Engineering, Vanderbilt University, Nashville, TN, United States\\
 
@@
 \par
-Acknowledgment: This work was supported by NIH R01 EB016695.
+Acknowledgment: This work was supported by NIH grants R01 EB016695 and U01 EB 025162.
 
@@
 {\bf Purpose:}
-something
+To improve the computational efficiency of parallel transmission pulse design. 
 \\[1em]
@@
 \\[1em]
-{\bf \noindent Key words:} Spectroscopy; RF pulses; Ultra-high field MRI; RF pulse design; Selective excitation; Optimization.
+{\bf \noindent Key words:} Parallel Transmission; RF pulses; Ultra-high field MRI; RF pulse design; Selective excitation.
 

### 2020-08-17 Manuscript/Introduction.tex
wag finished intro

@@
 and compensation of susceptibility-induced signal loss \cite{deng:2009}.
-One of the first algorithms developed to demonstrate the concept of parallel transmission was formulated in the k-space domain \cite{Katscher:2003:Magn-Reson-Med:12509830}.
-In that method, a dense system matrix was constructed by Fourier transforming each transmit coil's $B_1^+$ map,
+One of the first small-tip-angle pulse design algorithms developed to demonstrate the concept of parallel transmission was formulated in the 
+excitation k-space domain \cite{Katscher:2003:Magn-Reson-Med:12509830}.
+In that method, a dense system matrix was constructed by applying a Fourier transform to each transmit coil's $B_1^+$ map,
 forming a 2D convolution matrix for each coil, and then concatenating the coils' convolution matrices.
-The target pattern was also Fourier transformed and the pulses were solved by regularized pseudoinverse of the system matrix. 
-A spatial domain formulation \cite{Grissom:2006:MRM} was proposed soon after,
+The pulses were solved by multiplying the 
+regularized pseudoinverse of the system matrix into the target excitation pattern's Fourier transform. 
+A spatial domain small-tip-angle parallel transmit pulse design algorithm 
+\cite{Grissom:2006:MRM} was proposed soon after,
 wherein a non-uniform discrete Fourier transform matrix is constructed, 
@@
 it can have prohibitive computational requirements when the number of coils and the number of dimensions become large, 
-for example in three-dimensional and spectral-spatial pulse designs, and when off-resonance compensation is used.  
-The computation is multiplied further when the method is applied iteratively in magnitude least-squares \cite{setsompop2008magnitude} or constrained pulse designs \cite{brunner2010optimal,hoyos:tmi:2014}.
-Particularly, current spatial domain design methods map any given RF pulse $\mathbf{b}$ to its spatial excitation pattern $\mathbf{d}$ with a large system matrix $\mathbf{A}$, as:
-\begin{equation*}
-	\mathbf{d}=\mathbf{Ab}
-\end{equation*}
-The size of $\mathbf{A}$ is $N_s$ by $N_cN_t$, where $N_s$ is the number of spatial locations, $N_c$ is the number of coils, and $N_t$ is the number of RF samples. 
-Since $N_s$ becomes unbearably large in designs such as 2D plus spectral and 3D problems, 
-and $N_c$ increases with more advance hardware designs, 
-$\mathbf{A}$ is typically too large to store explicitly or directly invert. 
-Therefore, such design problems need to be solved by iterative conjugate-gradient (CG) methods which avoid matrix inversion. 
-However, even if no matrix inversions are performed, the large system matrix may still be memory-inefficient when used in many matrix multiplications over a large number of iterations, making the solving process very slow.
-Furthermore, the NUFFT-based pulse design methods can also be slow due to all the gridding steps.
-Although these can be eliminated in NUFFT-based image reconstruction using Toeplitz formulation \cite{fessler2005toeplitz}, 
-in RF pulse design the Toeplitz formulation does not exist since the inner product is over space. 
-These slow design methods are especially undesirable when tailored pulses are needed to be designed for each subject during one's examination in the scanner.
-Typically, the subject-tailored pulse design has to be done within one minute in the pre-scan stage, so that the incorporation of fast design of subject-tailored pulses into currently used workflow is desirable.
+for example in three-dimensional \cite{malik2012tailored,davids2016fast} or spectral-spatial pulse designs, 
+when there is a large number of coils \cite{orzada:2019},
+and when off-resonance compensation is used.  
+The spatial domain system matrix typically has dimensions $N_s \times (N_{coils} \cdot N_t)$, 
+where $N_s$ is the number of spatial and spectral locations defined in the target excitation pattern,
+$N_{coils}$ is the number of transmit channels, and $N_t$ is the number of time points in the pulse.
+Typically values for $N_s$ range from 1,000 for 2D designs to 250,000 for 3D designs,
+the number of coils varies from 8 to 32 on ultra-high field scanners,
+and the number of time points is typically between 1,000 and 10,000. 
+Overall, for a 3D design the spatial domain system matrix can occupy up to 150 gigabytes of memory,
+making it infeasible to construct and invert on most modern computers.
+Explicit matrix storage and inversion can be avoided using non-uniform fast Fourier transforms to evaluate matrix multiplies,
+combined with iterative conjugate gradient solvers. 
+In such designs, parallelization can be applied across coils or across time segments in off-resonance-compensated designs,
+and GPU-based pulse designs have been described \cite{deng:2011}. 
+However, parallelization cannot be applied across iterations;
+hundreds of iterations are commonly used for 3D designs and thousands of iterations can be required for 
+magnitude least-squares \cite{setsompop2008magnitude} 
+or constrained pulse designs \cite{brunner2010optimal,hoyos:tmi:2014}. 
+Furthermore, non-uniform fast Fourier transforms can require significant computation for the repeated gridding steps; 
+in image reconstruction these can be eliminated since the Gram matrix is Toeplitz and can therefore be multiplied using fast Fourier transforms \cite{fessler2005toeplitz},
+but this does not apply to parallel transmit pulse design since the Gram matrix is not Toeplitz. 
+A further challenge for parallel transmit pulse design is that pulses must be computed for each subject,
+as a pre-scan stage while the subject lies in the scanner.
 
-\par One application of subject-tailored multidimensional pTx pulses that is of particular interest of this paper is the 3D inner volume suppression (IVS) pulses for MR Corticography (MRCoG).MRCoG is a developing imaging technique which aims for submillimeter isotropic resolution whole-cortex and cortex-specific imaging.
-It is a promising technique to enable whole-brain functional and diffusion studies of the columnar and laminar subcortical structures, which are the fundamentals of higher-order brain functions. 
-%The current columnar and laminar fMRI methods all use a small field of view in order to achieve sub-millimeter resolution.
+\par Here we describe a single-step (non-iterative) small-tip-angle excitation k-space-domain 
+pulse design algorithm with low memory requirements, 
+that can be applied to large pulse design problems with fine parallelization. 
+The algorithm produces a sparse k-space-domain pseudoinverse pulse design matrix 
+that directly relates the Fourier transform of the target excitation pattern to the RF pulses that produce it.
+Once the matrix is built, 
+RF pulses are instantaneously solved by a sparse matrix multiplication,
+and the matrix need not be recomputed if the target pattern changes.
+The algorithm takes advantage of the compactness of $B_1^+$ maps in excitation k-space
+to independently formulate and solve a parallelizable set of small matrix-vector subproblems 
+to obtain the significant entries of each column or groups of columns of the sparse design matrix.  
+% We advance the work by Katscher et al \cite{katscher2003transmit} by solving the columns of the system matrix in a parallelized fashion.
+
+\par In the following, 
+we derive the independent solution for each column of the design matrix 
+and introduce a patch-wise parallelization that provides control over the size and accuracy of each subproblem. 
+We further accelerate the solution of each subproblem by proposing an efficient method to construct a required
+matrix of $B_1^+$ map inner products while maintaining accuracy. 
+A method to incorporate off-resonance correction is also described. 
+The algorithm was characterized and validated in terms of accuracy (measured by Bloch equation simulations) 
+and computation time, with comparisons to spatial domain designs using 
+non-uniform fast Fourier transforms and the conjugate gradient algorithm.
+The application for the designs was a three-dimensional inner-volume excitation using a simulated 24-channel transmit array
+and a SPINS trajectory \cite{malik2012tailored}.
+The results show how computation time and accuracy depend on the parameters of the patch-wise parallelization,
+and how well the algorithm accommodates undersampling of excitation k-space undersampling and compensates pulses for off-resonance.
+An early account of this work was provided in Ref. \cite{grissom:ismrm18}.
+
+%\par One application of subject-tailored multidimensional pTx pulses that is of particular interest of this paper is the 3D inner volume suppression (IVS) pulses for MR Corticography (MRCoG).MRCoG is a developing imaging technique which aims for submillimeter isotropic resolution whole-cortex and cortex-specific imaging.
+%It is a promising technique to enable whole-brain functional and diffusion studies of the columnar and laminar subcortical structures, which are the fundamentals of higher-order brain functions. 
+%%The current columnar and laminar fMRI methods all use a small field of view in order to achieve sub-millimeter resolution.
 This does not allow studies to be performed across the whole cerebral cortex.
 On the other hand, current whole brain fMRI methods typically have spatial resolution greater than 1 mm, which is not sufficient for the studies of columnar and laminar structures.
-MRCoG will use IVS to enable highly accelerated imaging of the cortex, by reducing g-factor and suppressing physiological noise from ventricle CSF.
+%MRCoG will use IVS to enable highly accelerated imaging of the cortex, by reducing g-factor and suppressing physiological noise from ventricle CSF.
 Therefore, subject-tailored IVS pTx pulses are needed, which could be applied before each excitation and readout.
@@
 However, this IVS pulse design problem is challenging due to its 3D nature and the large number of transmit channels.
-
-\par Here we propose a k-space-based approach to pTx pulse design that has low memory and computational requirements, and is highly parallelizable.
-Specifically, we build a sparse system matrix $\mathbf{W}$ that relates the Fourier transform of the spatial domain desired pattern and the desired RF pulse, so that the RF pulse can be instantaneously solved by a sparse matrix multiplication with no matrix inversion or iterative CG method.
-We advance the work by Katscher et al \cite{katscher2003transmit} by solving the columns of the system matrix in a parallelized fashion.
-This is done by utilizing the independence between columns of the system matrix which comes from the compactness of sensitivity maps in k-space.
-In the following text, we will derive the independent solution to each column and show a patch-wise parallelization that allows the control of the size and accuracy of each instance problem.
-We further accelerate the solution of each instance problem by proposing an efficient method to construct a key matrix needed while maintaining accuracy.
-Off-resonance correction is also incorporated into this k-space domain design.
-Then we apply this k-space domain design method to the 3D IVS pulse design problem, and demonstrate its striking acceleration to the computation speed by comparing its performance to the conventional spatial domain design method through simulations.
-We show how the computation speed and accuracy can be traded off through controlling the parameters of the patch-wise parallelization.
-We also demonstrate the k-space domain design's ability to accommodate excitation k-space undersampling and correct off-resonance.

### 2020-08-17 Manuscript/Introduction.tex
wag edited first section of theory

@@
 and when off-resonance compensation is used.  
-The spatial domain system matrix typically has dimensions $N_s \times (N_{coils} \cdot N_t)$, 
+The spatial domain system matrix typically has dimensions $N_s \times (N_c \cdot N_t)$, 
 where $N_s$ is the number of spatial and spectral locations defined in the target excitation pattern,
-$N_{coils}$ is the number of transmit channels, and $N_t$ is the number of time points in the pulse.
+$N_c$ is the number of transmit channels, and $N_t$ is the number of time points in the pulse.
 Typically values for $N_s$ range from 1,000 for 2D designs to 250,000 for 3D designs,

### 2020-08-17 Manuscript/Theory.tex
wag edited first section of theory

@@
 
-\subsection*{k-space domain parallel-transmit pulse design}
-\par Here we describe the derivation of the highly parallelizable k-sapce domain design method.
-We propose to find a system matrix $\mathbf{W}$ that directly maps a desired excitation pattern in k-space $\mathcal{F}(\mathbf{d})$, which is the Fourier transform of the spatial domain desired pattern $\mathbf{d}$, to the corresponding desired RF pulse $\mathbf{b}$, as:
-\begin{equation*}
-\mathbf{b}=\mathbf{W}\mathcal{F}(\mathbf{d})
-\end{equation*}
-$\mathcal{F}(\mathbf{d})$ is the vectorized k-space excitation pattern with length of $N_s$, which is the number of spatial/k-space locations.
-$\mathbf{b}$ is the concatenated multi-channel RF samples with length of $N_tN_c$, where $N_t$ and $N_c$ are the numbers of time points and coils, respectively.
-$\mathbf{W}$ is the $N_tN_c$ by $N_s$ system matrix, which will latter be shown sparse.
-Therefore, once the $\mathbf{W}$ matrix is found, the RF design problem can be instantaneously solved by a sparse matrix multiplication, and there is no matrix inversion or iterative CG method needed.
-Furthermore, in design problems involved iterative procedures, such as the phase updates in magnitude-least-squares pulse designs \cite{setsompop2008magnitude} and the regularization factor updates in power/roughness constrained pulse design, the sparsity of the $\mathbf{W}$ matrix makes the iterative process much more efficient in terms of memory and speed.
+\subsection*{k-Space-Domain Subproblems}
+We propose to compute a sparse 
+design matrix $\bm{W}$ that directly maps the Fourier transform of a desired spatial 
+excitation pattern to a vector of RF pulses that together produce the pattern, as:
+\begin{equation}
+\bm{b} = \bm{W} \mathcal{F}(\bm{d}),
+\end{equation}
+where $\bm{b}$ is a vector of concatenated multi-channel RF pulses with length $N_t \cdot N_c$, 
+where $N_t$ and $N_c$ are the numbers of time points and coils, respectively,
+and $\mathcal{F}(\bm{d})$ is a length-$N_s$ vector containing the 
+Fourier transform of the desired k-space excitation pattern $\bm{d}$.
+$\bm{W}$ has dimensions $N_t \cdot N_c \times N_s$.
+Once the entries of $\bm{W}$ are computed, 
+the RF design problem can be instantaneously solved by a sparse matrix multiplication, 
+without a full matrix inversion or an iterative algorithm. 
+Here we describe how to break down the problem of constructing $\bm{W}$ 
+into a set of smaller independent subproblems that can be solved in parallel.
+
+%Furthermore, in design problems involved iterative procedures, such as the phase updates in magnitude-least-squares pulse designs \cite{setsompop2008magnitude} and the regularization factor updates in power/roughness constrained pulse design, the sparsity of the $\bm{W}$ matrix makes the iterative process much more efficient in terms of memory and speed.
 In the work of Katscher et al \cite{katscher2003transmit}, parallel transmit pulse design was also formulated in the k-space domain.
-However, in Ref \cite{katscher2003transmit}, the matrix $\mathbf{W}$ was solved as a whole, which required constructing and inverting a large $\mathbf{S}^H\mathbf{S}$ matrix, which will be explained in the following text.
-Our proposed method finely divides the process of finding $\mathbf{W}$ into many independent instances, which allows the use of parallel computing to largely accelerate the computation.
-Furthermore, the $\mathbf{S}^H\mathbf{S}$ matrices of different instances are each small, and our proposed method efficiently constructs these matrices, which further accelerates the computation.
+However, in Ref \cite{katscher2003transmit}, the matrix $\bm{W}$ was solved as a whole, which required constructing and inverting a large $\bm{S}^H\bm{S}$ matrix, which will be explained in the following text.
+Our proposed method finely divides the process of finding $\bm{W}$ into many independent instances, which allows the use of parallel computing to largely accelerate the computation.
+Furthermore, the $\bm{S}^H\bm{S}$ matrices of different instances are each small, and our proposed method efficiently constructs these matrices, which further accelerates the computation.
 
-\par We can solve for the columns of the $\mathbf{W}$ matrix independently to each other, based on the key observation that if the desired k-space pattern is a delta function at a given k-space location $\vec{k}_i$ ($1\leq i \leq N_s$), then only the $i$-th column $\mathbf{w}_i$ of $\mathbf{W}$ relates the desired k-space pattern to the desired RF pulse.
-In this case, the vector $\mathbf{w}_i$ is identical to the desired RF.
-Therefore, the question of finding the $i$-th column $\mathbf{w}_i$ of $\mathbf{W}$ can be restated as the following: what should the RF pulse samples be in order to generate a unit delta function at the location $\vec{k}_i$ in k-space, and zeros elsewhere.
-Mathematically, the relationship that should be satisfied by the weights in column $\mathbf{w}_i$  can be expressed as \cite{katscher2003transmit}:
+\par The columns of $\bm{W}$ can be solved independently, 
+based on the observation that if the desired k-space pattern is a delta function at a k-space location 
+$\vec{k}_j$ ($1\leq j \leq N_s$), 
+then only the $j$-th column $\bm{w}_j$ of $\bm{W}$ is required to relate 
+the desired k-space pattern to the desired RF pulse. 
+In this case, the vector $\bm{w}_j$ is identical to the desired RF. 
+Therefore, the problem of finding the $j$-th column $\bm{w}_j$ of $\bm{W}$ can be restated as the following: 
+what should the RF pulse samples be to generate a unit delta function at the location $\vec{k}_j$ in k-space, 
+and zeros elsewhere? 
+Mathematically, the relationship that should be satisfied by the weights in column $\bm{w}_j$  can be expressed as:   
 \begin{equation}\label{eq:ScalerForm}
-\mathbf{\delta}(\vec{k}-\vec{k}_i)=\sum_{t=1}^{N_t}\sum_{c=1}^{N_c}w_c(\vec{k}_t)\mathbf{s}_c(\vec{k}-\vec{k}_t)
+\delta(\vec{k}-\vec{k}_j)=\sum_{i=1}^{N_t}\sum_{c=1}^{N_c} w_c(\vec{k}_i) s_c(\vec{k}-\vec{k}_i)
 \end{equation}
-where $t$ indexes RF samples on the pulse’s excitation k-space trajectory, and $c$ indexes coils.
-$w_c(\vec{k}_t)$ is the $((c-1)Nt+t)$-th element of the $\mathbf{w}_i$ vector.
-$s_c(\vec{k}-\vec{k}_t)$ is the Fourier transform of coil-$c$'s $B_1^+$ map , shifted to be centered at excitation k-space location $\vec{k}_t$.
-This relationship can be restated in a matrix-vector form as:                                       
+where $i$ indexes time points in the pulses' excitation k-space trajectory, 
+and $c$ indexes coils. 
+$w_c(\vec{k}_i)$ is the $((c-1)N_t+i)$-th element of the $\bm{w}_j$ vector,
+and $s_c(\vec{k}-\vec{k}_i)$ is the Fourier transform of coil-$c$'s $B_1^+$ map, 
+shifted to be centered at excitation k-space location $\vec{k}_i$. 
+Equation \ref{eq:ScalerForm} can be restated in matrix-vector form as:                                       
 \begin{equation}\label{eq:MatrixForm}
-\mathbf{Sw}_i=\mathbf{\delta}_i
+\bm{Sw}_j=\bm{\delta}_j,
 \end{equation}
-and the regularized pseudoinverse solution for the weight $\mathbf{w}_i$ is                       
+where $\bm{S}$ is a $N_s \times N_c \cdot N_t$ 
+matrix containing values of $s_c(\vec{k}-\vec{k}_i)$ for all $c$ and $i$,
+and $\bm{\delta}_j$ is a vector containing a one in the entry corresponding to excitation k-space location
+$\vec{k}_j$, and zeros in all other entries. 
+The regularized pseudoinverse solution for $\bm{w}_j$ is:                      
 \begin{equation}\label{eq:Solution}
-\mathbf{w}_i=\left( \mathbf{S}^{H} \mathbf{S} + \lambda \mathbf{I} \right) ^{-1} \mathbf{s}_i^{H}
+\bm{w}_j=\left( \bm{S}^{H} \bm{S} + \lambda \bm{I} \right) ^{-1} \bm{s}_j^{H}
 \end{equation}
-where $\mathbf{S}$ is the $N_s$ by $N_cN_t$ sensitivity matrix consisting of horizontally stacked $\mathbf{s}_c(\vec{k}-\vec{k}_t)$ vectors for all $c$ and $t$, and $\mathbf{s}_i^{H}$ is the conjugate transpose of the $i$-th row of $\mathbf{S}$.
-Since k-space sensitivity maps are localized around DC, only few elements in $\mathbf{s}_i^{H}$ and $\mathbf{w}_i$ corresponding to $\vec{k}_t$s near $\vec{k}_i$ are non-zero.
-In order words, only few RF samples on the excitation trajectory near the target $\vec{k}_i$ can and should contribute energy to the unit delta function at this location, and all other RF samples on the excitation trajectory should automatically be zero.
-Therefore, in Equation \ref{eq:ScalerForm}, only few subscript $t$s are needed in the summation, and in Equation \ref{eq:MatrixForm} and \ref{eq:Solution}, the size of matrix $\mathbf{S}$ is much smaller than it was defined in Ref \cite{katscher2003transmit}.
-It also indicates the system matrix $\mathbf{W}$ is sparse.
-Techniques for efficient parallelization of the computation of the column $\mathbf{w}_i$s and efficient construction of the $\mathbf{S}^{H}\mathbf{S}$ matrices are also developed and will be discussed in the following text.
+where $\bm{s}_j^{H}$ is the conjugate transpose of the $j$-th row of $\bm{S}$.
+
+\par If all points on the excitation k-space trajectory are considered in Equation \ref{eq:ScalerForm},
+then there is no reduction in computation compared to a conventional pseudoinverse-based pulse design.
+However, because $B_1^+$ maps are compact in excitation k-space and localized near DC,
+only a small number ($\ll N_t$) of trajectory points near the target location $\vec{k}_j$ can contribute significantly
+to the excitation pattern at $\vec{k}_j$ or its neighbors, 
+and therefore need to be considered in the subproblem;
+all other trajectory points can be ignored.
+This means we can modify Equation \ref{eq:ScalerForm} to:
+\begin{equation}
+\delta(\vec{k}-\vec{k}_j) = \sum_{\vec{k}_i \in \mathbb{N}}\sum_{c=1}^{N_c} w_c(\vec{k}_i) s_c(\vec{k}-\vec{k}_i),
+\end{equation} 
+where $\mathbb{N}$ is the set of trajectory points in the vicinity of $\vec{k}_j$. 
+This reduced set of trajectory points reduces the column dimension of $\bm{S}$.
+Since target locations that are distant to $\vec{k}_j$ can also be ignored,
+the row dimension of $\bm{S}$ is also reduced to the size of a smaller neighborhood immediately surrounding $\vec{k}_j$. 
+These reduced problem dimensions further imply that the design matrix $\bm{W}$ is sparse. 
+Figure \ref{fig:Patch}a illustrates a target point $\vec{k}_j$, 
+the nearby points on a spiral trajectory that need to be included in the solution for $\bm{w}_j$,
+and the neighboring target location points where a zero excitation must be enforced. 
+In the following, we define target and trajectory neighborhood sizes, and describe an efficient 
+method to construct the $\bm{S}^{H}\bm{S}$ matrices.
 
 \subsection*{Parallelization}
-\par A key advantage of the proposed pulse design formalism is that it can be broken down into many small problems and finely parallelized, because the process of solving each column of $\mathbf{W}$ is independent of other columns.
-The columns can be solved fully independently, or patchwise for target locations in neighborhoods, wherein all points in the neighborhood share the same $\mathbf{S}^{H}\mathbf{S}$ matrix.
+\par A key advantage of the proposed pulse design formalism is that it can be broken down into many small problems and finely parallelized, because the process of solving each column of $\bm{W}$ is independent of other columns.
+The columns can be solved fully independently, or patchwise for target locations in neighborhoods, wherein all points in the neighborhood share the same $\bm{S}^{H}\bm{S}$ matrix.
 \begin{figure}
@@
 For simplicity of visualization, it is demonstrated in a 2D problem, but the concept is easily extended to 3D.
-The figure depicts the solution of the $\mathbf{W}$ matrix 16 columns at a time, whose corresponding delta functions live within a patch of width 4 cycle/FOV (yellow points in Figure \ref{fig:Patch}).
+The figure depicts the solution of the $\bm{W}$ matrix 16 columns at a time, whose corresponding delta functions live within a patch of width 4 cycle/FOV (yellow points in Figure \ref{fig:Patch}).
 In this instance where the inclusion width is also 4 cycle/FOV, we truncate the $B_1^+$ map Fourier transforms to zero outside a 4 by 4 cycle/FOV square centered at DC.
-As a result, we must consider all the excitation trajectory points within a 12 by 12 cycle/FOV square, which is 4 cycle/FOV extended outside of the patch width 4 square, since they may contribute energy to the target locations corresponding to the 16 $\mathbf{W}$ matrix columns.
+As a result, we must consider all the excitation trajectory points within a 12 by 12 cycle/FOV square, which is 4 cycle/FOV extended outside of the patch width 4 square, since they may contribute energy to the target locations corresponding to the 16 $\bm{W}$ matrix columns.
 For a single instance of the 16-point target patch shown in Figure \ref{fig:Patch}, the 46 green points on the excitation trajectory may contribute significant energy and are considered in the weight design.
@@
 And the 20 by 20 cycle/FOV red patch is the total of the points that can be affected by all the excitation trajectory points considered in this instance.
-Therefore, in the solution for this instance, $\mathbf{w}$ is a 46$N_c\times$16 matrix, $\mathbf{S}$ is a 400$N_c\times$46$N_c$ matrix, $\mathbf{S}^{H}\mathbf{S}$ is a 46$N_c\times$46$N_c$ matrix, and $\mathbf{s}_i^{H}$ is a 46$N_c\times$16 matrix.
-%Since $\mathbf{s}_i^{H}$ is no longer related to the $i$th row of $\mathbf{S}$ and $i$th column of $\mathbf{W}$ only, it will be denoted as $\mathbf{S_{targ}}$ in later discussions. 
+Therefore, in the solution for this instance, $\bm{w}$ is a 46$N_c\times$16 matrix, $\bm{S}$ is a 400$N_c\times$46$N_c$ matrix, $\bm{S}^{H}\bm{S}$ is a 46$N_c\times$46$N_c$ matrix, and $\bm{s}_i^{H}$ is a 46$N_c\times$16 matrix.
+%Since $\bm{s}_i^{H}$ is no longer related to the $i$th row of $\bm{S}$ and $i$th column of $\bm{W}$ only, it will be denoted as $\bm{S_{targ}}$ in later discussions. 
 In the next instance, another 16 columns centered around another 4 points by 4 points patch will be solved.
@@
 The inclusion width determines the accuracy of $B_1^+$ information utilized in the design.
-Together, the patch width and the inclusion width determine how many excitation trajectory points are included in each instance, which further determines the size of $\mathbf{S}^{H}\mathbf{S}$ whose construction is most computationally burdensome within an instance.
-Therefore, increasing patch width reduces the number of $\mathbf{S}^{H}\mathbf{S}$ matrices to be constructed but increases the burden of constructing each of them.
+Together, the patch width and the inclusion width determine how many excitation trajectory points are included in each instance, which further determines the size of $\bm{S}^{H}\bm{S}$ whose construction is most computationally burdensome within an instance.
+Therefore, increasing patch width reduces the number of $\bm{S}^{H}\bm{S}$ matrices to be constructed but increases the burden of constructing each of them.
 An optimal patch width should be decided case by case for different excitation trajectories.
 
-\subsection*{Efficient construction of $\mathbf{S}^{H}\mathbf{S}$ matrix}
-\par Constructing $\mathbf{S}^{H}\mathbf{S}$ by finding $\mathbf{S}$ is computationally expensive.
-As described previously, the $((c-1)N_c+t)$-th column of the  $\mathbf{S}$ matrix, $\mathbf{S}_c(\vec{k}-\vec{k}_t)$, is the k-space sensitivity map of the $c$-th coil $\mathbf{S}_c(\vec{k})$ shifted to excitation k-space trajectory location $\vec{k}_t$.
-These shifts for each column of $\mathbf{S}$ are achieved by applying a linear phase modulation to the spatial domain $B_1^+$ map, followed by a fast Fourier transform (FFT).
+\subsection*{Efficient construction of $\bm{S}^{H}\bm{S}$ matrix}
+\par Constructing $\bm{S}^{H}\bm{S}$ by finding $\bm{S}$ is computationally expensive.
+As described previously, the $((c-1)N_c+t)$-th column of the  $\bm{S}$ matrix, $\bm{S}_c(\vec{k}-\vec{k}_t)$, is the k-space sensitivity map of the $c$-th coil $\bm{S}_c(\vec{k})$ shifted to excitation k-space trajectory location $\vec{k}_t$.
+These shifts for each column of $\bm{S}$ are achieved by applying a linear phase modulation to the spatial domain $B_1^+$ map, followed by a fast Fourier transform (FFT).
 This process becomes computationally overwhelming when there are many RF samples, which is often the case.
-Furthermore, the matrix multiplication between $\mathbf{S}^{H}$ and $\mathbf{S}$ is also computationally intensive due to the large row dimension of $\mathbf{S}$ (400$Nt$ in the above example in Figure \ref{fig:Patch}).
+Furthermore, the matrix multiplication between $\bm{S}^{H}$ and $\bm{S}$ is also computationally intensive due to the large row dimension of $\bm{S}$ (400$Nt$ in the above example in Figure \ref{fig:Patch}).
 
 \par Inspired by a rapid GRAPPA calibration method for arbitrary 2D/3D non-Cartesian trajectories proposed in Ref \cite{luo2019grappa}, we have developed a fast and memory-efficient algorithm to solve this problem.
-A key innovation of Ref \cite{luo2019grappa} is that the algorithm constructs the Hermitian $\mathbf{S}^{H}\mathbf{S}$ matrix directly by finding each of the matrix's lower triangle elements through interpolation, instead of building the $\mathbf{S}$ matrix explicitly followed by matrix multiplication.
-Conceptually, each element in the Hermitian matrix $\mathbf{S}^{H}\mathbf{S}$ is the vector sum of two shifted k-space sensitivity maps, which is also one single point of their convolution.
+A key innovation of Ref \cite{luo2019grappa} is that the algorithm constructs the Hermitian $\bm{S}^{H}\bm{S}$ matrix directly by finding each of the matrix's lower triangle elements through interpolation, instead of building the $\bm{S}$ matrix explicitly followed by matrix multiplication.
+Conceptually, each element in the Hermitian matrix $\bm{S}^{H}\bm{S}$ is the vector sum of two shifted k-space sensitivity maps, which is also one single point of their convolution.
 With the multiplication property of Fourier transform, this convolution in k-space can be calculated from the Fourier transform of the dot product of the two spatial domain $B_1^+$ maps.
 For a more detailed derivation, please refer to Ref \cite{luo2019grappa}.
-In practice, $\mathbf{S}^{H}\mathbf{S}$ is constructed in the following way.
-We first represent the $\mathbf{S}^{H}\mathbf{S}$ matrix with block matrices.
-Each block matrix $\mathbf{S}_i^{H}\mathbf{S}_j$ is of size $N_n$ by $N_n$, and $\mathbf{S}_i$ and $\mathbf{S}_j$ are the columns of $\mathbf{S}$ related to the k-space sensitivity maps of the $i$-th and $j$-th coils respectively.
+In practice, $\bm{S}^{H}\bm{S}$ is constructed in the following way.
+We first represent the $\bm{S}^{H}\bm{S}$ matrix with block matrices.
+Each block matrix $\bm{S}_i^{H}\bm{S}_j$ is of size $N_n$ by $N_n$, and $\bm{S}_i$ and $\bm{S}_j$ are the columns of $\bm{S}$ related to the k-space sensitivity maps of the $i$-th and $j$-th coils respectively.
 
 \begin{equation}\label{eq:SHS_blocks}
-\mathbf{S}^{H}\mathbf{S} = 
+\bm{S}^{H}\bm{S} = 
 \begin{pmatrix}
-\mathbf{S}_1^{H}\mathbf{S}_1 & \cdots & \mathbf{S}_1^{H}\mathbf{S}_{N_c} \\
+\bm{S}_1^{H}\bm{S}_1 & \cdots & \bm{S}_1^{H}\bm{S}_{N_c} \\
 \vdots  &  \ddots & \vdots  \\
-\mathbf{S}_{N_c}^{H}\mathbf{S}_1 & \cdots & \mathbf{S}_{N_c}^{H}\mathbf{S}_{N_c} 
+\bm{S}_{N_c}^{H}\bm{S}_1 & \cdots & \bm{S}_{N_c}^{H}\bm{S}_{N_c} 
 \end{pmatrix}
@@
 
-Since $\mathbf{S}^{H}\mathbf{S}$ is Hermitian, we only need to find the values within the lower triangle of the matrix, which are the lower triangle blocks $\mathbf{S}_i^{H}\mathbf{S}_j$ with $i>j$.
-For a given lower triangle block $\mathbf{S}_i^{H}\mathbf{S}_j$  ($i>j$), all of its elements are interpolated from the densely sampled Fourier transform of the dot product of the spatial domain $B_1^+$ maps of the $i$-th and $j$-th coils.
+Since $\bm{S}^{H}\bm{S}$ is Hermitian, we only need to find the values within the lower triangle of the matrix, which are the lower triangle blocks $\bm{S}_i^{H}\bm{S}_j$ with $i>j$.
+For a given lower triangle block $\bm{S}_i^{H}\bm{S}_j$  ($i>j$), all of its elements are interpolated from the densely sampled Fourier transform of the dot product of the spatial domain $B_1^+$ maps of the $i$-th and $j$-th coils.
 The $(m,n)$-th element is the value interpolated at $(\vec{k}_m-\vec{k}_n)$ away from DC.
-Therefore, to solve all the columns of $\mathbf{W}$, the total number of FFT operations needed in this efficient method is only $N_c(N_c+1)/2$, instead of ${N_t}{N_c}$, and the storage size is also much smaller.
-In addition to the efficiency related to FFT, this algorithm saves a large matrix multiplication between $\mathbf{S}^{H}$ and $\mathbf{S}$ for the solving of every single column of $\mathbf{W}$.
-Although an alternative strategy of determining each column of $\mathbf{S}$ explicitly by interpolating the $N_s$ sample points from unshifted $B_1^+$ Fourier transforms can also reduce the number of FFT operations, it still has the problem of large multiplications between $\mathbf{S}^{H}$ and $\mathbf{S}$ matrices.
-Furthermore, to calculate each element of $\mathbf{S}^{H}\mathbf{S}$, there are $2N_s$ number of interpolations involved with this sub-optimal strategy.
+Therefore, to solve all the columns of $\bm{W}$, the total number of FFT operations needed in this efficient method is only $N_c(N_c+1)/2$, instead of ${N_t}{N_c}$, and the storage size is also much smaller.
+In addition to the efficiency related to FFT, this algorithm saves a large matrix multiplication between $\bm{S}^{H}$ and $\bm{S}$ for the solving of every single column of $\bm{W}$.
+Although an alternative strategy of determining each column of $\bm{S}$ explicitly by interpolating the $N_s$ sample points from unshifted $B_1^+$ Fourier transforms can also reduce the number of FFT operations, it still has the problem of large multiplications between $\bm{S}^{H}$ and $\bm{S}$ matrices.
+Furthermore, to calculate each element of $\bm{S}^{H}\bm{S}$, there are $2N_s$ number of interpolations involved with this sub-optimal strategy.
 While with the efficient algorithm there is only one interpolation from the densely sampled Fourier Transform of the dot product of two spatial domain $B_1^+$ maps needed.
-The extra interpolations involved in the sub-optimal strategy would introduce a larger error to $\mathbf{S}^{H}\mathbf{S}$.
+The extra interpolations involved in the sub-optimal strategy would introduce a larger error to $\bm{S}^{H}\bm{S}$.
 
@@
 %\par As shown in Equation \ref{eq:SpatialDomainEquation} when we introduced spatial domain design in Chapter \ref{chap:SpatialDesign}, the equation connecting a pTx pulse to its excitation pattern has an off-resonance dependent term
-$e^{\imath \gamma \Delta B_0(\mathbf{x})(t-T)}$. 
+$e^{\imath \gamma \Delta B_0(\bm{x})(t-T)}$. 
 In order to model the off-resonance into our k-space domain design, we adapted a fast implementation of the off-resonance compensation with time segmentation approximation and weighted least-squares interpolators \cite{fessler2005toeplitz}.
@@
 \begin{equation*}
-\mathbf{d}=\sum_{l=1}^{L}diag\{\mathbf{h}_l\}\mathbf{A}(diag\{\mathbf{g}_l\}\mathbf{b})
+\bm{d}=\sum_{l=1}^{L}diag\{\bm{h}_l\}\bm{A}(diag\{\bm{g}_l\}\bm{b})
 \end{equation*}
-The spatial interpolators can be absorbed into the sensitivity maps. The $\mathbf{S}$ matrix in Equation \ref{eq:MatrixForm} will then become 
+The spatial interpolators can be absorbed into the sensitivity maps. The $\bm{S}$ matrix in Equation \ref{eq:MatrixForm} will then become 
 \begin{equation*}
-\mathbf{S_{offres}}=\sum_{l=1}^{L}\mathbf{S}_l diag\{\mathbf{g}_l\}
+\bm{S_{offres}}=\sum_{l=1}^{L}\bm{S}_l diag\{\bm{g}_l\}
 \end{equation*}
-where the columns of the $\mathbf{S}_l$ matrix, instead of being the aforementioned k-space sensitivity maps, are now the Fourier transform of the dot products of the spatial $B_1^+$ maps and the spatial interpolatros of the $l$-th segment, shifted to corresponding excitation k-space locations.
-The efficient construction of $\mathbf{S_{offres}}^{H}\mathbf{S_{offres}}$ follows the same concept mentioned before. 
-But with off-resonance, for the elements within an element matrix $\mathbf{S}_i^{H}\mathbf{S}_j$ in Equation \ref{eq:SHS_blocks}, instead of being interpolated from one densely sampled Fourier transform map, which is of the dot product of the spatial domain $B_1^+$ maps of the $i$-th and $j$-th coils, now they are interpolated from $L(L+1)/2$ different Fourier transform maps, each of which has underlying spatial $B_1^+$ maps with two sets of spatial interpolators absorbed into them.
-For the $(m,n)$-th element within the element matrix $\mathbf{S}_i^{H}\mathbf{S}_j$, the $L(L+1)/2$ interpolated values were then summed with weights $g_{l_i}(t_m)g_{l_j}(t_n)$, where $l_i$ and $l_j$ are the two segment numbers of the spatial interpolators observed into the corresponding $B_1^+$ maps.
+where the columns of the $\bm{S}_l$ matrix, instead of being the aforementioned k-space sensitivity maps, are now the Fourier transform of the dot products of the spatial $B_1^+$ maps and the spatial interpolatros of the $l$-th segment, shifted to corresponding excitation k-space locations.
+The efficient construction of $\bm{S_{offres}}^{H}\bm{S_{offres}}$ follows the same concept mentioned before. 
+But with off-resonance, for the elements within an element matrix $\bm{S}_i^{H}\bm{S}_j$ in Equation \ref{eq:SHS_blocks}, instead of being interpolated from one densely sampled Fourier transform map, which is of the dot product of the spatial domain $B_1^+$ maps of the $i$-th and $j$-th coils, now they are interpolated from $L(L+1)/2$ different Fourier transform maps, each of which has underlying spatial $B_1^+$ maps with two sets of spatial interpolators absorbed into them.
+For the $(m,n)$-th element within the element matrix $\bm{S}_i^{H}\bm{S}_j$, the $L(L+1)/2$ interpolated values were then summed with weights $g_{l_i}(t_m)g_{l_j}(t_n)$, where $l_i$ and $l_j$ are the two segment numbers of the spatial interpolators observed into the corresponding $B_1^+$ maps.
 Compared to the efficient construction method without off-resonance, taking off-resonance into account increases the total number of FFT operations form $N_c(N_c+1)/2$ to $N_cL(N_cL+1)/2$, and increased the number of interpolations needed for each element from 1 to $L(L+1)/2$.

### 2020-08-17 Manuscript/kPtx_paper.tex
wag edited first section of theory

@@
 \title{k-Space Domain Parallel Transmit Pulse Design}
-\author{Jun Ma$^{1,2}$ and William A. Grissom$^{*1,2}$}
+\author{Jun Ma$^{1,2}$, Bernhard Gruber, Xinqiang Yan$^{1,3}$, and William A. Grissom$^{1,2*}$}
 \maketitle
@@
 $^2$Department of Biomedical Engineering, Vanderbilt University, Nashville, TN, United States\\
+$^3$Department of Radiology and Radiological Sciences, Vanderbilt University, Nashville, TN, United States\\
 

### 2020-08-21 Manuscript/Theory.tex
wag edited through efficient SHS construction

@@
 where $\bm{b}$ is a vector of concatenated multi-channel RF pulses with length $N_t \cdot N_c$, 
-where $N_t$ and $N_c$ are the numbers of time points and coils, respectively,
+where $N_t$ and $N_c$ are the numbers of time points and channels, respectively,
 and $\mathcal{F}(\bm{d})$ is a length-$N_s$ vector containing the 
@@
 In this case, the vector $\bm{w}_j$ is identical to the desired RF. 
-Therefore, the problem of finding the $j$-th column $\bm{w}_j$ of $\bm{W}$ can be restated as the following: 
+Therefore, the problem of finding the $j$-th column $\bm{w}_j$ of $\bm{W}$ can be restated as: 
 what should the RF pulse samples be to generate a unit delta function at the location $\vec{k}_j$ in k-space, 
@@
 where $i$ indexes time points in the pulses' excitation k-space trajectory, 
-and $c$ indexes coils. 
+and $c$ indexes channels. 
 $w_c(\vec{k}_i)$ is the $((c-1)N_t+i)$-th element of the $\bm{w}_j$ vector,
-and $s_c(\vec{k}-\vec{k}_i)$ is the Fourier transform of coil-$c$'s $B_1^+$ map, 
+and $s_c(\vec{k}-\vec{k}_i)$ is the Fourier transform of channel-$c$'s $B_1^+$ map, 
 shifted to be centered at excitation k-space location $\vec{k}_i$. 
@@
 where $\mathbb{N}$ is the set of trajectory points in the vicinity of $\vec{k}_j$. 
-This reduced set of trajectory points reduces the column dimension of $\bm{S}$.
-Since target locations that are distant to $\vec{k}_j$ can also be ignored,
-the row dimension of $\bm{S}$ is also reduced to the size of a smaller neighborhood immediately surrounding $\vec{k}_j$. 
-These reduced problem dimensions further imply that the design matrix $\bm{W}$ is sparse. 
-Figure \ref{fig:Patch}a illustrates a target point $\vec{k}_j$, 
-the nearby points on a spiral trajectory that need to be included in the solution for $\bm{w}_j$,
-and the neighboring target location points where a zero excitation must be enforced. 
-In the following, we define target and trajectory neighborhood sizes, and describe an efficient 
-method to construct the $\bm{S}^{H}\bm{S}$ matrices.
+In this work we define `inclusion width' as the distance, 
+in cycles per excitation field-of-view (cycles/FOV), 
+from each target location $\vec{k}_j$ within which which all trajectory points are accrued into $\mathbb{N}$.
+This reduced set of trajectory points reduces the column dimension of $\bm{S}$
+and both dimensions of $\bm{S}^H\bm{S}$,
+and implies that the design matrix $\bm{W}$ is sparse.
+Figure \ref{fig:Patch}a illustrates a target point $\vec{k}_j$ for a two-dimensional spiral pulse design, 
+and the nearby points on the spiral trajectory that need to be included in the solution for $\bm{w}_j$
+for an inclusion width of 4 cycles/FOV.
 
-\subsection*{Parallelization}
-\par A key advantage of the proposed pulse design formalism is that it can be broken down into many small problems and finely parallelized, because the process of solving each column of $\bm{W}$ is independent of other columns.
-The columns can be solved fully independently, or patchwise for target locations in neighborhoods, wherein all points in the neighborhood share the same $\bm{S}^{H}\bm{S}$ matrix.
+%\par A key advantage of the proposed pulse design formalism is that it can be finely parallelized
+%across the columns of the $\bm{W}$ matrix. 
+\par The $\bm{W}$ matrix columns $\bm{w}_j$ can be solved in parallel one-at-a-time or patch-wise, 
+wherein all target points in a patch share the same $\bm{S}^{H}\bm{S}$ matrix,
+and their $\bm{s}_j^H$ vectors are concatenated in the column dimension
+to form a matrix in Equation \ref{eq:Solution}. 
+An illustration of a $4 \times 4$ patch and its included trajectory points is shown in Figure \ref{fig:Patch}b,
+for a two-dimensional spiral pulse design. 
+The inclusion width is also 4 cycles/FOV from any target point in the patch, 
+%we truncate the $B_1^+$ map Fourier transforms to zero outside a 4 by 4 cycle/FOV square centered at DC. 
+so all the excitation trajectory points within a $12 \times 12$ cycles/FOV square are included in the calculation.
+
+%Since target locations that are distant to $\vec{k}_j$ can also be ignored,
+%the row dimension of $\bm{S}$ is also reduced to the size of a smaller neighborhood immediately surrounding $\vec{k}_j$. 
+%These reduced problem dimensions further imply that the design matrix $\bm{W}$ is sparse. 
+%Figure \ref{fig:Patch}a illustrates a target point $\vec{k}_j$, 
+%the nearby points on a spiral trajectory that need to be included in the solution for $\bm{w}_j$,
+%and the neighboring target location points where a zero excitation must be enforced. 
+%In the following, we define target and trajectory neighborhood sizes, 
+%and describe an efficient method to construct the $\bm{S}^{H}\bm{S}$ matrices.
+
 \begin{figure}
@@
 \end{figure}
-An example of this concept is shown in Figure \ref{fig:Patch}.
-For simplicity of visualization, it is demonstrated in a 2D problem, but the concept is easily extended to 3D.
-The figure depicts the solution of the $\bm{W}$ matrix 16 columns at a time, whose corresponding delta functions live within a patch of width 4 cycle/FOV (yellow points in Figure \ref{fig:Patch}).
-In this instance where the inclusion width is also 4 cycle/FOV, we truncate the $B_1^+$ map Fourier transforms to zero outside a 4 by 4 cycle/FOV square centered at DC.
-As a result, we must consider all the excitation trajectory points within a 12 by 12 cycle/FOV square, which is 4 cycle/FOV extended outside of the patch width 4 square, since they may contribute energy to the target locations corresponding to the 16 $\bm{W}$ matrix columns.
-For a single instance of the 16-point target patch shown in Figure \ref{fig:Patch}, the 46 green points on the excitation trajectory may contribute significant energy and are considered in the weight design.
-Furthermore, we must constrain the total excitation to zero at all k-space locations within a 20 by 20 cycle/FOV red patch in Figure \ref{fig:Patch}.
-This is because any energy deposited at each considered excitation trajectory points will affect not only the target points in the yellow square, but also the whole 2$\times$4 wide patch around that trajectory point.
+
+\subsection*{Efficient $\bm{S}^H\bm{S}$ matrix construction}
+%%which is 4 cycle/FOV extended outside of the patch width 4 square, since they may contribute energy to the target locations corresponding to the 16 $\bm{W}$ matrix columns. 
+%For the patch illustrated in Figure \ref{fig:Patch}, 
+%the 46 green points on the excitation trajectory may contribute significant energy and are considered in the weight design. 
+%Furthermore, we must constrain the total excitation to zero at all k-space locations within a 20 by 20 cycle/FOV red patch in Figure \ref{fig:Patch}. 
+%This is because any energy deposited at each considered excitation trajectory points will affect not only the target points in the yellow square, but also the whole 2$\times$4 wide patch around that trajectory point.
 And the 20 by 20 cycle/FOV red patch is the total of the points that can be affected by all the excitation trajectory points considered in this instance.
 Therefore, in the solution for this instance, $\bm{w}$ is a 46$N_c\times$16 matrix, $\bm{S}$ is a 400$N_c\times$46$N_c$ matrix, $\bm{S}^{H}\bm{S}$ is a 46$N_c\times$46$N_c$ matrix, and $\bm{s}_i^{H}$ is a 46$N_c\times$16 matrix.
-%Since $\bm{s}_i^{H}$ is no longer related to the $i$th row of $\bm{S}$ and $i$th column of $\bm{W}$ only, it will be denoted as $\bm{S_{targ}}$ in later discussions. 
-In the next instance, another 16 columns centered around another 4 points by 4 points patch will be solved.
+%%Since $\bm{s}_i^{H}$ is no longer related to the $i$th row of $\bm{S}$ and $i$th column of $\bm{W}$ only, it will be denoted as $\bm{S_{targ}}$ in later discussions. 
+%In the next instance, another 16 columns centered around another 4 points by 4 points patch will be solved.
 It should be noted that in different instances, the number of neighboring excitation trajectory points (the 46 green points in the previous instance) can vary.
@@
 $N_n$ can be zero when a patch is at the corners where no excitation trajectory point is adjacent.
-%For patches near edges of the excitation k-space FOV, the solution neighborhood and area may wrap back in a circulant shift fashion, depending on the resolution of the final spatial grid on which the user will evaluate the pulse.
+%%For patches near edges of the excitation k-space FOV, the solution neighborhood and area may wrap back in a circulant shift fashion, depending on the resolution of the final spatial grid on which the user will evaluate the pulse.
 In Figure \ref{fig:Patch}), denoted by the red area to the right of Figure \ref{fig:Patch}).
 
-\par The patch width determines the total number of instances to be solved.
+%\par The patch width determines the total number of instances to be solved.
 The inclusion width determines the accuracy of $B_1^+$ information utilized in the design.
@@
 
-\subsection*{Efficient construction of $\bm{S}^{H}\bm{S}$ matrix}
-\par Constructing $\bm{S}^{H}\bm{S}$ by finding $\bm{S}$ is computationally expensive.
-As described previously, the $((c-1)N_c+t)$-th column of the  $\bm{S}$ matrix, $\bm{S}_c(\vec{k}-\vec{k}_t)$, is the k-space sensitivity map of the $c$-th coil $\bm{S}_c(\vec{k})$ shifted to excitation k-space trajectory location $\vec{k}_t$.
-These shifts for each column of $\bm{S}$ are achieved by applying a linear phase modulation to the spatial domain $B_1^+$ map, followed by a fast Fourier transform (FFT).
-This process becomes computationally overwhelming when there are many RF samples, which is often the case.
-Furthermore, the matrix multiplication between $\bm{S}^{H}$ and $\bm{S}$ is also computationally intensive due to the large row dimension of $\bm{S}$ (400$Nt$ in the above example in Figure \ref{fig:Patch}).
-
-\par Inspired by a rapid GRAPPA calibration method for arbitrary 2D/3D non-Cartesian trajectories proposed in Ref \cite{luo2019grappa}, we have developed a fast and memory-efficient algorithm to solve this problem.
-A key innovation of Ref \cite{luo2019grappa} is that the algorithm constructs the Hermitian $\bm{S}^{H}\bm{S}$ matrix directly by finding each of the matrix's lower triangle elements through interpolation, instead of building the $\bm{S}$ matrix explicitly followed by matrix multiplication.
-Conceptually, each element in the Hermitian matrix $\bm{S}^{H}\bm{S}$ is the vector sum of two shifted k-space sensitivity maps, which is also one single point of their convolution.
-With the multiplication property of Fourier transform, this convolution in k-space can be calculated from the Fourier transform of the dot product of the two spatial domain $B_1^+$ maps.
-For a more detailed derivation, please refer to Ref \cite{luo2019grappa}.
-In practice, $\bm{S}^{H}\bm{S}$ is constructed in the following way.
-We first represent the $\bm{S}^{H}\bm{S}$ matrix with block matrices.
-Each block matrix $\bm{S}_i^{H}\bm{S}_j$ is of size $N_n$ by $N_n$, and $\bm{S}_i$ and $\bm{S}_j$ are the columns of $\bm{S}$ related to the k-space sensitivity maps of the $i$-th and $j$-th coils respectively.
-
+%\subsection*{Efficient construction of $\bm{S}^{H}\bm{S}$ matrix}
+\par Constructing the $\bm{S}^{H}\bm{S}$ matrix by first constructing $\bm{S}$ is computationally expensive 
+because it requires each channel's $B_1^+$ map to be shifted to each trajectory location $\vec{k}_i$
+by phase modulation followed by Fourier transform, or by Fourier transform followed by interpolation. 
+Furthermore, 
+the matrix multiplication between $\bm{S}^{H}$ and $\bm{S}$ is also computationally intensive due to the potentially 
+large row dimension of $\bm{S}$, if the zero excitation condition is enforced on a large grid of points around each $\vec{k}_j$.
+The computational costs can be reduced by truncating the $B_1^+$ maps in k-space, 
+but this introduces large errors. 
+Instead, inspired by the rapid GRAPPA calibration method for arbitrary 2D/3D non-Cartesian trajectories of Ref \cite{luo2019grappa}, 
+we propose to construct the Hermitian $\bm{S}^{H}\bm{S}$ matrix directly via interpolation of the Fourier transforms
+of inner products of pairs of $B_1^+$ maps. 
+The $\bm{S}^H\bm{S}$ matrix can be written in block form as:
 \begin{equation}\label{eq:SHS_blocks}
@@
 \bm{S}_{N_c}^{H}\bm{S}_1 & \cdots & \bm{S}_{N_c}^{H}\bm{S}_{N_c} 
-\end{pmatrix}
+\end{pmatrix}, 
 \end{equation}
+where each sub-matrix $\bm{S}_i^H\bm{S}_j$ contains inner products of the Fourier transforms of channel $i$ and channel $j$'s 
+$B_1^+$ maps, after they are shifted to be centered different points on the excitation trajectory corresponding to the row 
+and column indices of the sub-matrix.
+These inner products can be calculated by interpolating the Fourier transform of the inner product of 
+channel $i$ and channel $j$'s $B_1^+$ maps. 
+In other words, each element in the Hermitian matrix $\bm{S}_i^{H}\bm{S}_j$ 
+is the vector sum of channel $i$ and channel $j$'s shifted k-space $B_1^+$ maps, 
+which is also a single point of their k-space convolution. 
+Via the multiplication property of the Fourier transform, 
+this convolution in k-space can be calculated from the Fourier transform of the dot product of the two spatial domain $B_1^+$ maps. 
+For further details, please refer to Ref. \cite{luo2019grappa}.
+%In practice, $\bm{S}^{H}\bm{S}$ is constructed in the following way. 
+%We first represent the $\bm{S}^{H}\bm{S}$ matrix with block matrices.
+Each block matrix $\bm{S}_i^{H}\bm{S}_j$ is of size $N_n$ by $N_n$, and $\bm{S}_i$ and $\bm{S}_j$ are the columns of $\bm{S}$ related to the k-space sensitivity maps of the $i$-th and $j$-th coils respectively.
 
-Since $\bm{S}^{H}\bm{S}$ is Hermitian, we only need to find the values within the lower triangle of the matrix, which are the lower triangle blocks $\bm{S}_i^{H}\bm{S}_j$ with $i>j$.
-For a given lower triangle block $\bm{S}_i^{H}\bm{S}_j$  ($i>j$), all of its elements are interpolated from the densely sampled Fourier transform of the dot product of the spatial domain $B_1^+$ maps of the $i$-th and $j$-th coils.
-The $(m,n)$-th element is the value interpolated at $(\vec{k}_m-\vec{k}_n)$ away from DC.
-Therefore, to solve all the columns of $\bm{W}$, the total number of FFT operations needed in this efficient method is only $N_c(N_c+1)/2$, instead of ${N_t}{N_c}$, and the storage size is also much smaller.
-In addition to the efficiency related to FFT, this algorithm saves a large matrix multiplication between $\bm{S}^{H}$ and $\bm{S}$ for the solving of every single column of $\bm{W}$.
-Although an alternative strategy of determining each column of $\bm{S}$ explicitly by interpolating the $N_s$ sample points from unshifted $B_1^+$ Fourier transforms can also reduce the number of FFT operations, it still has the problem of large multiplications between $\bm{S}^{H}$ and $\bm{S}$ matrices.
-Furthermore, to calculate each element of $\bm{S}^{H}\bm{S}$, there are $2N_s$ number of interpolations involved with this sub-optimal strategy.
+\par Since $\bm{S}^{H}\bm{S}$ and its sub-matrices are Hermitian, 
+we only need to find the values within the lower triangle of the matrix, 
+which are the sub-matrices $\bm{S}_i^{H}\bm{S}_j$ with $i>j$ that are themselves lower triangular. 
+The elements of a given sub-matrix $\bm{S}_i^{H}\bm{S}_j$ 
+are interpolated from a densely sampled Fourier transform of the dot product of the spatial domain $B_1^+$ maps of the $i$-th and $j$-th channels. 
+The $(m,n)$-th element is the value interpolated at a position $\vec{k}_m-\vec{k}_n$ away from DC,
+where $\vec{k}_m$ and $\vec{k}_n$ are the excitation k-space trajectory locations corresponding to row $m$ and column $n$.
+Compared to phase-modulating and Fourier transforming each channel's $B_1^+$ map for each point 
+on the trajectory which would require $N_t \cdot N_c$ Fourier transforms,
+to solve all the columns of $\bm{W}$ the total number of Fourier transforms needed in this efficient method is $N_c(N_c+1)/2$. 
+The storage size is also much smaller, 
+and the potentially large matrix multiplication between $\bm{S}^H$ and $\bm{S}$ is avoided.
+An alternative strategy would be to construct $\bm{S}$ by Fourier transforming each channel's $B_1^+$ map 
+and then interpolating it to be centered at each trajectory location, 
+but this again requires multiplication of the $\bm{S}^{H}$ and $\bm{S}$ matrices,
+which further involves the multiplication of interpolated values. 
+We have found empirically that this strategy introduces higher error
+than interpolating inner product values. 
+%Furthermore, to calculate each element of $\bm{S}^{H}\bm{S}$, there are $2N_s$ number of interpolations involved with this sub-optimal strategy.
 While with the efficient algorithm there is only one interpolation from the densely sampled Fourier Transform of the dot product of two spatial domain $B_1^+$ maps needed.

### 2020-08-21 Manuscript/kPtx_paper.tex
wag edited through efficient SHS construction

--- 2020-08-17 Manuscript/kPtx_paper.tex
@@
 \title{k-Space Domain Parallel Transmit Pulse Design}
-\author{Jun Ma$^{1,2}$ and William A. Grissom$^{*1,2}$}
+\author{Jun Ma$^{1,2}$, Bernhard Gruber$^{3,4}$, Xinqiang Yan$^{1,5}$, and William A. Grissom$^{1,2,5*}$}
 \maketitle
@@
 $^2$Department of Biomedical Engineering, Vanderbilt University, Nashville, TN, United States\\
+$^3$A. A. Martinos Center for Biomedical Imaging, Massachusetts General Hospital, Harvard Medical School, Charlestown, MA, United States\\
+$^4$Division MR Physics, Center for Medical Physics and Biomedical Engineering, Medical University Vienna, Vienna, Austria\\
+$^5$Department of Radiology and Radiological Sciences, Vanderbilt University, Nashville, TN, United States\\
 

### 2020-08-24 Manuscript/Theory.tex
wag edited through off-resonace

@@
 \end{equation}
-where $\bm{b}$ is a vector of concatenated multi-channel RF pulses with length $N_t \cdot N_c$, 
+where $\bm{b}$ is a vector of concatenated multi-channel RF pulses with length $N_t  N_c$, 
 where $N_t$ and $N_c$ are the numbers of time points and channels, respectively,
@@
 Fourier transform of the desired k-space excitation pattern $\bm{d}$.
-$\bm{W}$ has dimensions $N_t \cdot N_c \times N_s$.
+$\bm{W}$ has dimensions $N_t  N_c \times N_s$.
 Once the entries of $\bm{W}$ are computed, 
@@
 \end{equation}
-where $\bm{S}$ is a $N_s \times N_c \cdot N_t$ 
+where $\bm{S}$ is a $N_s \times N_c  N_t$ 
 matrix containing values of $s_c(\vec{k}-\vec{k}_i)$ for all $c$ and $i$,
@@
 Compared to phase-modulating and Fourier transforming each channel's $B_1^+$ map for each point 
-on the trajectory which would require $N_t \cdot N_c$ Fourier transforms,
+on the trajectory which would require $N_t  N_c$ Fourier transforms,
 to solve all the columns of $\bm{W}$ the total number of Fourier transforms needed in this efficient method is $N_c(N_c+1)/2$. 
@@
 We have found empirically that this strategy introduces higher error
-than interpolating inner product values. 
+than interpolating the inner product values. 
 %Furthermore, to calculate each element of $\bm{S}^{H}\bm{S}$, there are $2N_s$ number of interpolations involved with this sub-optimal strategy.
@@
 
-\subsection*{ Off-Resonance correction}
-%\par As shown in Equation \ref{eq:SpatialDomainEquation} when we introduced spatial domain design in Chapter \ref{chap:SpatialDesign}, the equation connecting a pTx pulse to its excitation pattern has an off-resonance dependent term
-$e^{\imath \gamma \Delta B_0(\bm{x})(t-T)}$. 
-In order to model the off-resonance into our k-space domain design, we adapted a fast implementation of the off-resonance compensation with time segmentation approximation and weighted least-squares interpolators \cite{fessler2005toeplitz}.
-By segmenting the RF pulse into multiple segments, this method disentangles the space-and-time dependent phase accrual induced by main field inhomogeneity into either space- or time- dependent terms, and therefore a same system matrix can be applied within each segment.
-Mathematically, it is
-\begin{equation*}
-e^{\imath \Delta\omega_j (t_i-T) }\approx\sum_{l=1}^{L} g_{l}(t_i) e^{\imath \theta_{l}(\Delta\omega_j)}
-\end{equation*}
-where $i=1\dots Nt$ indexes the RF samples, $j=1\dots Ns$ indexes the spatial locations, and $l$ indexes the time segments.
-The left term is the problematic space-and-time dependent term, with $\Delta\omega_j$ representing the off-resonance at the location-$j$ obtained from a field map and $T$ being the pulse duration.
-$g_{il}=b_{l}(t_i)$ are the time-dependent-only weights called temporal interpolators applied upon RF samples.
-$h_{lj}=e^{\imath \theta_{l}(\Delta\omega_j)}$ are the space-dependent-only phase accrual called spatial interpolators, applied upon the excitation pattern of each weighted RF segment.
-Therefore, the spatial domain formulation becomes
-\begin{equation*}
-\bm{d}=\sum_{l=1}^{L}diag\{\bm{h}_l\}\bm{A}(diag\{\bm{g}_l\}\bm{b})
-\end{equation*}
-The spatial interpolators can be absorbed into the sensitivity maps. The $\bm{S}$ matrix in Equation \ref{eq:MatrixForm} will then become 
-\begin{equation*}
-\bm{S_{offres}}=\sum_{l=1}^{L}\bm{S}_l diag\{\bm{g}_l\}
-\end{equation*}
-where the columns of the $\bm{S}_l$ matrix, instead of being the aforementioned k-space sensitivity maps, are now the Fourier transform of the dot products of the spatial $B_1^+$ maps and the spatial interpolatros of the $l$-th segment, shifted to corresponding excitation k-space locations.
-The efficient construction of $\bm{S_{offres}}^{H}\bm{S_{offres}}$ follows the same concept mentioned before. 
-But with off-resonance, for the elements within an element matrix $\bm{S}_i^{H}\bm{S}_j$ in Equation \ref{eq:SHS_blocks}, instead of being interpolated from one densely sampled Fourier transform map, which is of the dot product of the spatial domain $B_1^+$ maps of the $i$-th and $j$-th coils, now they are interpolated from $L(L+1)/2$ different Fourier transform maps, each of which has underlying spatial $B_1^+$ maps with two sets of spatial interpolators absorbed into them.
-For the $(m,n)$-th element within the element matrix $\bm{S}_i^{H}\bm{S}_j$, the $L(L+1)/2$ interpolated values were then summed with weights $g_{l_i}(t_m)g_{l_j}(t_n)$, where $l_i$ and $l_j$ are the two segment numbers of the spatial interpolators observed into the corresponding $B_1^+$ maps.
-Compared to the efficient construction method without off-resonance, taking off-resonance into account increases the total number of FFT operations form $N_c(N_c+1)/2$ to $N_cL(N_cL+1)/2$, and increased the number of interpolations needed for each element from 1 to $L(L+1)/2$.
+\subsection*{Off-Resonance Compensation}
+% In order to model the off-resonance into our k-space domain design, we adapted a fast implementation of the off-resonance compensation with time segmentation approximation and weighted least-squares interpolators \cite{fessler2005toeplitz}.
+Off-resonance compensation is common in spatial-domain parallel pulse designs \cite{Grissom:2006:MRM}, 
+but has not been previously implemented in a k-space-domain design.
+Spatial domain designs based on non-uniform fast Fourier transforms make use of an approximate time-segmented
+model for the off-resonance term \cite{fessler2005toeplitz},
+which decouples the space- and time-dependence of off-resonant phase accrual into the product of 
+space- and time-dependent terms, which are applied on either side of the non-uniform fast Fourier transform operator. 
+Here we show that a time-segmented off-resonance model can be incorporated in the proposed k-space-domain algorithm. 
+Mathematically, the time-segmented model is given by:
+\begin{equation}
+e^{\imath \Delta\omega_j (t_i-T) }\approx\sum_{l=1}^{L} g_l(t_i) e^{\imath \Delta\omega_j \breve{t}_l},
+\end{equation}
+where $\Delta\omega_j$ is the off-resonance frequency at location $\vec{x}_j$, 
+$i$ indexes time points in the pulse, 
+$T$ is the pulse duration,
+and $l$ indexes the $L$ time segments, where $L$ is typically between 4 and 8. 
+$g_{il}=b_{l}(t_i)$ are the temporal interpolators that multiply into the RF samples,
+and $h_{lj}=e^{\imath \Delta\omega_j\breve{t}_l}$ are the off-resonance phase shifts 
+applied to the excitation patterns produced by the RF pulse time segments centered at time points $\{\breve{t}_l: l = 1, \dots, L\}$.
+We can incorporate the time-segmented off-resonance model into Equation \ref{eq:ScalerForm} as:
+\begin{equation}
+	\delta(\vec{k}-\vec{k}_j)=\sum_{l = 1}^L \sum_{i=1}^{N_t}\sum_{c=1}^{N_c} w_c(\vec{k}_i) g_l(t_i) \tilde{s}_{cl} (\vec{k}-\vec{k}_i), 
+\end{equation}
+where $\tilde{s}_{cl}(\vec{k})$ is the Fourier transform of the product of channel $c$'s $B_1^+$ map and time segment $l$'s 
+off-resonance phase exponential. 
+We can then write the equivalent of Equation \ref{eq:MatrixForm} with the off-resonance model:
+\begin{equation}
+	\sum_{l=1}^L \bm{S}_l \textrm{diag}(g_{il}) \bm{w}_j = \bm{\delta}_j,
+\end{equation} 
+where the matrix $\bm{S}_l$ is now formed from the $N_c  L$ Fourier transforms of the $B_1^+$ map and off-resonance
+phase exponential products.  
+Efficient construction of the $\bm{S}^{H}\bm{S}$ matrix follows much the same procedure as without
+off-resonance except that with off-resonance,
+the elements of each sub-matrix $\bm{S}_i^{H}\bm{S}_j$ in Equation \ref{eq:SHS_blocks}
+are interpolated from $L(L+1)/2$ Fourier transformed maps,
+and the interpolated values are weighted by the temporal interpolators for each pair of multiplied time segments before they 
+are summed.
+Compared to constructing $\bm{S}^H\bm{S}$ without off-resonance, 
+taking off-resonance into account increases the total number of FFT operations form $N_c(N_c+1)/2$ to $N_cL(N_cL+1)/2$, 
+and increases the number of interpolations needed for each sub-matrix element from 1 to $L(L+1)/2$.  
+However, we note that only adjacent time segments with overlapping temporal interpolators at a given time point
+need to be considered when calculating the elements of $\bm{S}^H\bm{S}$ corresponding to that time point.

### 2020-08-31 Manuscript/Theory.tex
wag theory fig 1 edits

@@
 \begin{equation}\label{eq:ScalerForm}
-\delta(\vec{k}-\vec{k}_j)=\sum_{i=1}^{N_t}\sum_{c=1}^{N_c} w_c(\vec{k}_i) s_c(\vec{k}-\vec{k}_i)
+\delta(\vec{k}-\vec{k}_j)=\sum_{i=1}^{N_t}\sum_{c=1}^{N_c} w_c(\vec{k}_i) s_c(\vec{k}-\vec{k}_i),
 \end{equation}
@@
 all other trajectory points can be ignored.
-This means we can modify Equation \ref{eq:ScalerForm} to:
+This means Equation \ref{eq:ScalerForm} can be modified to:
 \begin{equation}
@@
 where $\mathbb{N}$ is the set of trajectory points in the vicinity of $\vec{k}_j$. 
-In this work we define `inclusion width' as the distance, 
+In this work `inclusion width' is defined as the distance, 
 in cycles per excitation field-of-view (cycles/FOV), 
@@
 and implies that the design matrix $\bm{W}$ is sparse.
-Figure \ref{fig:Patch}a illustrates a target point $\vec{k}_j$ for a two-dimensional spiral pulse design, 
-and the nearby points on the spiral trajectory that need to be included in the solution for $\bm{w}_j$
+Figure \ref{fig:Patch}a illustrates a target point $\vec{k}_j$ for a two-dimensional pulse design, 
+and the nearby points on the trajectory that need to be included in the solution for $\bm{w}_j$
 for an inclusion width of 4 cycles/FOV.
@@
 	\centering
-	\includegraphics[width=6cm]{kspace_PTX_Patch}
-	\caption{\textcolor{red}{WAG: I think you should make two subfigures here: one that illustrates a single target location, and one that illustrates a patch of target locations.
-Also you should annotate the different widths, in the figures, with arrows.
-Also add a legend for the dots}
-	Illustration of one instance within the palatalization of a 2D k-space domain design problem.
-The totally design problem is divided into patches of width 4 cycle/FOV, and the 16 yellow points are the target points in this instance.
-With inclusion width of 4 cycle/FOV, the 46 green excitation trajectory points within the 12 cycle/FOV wide green square (4 cycle/FOV extended outside of the patch) are considered in this instance.
-The excitation within the 20 cycle/FOV wide red patch is constrained to zero except the point where the delta function is.}
+	\includegraphics[width=\textwidth]{kspace_PTX_Patch}
+	\caption{(a) A target point $\vec{k}_j$ and the nearby trajectory points that are included when calculating 
+	RF pulse weight contributions from this point.
+	Inclusion width is defined as the distance from each target location $\vec{k}_j$ within which 
+	which all trajectory points are considered when solving for the $j$-th column of the design ($\bm{W}$) matrix.
+	(b) Calculation of the $\bm{W}$ matrix can be performed column-by-column for each target location $\vec{k}_j$,
+	or patches of target points can be solved for jointly. 
+	Here the 16 columns of $\bm{W}$ for a 4 $\times$ 4 patch of target points are solved together,
+	and an inclusion width of 4 cycles/FOV dictates that all trajectory points within a 12 $\times$ 12 region
+	centered on the patch are considered in the calculation.}
 	\label{fig:Patch}
@@
 applied to the excitation patterns produced by the RF pulse time segments centered at time points $\{\breve{t}_l: l = 1, \dots, L\}$.
-We can incorporate the time-segmented off-resonance model into Equation \ref{eq:ScalerForm} as:
+The time-segmented off-resonance model can be incorporated into Equation \ref{eq:ScalerForm} as:
 \begin{equation}

### 2020-09-01 Manuscript/Method.tex
edited wording
change method and result according to new figures

@@
 	\includegraphics[width=3cm]{kspace_PTX_Coil}
-	\caption{24-channel loop Tx array. The array has diameter 32 cm and height 28 cm. The 16 cm $times$ 11 cm loops are arranged in 3 rows of 8.}
+	\caption{24-channel loop Tx array. The array has diameter 32 cm and height 28 cm. The 16 cm $\times$ 11 cm loops are arranged in 3 rows of 8.}
 	\label{fig:Coil}
@@
 The resulted pulses were evaluated against the target pattern with the 128$\times$128$\times$96 grid in order to expose Gibbs ringing.
-The normalized root-mean-square error (NRMS) was calculated against the voxels within the cerebrum.
+The excited transverse spins were simulated through Bloch simulation and the magnitude root-mean-square error (RMSE) was calculated against the voxels within the cerebrum, except for an $\approx$5 mm thick transition band.
 
@@
 The computation was done on a computer with a 512 GB RAM and two 24-core 2.1 GHz Intel Xeon CPUs which provides maximum 94 threads.
-For each design case, the computation was run 5 times, and the mean computation time and the NRMSE were recorded.
+For each design case, the computation was run 5 times, and the mean computation time and the RMSE were recorded.
 
@@
 The k-space domain design method's performance regarding k-space undersampling, which is desired for shorter pulse duration, was also examined and compared against the spatial domain design.
-The undersampling was achieved by reducing the numbers of the previously specified SPIN trajectory's polar and azimuthal rotations proportionally by a factor called acceleration factor, as shown in the third row of Figure \ref{fig:kspace_PTX_Acceleration}.
+The undersampling was achieved by reducing the numbers of the previously specified SPIN trajectory's polar and azimuthal rotations proportionally by a factor called reduction factor, as shown in the third row of Figure \ref{fig:kspace_PTX_Acceleration}.
 
@@
 We incorporated a normalized field map with Gaussian inhomogeneity centered above the frontal sinus (Figure \ref{fig:kspace_PTX_B0}a), mimicking a characteristic susceptibility induced $B_0$ inhomogeneity.
-The field maps were than scaled so that the maximum off-resonance reached +100 Hz, +200 Hz, and +300 Hz.
+The field maps were than scaled so that the maximum off-resonance reached +200 Hz and +400 Hz.
 Off-resonance corrected spatial domain designs were done with system matrices whose field maps were also incorporated through time segmentation approximation \cite{fessler2005toeplitz}.
-k-space domain design were done with or without off-resonance correction.
+K-space domain designs were done with or without off-resonance correction.

### 2020-09-01 Manuscript/Result.tex
Changed figures
change method and result according to new figures

@@
 	\centering
-	\includegraphics[width=\textwidth]{kspace_PTX_ComputationTime}
+	\includegraphics[width=\textwidth]{ComputationTime_2}
 	\caption{\textcolor{red}{WAG: Can you also run $2^0$ (most importantly) and $2^5$ patch width here?
-It would be good to show that the NRMSE levels off at some point.
-Also can you change the NRMSE axis to go from 0 to 6?
+It would be good to show that the RMSE levels off at some point.
+Also can you change the RMSE axis to go from 0 to 6?
 That will help emphasize that even though the error is decreasing with increasing patch width,
@@
 Patch width and inclusion with were kept at 4 cycle/FOV.
-\textbf{(b\&c)} Computation time (blue axis) and NRMSE (red axis) vs.
+\textbf{(b\&c)} Computation time (blue axis) and RMSE (red axis) vs.
 patch widths (b) and inclusion widths (c).
@@
 The thread number was conservatively chosen to be 16 for the following studies to ensure timely solutions.
-Figure \ref{fig:ComputationTime}b shows the mean computation time and the NRMSE with different patch widths.
-The computation time increases and the NRMSE decreases as the patch width increases.
+Figure \ref{fig:ComputationTime}b shows the mean computation time and the RMSE with different patch widths.
+The computation time increases and the RMSE decreases as the patch width increases.
 This was because when patch width increases, there are more excitation trajectory points included in one instance problem, even with the same inclusion width.
@@
 Here, we chose patch widths 4 and 8 (labeled $2^2$ and $2^3$) to balance time and accuracy for further evaluation.
-Figure \ref{fig:ComputationTime}c shows the mean computation time and the NRMSE with different inclusion widths.
+Figure \ref{fig:ComputationTime}c shows the mean computation time and the RMSE with different inclusion widths.
 The solid lines and dashed lines were obtained with patch width 4 and 8, respectively.
@@
 	\centering
-	\includegraphics[width=\textwidth]{kspace_PTX_ErrorMap2}
+	\includegraphics[width=\textwidth]{ErrorMap_2}
 	\caption{\textcolor{red}{WAG: I think this is the figure that your example in Github should replicate.}
-	Normalized excitation patterns (top row) and error maps (bottom row) for k-space domain design (left column) and spatial domain design (right column), with NRMSE and design time indicated.}
+	Normalized excitation patterns (top row) and error maps (bottom row) for k-space domain design (left column) and spatial domain design (right column), with RMSE and design time indicated.}
 	\label{fig:ErrorMap}
 \end{figure}
-The normalized excitation patterns and error maps are shown in Fig \ref{fig:ErrorMap} for both k-space domain design (left) and spatial domain design (right), where the k-space domain design was solved with 16 parallel computing threads, patch width 4, and inclusion width 4.
+The simulated excitation patterns and error maps are shown in Fig \ref{fig:ErrorMap} for both k-space domain design (left) and spatial domain design (right), where the k-space domain design was solved with 16 parallel computing threads, patch width 4, and inclusion width 4.
 Both designs were done with the 64$\times$64$\times$48 grid size (3mm iso-resolution), and the excitation patterns were evaluated against the target pattern with the 128$\times$128$\times$96 grid size (1.5mm iso-resolution).
 grid size.
-The calculated NRMSE from the k-space domain design and the spatial domain design were 5.02\% and 4.94\%, respectively, which were practically equal.
+The calculated RMSE from the k-space domain design and the spatial domain design were 2.42\% and 2.68\%, respectively, which were practically equal.
 For both design methods, most of the errors appeared at the edges of the transition band, with other errors lower than 5\% of the target flip angle.
@@
 	\centering
-	\includegraphics[width=\textwidth]{kspace_PTX_GibbsRinging}
-	\caption{Normalized error maps and NRMSE for \textbf{(a)} spatial domain design and \textbf{(c)} k-space domain design with 6 mm iso-resolution, 32$\times$32$\times$24 design grid.
+	\includegraphics[width=\textwidth]{GibbsRinging_3}
+	\caption{Normalized error maps and RMSE for \textbf{(a)} spatial domain design and \textbf{(c)} k-space domain design with 6 mm iso-resolution, 32$\times$32$\times$24 design grid.
 Red arrows indicate the Gibbs ringing in low-resolution spatial domain design.
@@
 	\centering
-	\includegraphics[width=\textwidth]{kspace_PTX_Acceleration}
+	\includegraphics[width=\textwidth]{Acceleration_3}
 	\caption{ \textcolor{red}{We should talk about this; I don't think reviewers will like the fact that the scale starts at 0.2. Also we should probably call it `Reduction Factor' since it is 
 	really the factor by which the pulse duration is reduced, and not exactly a k-space undersampling factor, is that right?}
-	Normalized error maps and RMSE for spatial domain design (first row) and k-space domain design (second row), with excitation trajectories undersampled by different acceleration factors (third row).}
+	Normalized error maps and RMSE for spatial domain design (first row) and k-space domain design (second row), with excitation trajectories undersampled by different reduction factors (third row).}
 	\label{fig:kspace_PTX_Acceleration}
@@
 
-Figure \ref{fig:kspace_PTX_Acceleration} shows a comparison between the performance of spatial domain design (first row) and k-space domain design (second row) regarding undersampled excitation trajectories (third row) with different acceleration factors.
+Figure \ref{fig:kspace_PTX_Acceleration} shows a comparison between the performance of spatial domain design (first row) and k-space domain design (second row) regarding undersampled excitation trajectories (third row) with different reduction factors.
 Both design methods had larger errors when the excitation k-space was less densely traversed.
-The k-space domain design provided similar error maps and practically equal NRMSE.
-The k-space domain design had slightly larger NRMSE because of the interpolation and truncation of the k-space sensitivity when building the $\mathbf{S}^{H}\mathbf{S}$ matrix, and can be improved by increasing the inclusion width.
+The k-space domain design provided similar error maps and practically equal RMSE.
+The k-space domain design had slightly larger RMSE because of the interpolation and truncation of the k-space sensitivity when building the $\mathbf{S}^{H}\mathbf{S}$ matrix, and can be improved by increasing the inclusion width.
 
@@
 As shown in the second row of Figure \ref{fig:kspace_PTX_B0}b, off-resonance caused false excitation outside the designated suppression region, and must be corrected.
-k-space domain design with correction was able to correct off-resonance artifacts and provide excitation patterns comparable to spatial domain design, for maximum off-resonance up to 200 Hz, which is the typical range of off-resonance observed in clinical studies.
+With 200 Hz maximum off-resonance, which is the typical range of off-resonance observed in clinical studies, k-space domain design with correction was able to fully correct the off-resonance artifacts.
+It was also able to provide excitation pattern comparable to spatial domain design with 400 Hz maximum off-resonance.
 The k-space domain design has a weaker performance with higher off-resonance due to the fact that the time segmentation approximation in Ref \cite{fessler2005toeplitz} was meant to approximate forward models from RF to excitation patterns and does not serve as an accurate approximation to the backward model as we need in the k-space domain design.

### 2020-09-05 Manuscript/Method.tex
WAG done with Methods

@@
 \section*{Methods}
-RF pulses were designed for the 24-channel loop transmit array (Figure \ref{fig:Coil}) that will be built for the MRCoG scanner  and compressed to 16 channels using array compressed parallel transmission \cite{cao2016array}.
-$B_1^+$ maps used in the pulse design were simulated in a human head model using Ansys High Frequency Structure Simulator (Canonsburg, PA, USA) with 1.5 mm isotropic resolution.
-A SPINS  trajectory \cite{malik2012tailored} (Figure \ref{fig:Target}a\&b) with 5 mm max resolution was empirically designed for the pulse.
-The gradient duration was minimized to 10 ms through time-optimal design \cite{lustig2008fast} subject to the proposed MRCoG scanner’s gradient amplitude and slew rate constraints of 200 mT/m and 700T/m/s, respectively.
+\subsection*{Design and Simulation Setup}
+Simulations were performed to validate and characterize the proposed k-space domain parallel transmit pulse design method,
+with comparisons to the spatial-domain method of Ref. \cite{Grissom:2006:MRM}.
+RF pulses were designed for a simulated 24-channel loop transmit array (Figure \ref{fig:Coil}) that is under construction for a 7 Tesla scanner optimized
+for imaging the human cortex.  
+24-channel complex-valued $B_1^+$ maps used in the pulse designs were simulated in a male human head model using 
+Ansys High Frequency Structure Simulator (Canonsburg, PA, USA) with 1.5 mm isotropic resolution. 
+All pulse designs used a SPINS excitation k-space trajectory \cite{malik2012tailored} (Figures \ref{fig:Target}b\&c) with 5 mm max resolution. 
+The SPINS trajectories were first designed analytically and the final gradient and excitation k-space trajectories were designed from them 
+using the minimum-time gradient waveform design method \cite{lustig2008fast}, 
+for a 15 {\textmu}s dwell time and subject to the scanner's gradient amplitude and slew rate constraints of 200 mT/m and 700 T/m/s, respectively. 
+The SPINS trajectory comprised three segments, with radii ranging between 1-0.625, 0.625-0.375, and 0.375-0 /cm, respectively.
+The number of polar and azimuthal rotations were 15.5/2.125, 20.66/2.833, 15.5/2.125, respectively, for each segment.
+The durations the segments after minimum-time gradient design were 4.174, 4.326, and 1.5 ms, respectively.
+With the exception of the simulations across undersampling factors, all pulse designs used the 10 ms trajectory shown in Figures \ref{fig:Target}b\&c.
 
@@
 	\centering
-	\includegraphics[width=3cm]{kspace_PTX_Coil}
-	\caption{24-channel loop Tx array. The array has diameter 32 cm and height 28 cm. The 16 cm $\times$ 11 cm loops are arranged in 3 rows of 8.}
+	\includegraphics[width=6cm]{kspace_PTX_Coil}
+	\caption{The 24-channel loop Tx array that was simulated in a human head model to obtain $B_1^+$ maps. 
+	The array has diameter 32 cm and height 28 cm. The 16 cm $\times$ 11 cm rectangular loops are arranged in 3 rows of 8.}
 	\label{fig:Coil}
@@
 	\includegraphics[width=\textwidth]{kSpace_PTX_Pattern_Trajectory}
-	\caption{(a) Target excitation pattern for the IVS pulses. (b) 10 ms SPIN trajectory used in the designs. (c) Gradient waveforms of the excitation trajectory.}
+	\caption{(a) Middle axial, sagittal, and coronal slices of the target excitation pattern used for all pulse designs. 
+	(b) The SPINS trajectory used in the designs. 
+	(c) 10 ms minimum-time gradient waveforms that produce the SPINS trajectory.}
 	\label{fig:Target}
 \end{figure}
-Figure \ref{fig:Target}a shows the target pattern for the pulse design shaped as an ellipse centered on the ventricles with AP/HF/LR semi-axes of 4.8/3.2/3.2 cm.
-The target pattern was smoothed by a Fermi filter.
+
+\par Figure \ref{fig:Target}a shows the target pattern for all pulse designs which comprised an ellipse centered on the ventricles with AP/HF/LR semi-axes of 4.8/3.2/3.2 cm.
+The pattern was smoothed by a Fermi filter that was applied in the frequency domain to match the target pattern's effective resolution to the excitation k-space trajectory's 5 mm resolution.
+This choice of target pattern was motivated by imaging applications for the 7 Tesla scanner 
+in which midbrain signals will be saturated for high-resolution, highly-accelerated imaging of the cortex. 
 Pulses were designed to excite the entire ellipse and achieve zero excitation in voxels in the cerebrum but outside the ellipse. 
-Both the smoothed target pattern and the $B_1^+$ maps were undersampled from 128$\times$128$\times$96 grids (1.5mm iso-resolution) into 64$\times$64$\times$48 grids (3mm iso-resolution).
-The RF designs were done with the 64$\times$64$\times$48 grid size.
-The resulted pulses were evaluated against the target pattern with the 128$\times$128$\times$96 grid in order to expose Gibbs ringing.
-The excited transverse spins were simulated through Bloch simulation and the magnitude root-mean-square error (RMSE) was calculated against the voxels within the cerebrum, except for an $\approx$5 mm thick transition band.
+The smoothed target pattern and the $B_1^+$ maps were downsampled from their original 128$\times$128$\times$96 grids (1.5 mm isotropic resolution) to 
+64$\times$64$\times$48 grids (3 mm isotropic resolution),
+and RF designs were performed with the 64$\times$64$\times$48 grid size. 
+All pulse designs and simulations were performed in MATLAB (Mathworks, Natick, MA, USA).
+For spatial domain designs, 
+RF pulses were solved using an iterative least-squares conjugate-gradient descent method \cite{Grissom:2006:MRM} with 35 iterations,
+which was accelerated by non-uniform fast Fourier transforms \cite{Fessler:2003fk}. 
+The proposed k-space domain algorithm was implemented based on code for the non-Cartesian GRAPPA method of Ref. \cite{luo2019grappa},
+as a function that takes as input the $B_1^+$ maps, 
+a normalized excitation k-space trajectory, and optional off-resonance and design parameters. 
+Within that function the Fourier transforms of the $B_1^+$ products are calculated,
+and a C-based MEX function is invoked to solve for the non-zero elements of each column of $\bm{W}$. 
+Those elements are then inserted into a sparse $\bm{W}$ matrix, which is the single output of the main function. 
+Parallelization was implemented across patches within the C-based MEX function using OpenMP. 
+The final pulses are calculated by multiplying the sparse $\bm{W}$ matrix into the Fourier transform of the target pattern. 
+This code, the $B_1^+$ maps, and a demo script are available at https://github.com/wgrissom/kpTx. 
+All pulse designs were performed on a server (Colfax International, Santa Clara, CA, USA) 
+with 512 GB RAM and two 24-core 2.1 GHz Intel Xeon CPUs which provide up to 94 threads (Intel Corporation, Santa Clara, CA, USA). 
+Designs were performed five times for each case, and the mean computation time was recorded.
+For the k-space domain designs, the design time comprised the time to compute the sparse $\bm{W}$ matrix, 
+and the time to multiply it into the target pattern to obtain the pulses.
+The resulting pulses were Bloch equation-simulated and compared to the target pattern on the finer 128$\times$128$\times$96 grid to capture Gibbs ringing. 
+When calculating excitation errors, the magnitude root-mean-square error (RMSE) was calculated in voxels within the cerebrum,
+except for an $\approx$5 mm-thick transition band around the edge of the elliptical target region.
 
-With conventional spatial domain design, RF pulses were solved using an iterative least-squares conjugate-gradient decent method \cite{Grissom:2006:MRM}.
-With the proposed k-space domain design, RF pulses were solved with different parallelization parameters: thread number, patch width, and inclusion width.
-In order to study the computational acceleration provided by parallel computing, the design problem was solved with thread numbers ranging from 1 to 32, while the patch width and inclusion width were both set to 4.
-In order to study the computation time and error with respect to different patch widths and inclusion widths, we then held the computing threads constant at 16 while varying the patch and inclusion widths.
-The computation was done on a computer with a 512 GB RAM and two 24-core 2.1 GHz Intel Xeon CPUs which provides maximum 94 threads.
-For each design case, the computation was run 5 times, and the mean computation time and the RMSE were recorded.
+\subsection*{k-Space Algorithm Parameters}
+To evaluate how accuracy and compute time depend on k-space-domain design parameters and parallelization,
+pulse designs were done across numbers of threads (i.e., how many patches were solved simultaneously; 1 to 32), 
+patch widths (1 to 16 cycles/FOV), and inclusion widths (2 to 8 cycles/FOV). 
+The number of threads were varied while holding the patch width and inclusion width both at 4 cycles/FOV.
+The patch width was varied while holding the number of threads at 16, and the inclusion width at 4,
+and the inclusion width was varied while holding the number of threads at 16, and the patch width at 4 and 8.
 
-In order to demonstrate the k-space domain design’s robustness to Gibbs ringing, the target pattern and $B1^+$ maps were down-sampled into 32$\times$32$\times$24 (6mm iso-resolution)  and 64$\times$64$\times$48 grids (3mm iso-resolution).
-The outer sections of the excitation trajectory, equaling 2.1 ms, was excluded so that the maximum excitation resolution matched with the chosen 6 mm iso-resolution.
-All three designs were evaluated against the target pattern with the fully sampled 128$\times$128$\times$96 grid for validation.
+\subsection*{Gibbs Ringing}
+Gibbs ringing commonly arises in spatial domain parallel pulse designs when the resolution of the 
+design grid is similar to that of the excitation k-space trajectory. 
+The proposed k-space-domain method is implemented without wraparound or circulant end conditions in excitation k-space, 
+so Gibbs ringing should be suppressed even when using a design grid that is only slightly wider than the trajectory. 
+To demonstrate this, 
+the target pattern and $B_1^+$ maps were further down-sampled to 32$\times$32$\times$24 (6 mm isotropic-resolution),
+and the outermost leaves of the SPINS trajectory which had duration 2.1 ms were excluded so that the maximum excitation 
+resolution matched the 6 mm target pattern and $B_1^+$ map resolution. 
+Pulses were designed by the spatial domain method using both 32$\times$32$\times$24 and 64$\times$64$\times$48 grid sizes,
+and by the k-space-domain method for 32$\times$32$\times$24 grid size.
+The designed pulses were then evaluated against the target pattern using the 128$\times$128$\times$96 grid size,
+to visualize the ringing.
 
-The k-space domain design method's performance regarding k-space undersampling, which is desired for shorter pulse duration, was also examined and compared against the spatial domain design.
-The undersampling was achieved by reducing the numbers of the previously specified SPIN trajectory's polar and azimuthal rotations proportionally by a factor called reduction factor, as shown in the third row of Figure \ref{fig:kspace_PTX_Acceleration}.
+\subsection*{Excitation k-Space Undersampling}
+An important application of parallel transmission is the reduction of multidimensional pulse durations by excitation k-space undersampling.
+To compare the spatial domain and k-space domain methods across undersampling factors,
+the number of polar and azimuthal rotations were increased and reduced relative to the reference design described above, 
+for reduction factors of 0.5, 2, 3, and 4.
 
-In order to show the k-space domain design method's ability to compensate moderate off-resonance and compare it against the spatial domain method.
-We incorporated a normalized field map with Gaussian inhomogeneity centered above the frontal sinus (Figure \ref{fig:kspace_PTX_B0}a), mimicking a characteristic susceptibility induced $B_0$ inhomogeneity.
+\subsection*{Off-Resonance}
+To compare the off-resonance-compensated k-space domain designs with off-resonance-compensated spatial domain designs,
+we incorporated a Gaussian ($\sigma = 3$ cm) field map centered above the frontal sinus, 
+which was designed to mimic the characteristic susceptibility-induced $B_0$ inhomogeneity in this part of the human brain. 
 The field maps were than scaled so that the maximum off-resonance reached +200 Hz and +400 Hz.
-Off-resonance corrected spatial domain designs were done with system matrices whose field maps were also incorporated through time segmentation approximation \cite{fessler2005toeplitz}.
-K-space domain designs were done with or without off-resonance correction.
+A time-segmented approximate off-resonance model was calculated using the method of Ref. \cite{fessler2005toeplitz} with $L = 4$ time segments,
+and this model was used in both spatial domain and k-space domain designs.

### 2020-09-07 code/LS_fft_mex_clean_ForB0.c
wag working on code

@@ -1,748 +1,0 @@
-// Important changes compared to LS_fft_mex_clean (without B0)
-// Introduced nC_actual, which is different from nC that is now nC*Lseg
-// Difference in function LS_BP_prep
-// Difference in function LS_NhN_form and LS_NhC_form
-
-
-/* LS_fft_mex.c
- *
- * compile with "mex -largeArrayDims -lmwlapack LS_fft_mex_clean_ForB0.c
- *
- * As the FFT trick grid may be large, here we enforce using
- *   size_t:    for (large-sized) grid indexing
- *   ptrdiff_t: to address negative offsets from grid center
- * instead of mwSize and mwSignedIndex
- *
- * some acronyms used:
- * _ctor: constructor
- * _dtor: destructor
- * _B:    a Block of a block matrix
- * _P:    Pointer
- * _U:    Upper matrix
- * _L:    Lower matrix
- * _t:    Temporary (when appended to a variable)
- * _i:    Iterator
- * _R:    Real
- * _I:    Imag
- */
-#if !defined(_WIN32)
-#define cposv cposv_
-/* #define chesv chesv_ */
-#endif
-
-#include <mex.h>
-#include <math.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <lapack.h>
-#include <stddef.h> /* common macros: size_t, ptrdiff_t, etc. */
-
-/* def of GRID
- * GIM GCO GNO are defined w/ ptrdiff_t as they are used in signed index
- * calculation in LS_init()
- */
-struct GRID
-{
-  float      Tik;  /* (1,), Tik regularizor coeff */
-  size_t     nC;   /* (1,), number of coils*Lseg */
-  size_t     nC_actual;   /* (1,), number of actual coils */
-  size_t     nSolve;   /* (1,), number of solved points (delta function) */
-  size_t     nDim; /* (1,), number of dimensions (1|2|3) */
-  size_t     nVtx; /* (1,), number of lin-interp ngbs, (2|4|8) */
-  mwSize    *nd;   /* (nDim,), grid size along each dim */
[…]

### 2020-09-07 code/LS_fft_mex_clean_OpenMP_Calloc_ForB0.c

@@ -1,704 +1,0 @@
-// Important:
-// This is a most direct implementation of LS_fft_mex_clean_ForB0 into OpenMP
-// Assuming mxCalloc is thread safe
-// And not even using coef_m to pre-store all the coef within openMP
-// but use mxSetCell within openMP
-
-
-/* LS_fft_mex.c
- *
- * compile with
- * mex -largeArrayDims -lmwlapack CXXFLAGS="$CXXFLAGS -fopenmp" LDFLAGS="$LDFLAGS -fopenmp" COPTIMFLAGS="$COPTIMFLAGS -fopenmp -O2" LDOPTIMFLAGS="$LDOPTIMFLAGS -fopenmp -O2" DEFINES="$DEFINES -fopenmp" LS_fft_mex_clean_OpenMP_Calloc_ForB0.c
- * As the FFT trick grid may be large, here we enforce using
- *   size_t:    for (large-sized) grid indexing
- *   ptrdiff_t: to address negative offsets from grid center
- * instead of mwSize and mwSignedIndex
- *
- * some acronyms used:
- * _ctor: constructor
- * _dtor: destructor
- * _B:    a Block of a block matrix
- * _P:    Pointer
- * _U:    Upper matrix
- * _L:    Lower matrix
- * _t:    Temporary (when appended to a variable)
- * _i:    Iterator
- * _R:    Real
- * _I:    Imag
- */
-#if !defined(_WIN32)
-#define cposv cposv_
-/* #define chesv chesv_ */
-#endif
-
-#include <mex.h>
-#include <math.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <lapack.h>
-#include <stddef.h> /* common macros: size_t, ptrdiff_t, etc. */
-#include <omp.h>
-
-/* def of GRID
- * GIM GCO GNO are defined w/ ptrdiff_t as they are used in signed index
- * calculation in LS_init()
- */
-struct GRID
-{
-  float      Tik;  /* (1,), Tik regularizor coeff */
-  size_t     nC;   /* (1,), number of coils*Lseg */
-  size_t     nC_actual;   /* (1,), number of actual coils */
[…]

### 2020-09-07 code/LS_fft_mex_clean_OpenMP_Calloc_ForB0_2.c

@@ -1,806 +1,0 @@
-// Important changes compared to LS_fft_mex_clean (without B0)
-// Introduced nC_actual, which is different from nC that is now nC*Lseg
-// Difference in function LS_BP_prep
-// Difference in function LS_NhN_form and LS_NhC_form
-
-
-/* LS_fft_mex.c
- *
- * compile with 
- * mex -largeArrayDims -lmwlapack CXXFLAGS="$CXXFLAGS -fopenmp" LDFLAGS="$LDFLAGS -fopenmp" COPTIMFLAGS="$COPTIMFLAGS -fopenmp -O2" LDOPTIMFLAGS="$LDOPTIMFLAGS -fopenmp -O2" DEFINES="$DEFINES -fopenmp" LS_fft_mex_clean_OpenMP_Calloc_ForB0.c
- * As the FFT trick grid may be large, here we enforce using
- *   size_t:    for (large-sized) grid indexing
- *   ptrdiff_t: to address negative offsets from grid center
- * instead of mwSize and mwSignedIndex
- *
- * some acronyms used:
- * _ctor: constructor
- * _dtor: destructor
- * _B:    a Block of a block matrix
- * _P:    Pointer
- * _U:    Upper matrix
- * _L:    Lower matrix
- * _t:    Temporary (when appended to a variable)
- * _i:    Iterator
- * _R:    Real
- * _I:    Imag
- */
-#if !defined(_WIN32)
-#define cposv cposv_
-/* #define chesv chesv_ */
-#endif
-
-#include <mex.h>
-#include <math.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <lapack.h>
-#include <stddef.h> /* common macros: size_t, ptrdiff_t, etc. */
-#include <omp.h>
-
-#define NTHREADS 2
-
-/* def of GRID
- * GIM GCO GNO are defined w/ ptrdiff_t as they are used in signed index
- * calculation in LS_init()
- */
-struct GRID
-{
-  float      Tik;  /* (1,), Tik regularizor coeff */
-  size_t     nC;   /* (1,), number of coils */
-  size_t     nC_actual;   /* (1,), number of actual coils */
-  size_t     nSolve;   /* (1,), number of solved points (delta function) */
[…]

### 2020-09-07 code/LS_fft_mex_clean_OpenMP_SetMaxNhNSize.c

@@ -1,815 +1,0 @@
-//     Important:
-//     Compared to LS_fft_mex_clean
-//
-//     Here, we pre-define the max size of the NhN and NhC for each thread
-//     and pre-allocate these memory before going into parallel computing
-//     so that the parallel computing will be memory safe.
-//
-//     Furthermore, the coeff calculated by different threads will be stored in a pre-allocated memory range
-//     so that the mex funtion handeling, which put the corresponding coeff into the final output cell
-//     can happen outside of openMP
-//
-//     However, it seems the mex function is thread safe when using openMP
-//     So the Calloc version of OpenMP also works.
-    
-
-
- /* compile with 
- * mex -largeArrayDims -lmwlapack CXXFLAGS="$CXXFLAGS -fopenmp" LDFLAGS="$LDFLAGS -fopenmp" COPTIMFLAGS="$COPTIMFLAGS -fopenmp -O2" LDOPTIMFLAGS="$LDOPTIMFLAGS -fopenmp -O2" DEFINES="$DEFINES -fopenmp" LS_fft_mex_clean_OpenMP_SetMaxNhNSize.c
- * As the FFT trick grid may be large, here we enforce using
- *   size_t:    for (large-sized) grid indexing
- *   ptrdiff_t: to address negative offsets from grid center
- * instead of mwSize and mwSignedIndex
- *
- * some acronyms used:
- * _ctor: constructor
- * _dtor: destructor
- * _B:    a Block of a block matrix
- * _P:    Pointer
- * _U:    Upper matrix
- * _L:    Lower matrix
- * _t:    Temporary (when appended to a variable)
- * _i:    Iterator
- * _R:    Real
- * _I:    Imag
- */
-#if !defined(_WIN32)
-#define cposv cposv_
-/* #define chesv chesv_ */
-#endif
-
-#include <mex.h>
-#include <math.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <lapack.h>
-#include <stddef.h> /* common macros: size_t, ptrdiff_t, etc. */
[…]

### 2020-09-07 code/LS_fft_mex_clean_OpenMP_SetMaxNhNSize_ForB0.c

@@ -1,802 +1,0 @@
-// Important changes compared to LS_fft_mex_clean_forB0 and LS_fft_mex_clean_OpenMP_SetMaxNhN_Size (no B0)
-// In function LS_NhN_form and LS_NhC_form, 
-// since we do accumulative sum while reusing the pre-allocated maximum memory for NhN and NhC for different instances 
-// we have to reset the content of the memory to all zero before reusing it in differnt instances
-
-
-/* LS_fft_mex.c
- *
- * compile with
- * mex -largeArrayDims -lmwlapack CXXFLAGS="$CXXFLAGS -fopenmp" LDFLAGS="$LDFLAGS -fopenmp" COPTIMFLAGS="$COPTIMFLAGS -fopenmp -O2" LDOPTIMFLAGS="$LDOPTIMFLAGS -fopenmp -O2" DEFINES="$DEFINES -fopenmp" LS_fft_mex_clean_OpenMP_SetMaxNhNSize_ForB0.c
- * As the FFT trick grid may be large, here we enforce using
- *   size_t:    for (large-sized) grid indexing
- *   ptrdiff_t: to address negative offsets from grid center
- * instead of mwSize and mwSignedIndex
- *
- * some acronyms used:
- * _ctor: constructor
- * _dtor: destructor
- * _B:    a Block of a block matrix
- * _P:    Pointer
- * _U:    Upper matrix
- * _L:    Lower matrix
- * _t:    Temporary (when appended to a variable)
- * _i:    Iterator
- * _R:    Real
- * _I:    Imag
- */
-#if !defined(_WIN32)
-#define cposv cposv_
-/* #define chesv chesv_ */
-#endif
-
-#include <mex.h>
-#include <math.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <lapack.h>
-#include <stddef.h> /* common macros: size_t, ptrdiff_t, etc. */
-#include <omp.h>
-
-
-
-#define MAXnNgb 280 
-#define NTHREADS 4
-
-/* def of GRID
- * GIM GCO GNO are defined w/ ptrdiff_t as they are used in signed index
- * calculation in LS_init()
- */
-struct GRID
-{
[…]

### 2020-09-07 code/Oldest_method.m

@@ -1,423 +1,0 @@
-% same as delta_wts_test, but loop over each target point and build
-% individual kernel, then try reduced sampling pattern. also adding spiral
-% traj
-
-% next steps:
-% 2) parallelize!
-% 3) test off resonance
-% 4) test 3D
-% 5) Large-tip
-
-FOV = 20;
-%xyDim = 32;
-
-traj = 'spiral'; % 'spiral' or 'cartesian'
-accfactor = 3;
-dPattern = 'circle'; % 'square' or 'circle'
-kRadTraj = 4/FOV; % in fitting weights, consider radius of 5 k-locations around target point
-
-genfig = true;
-
-% load sensitivities
-disp 'loading sensitivities'
-%load ~/data/data_FROMOLDDRIVE/xsense_sim/sensitivities/sensitivities_0503_1_masked
-load('sensitivities_0503_1_masked.mat')
-nCoils = size(sens32,1);
-for ii = 1:nCoils
-    sens32(ii,:,:) = squeeze(sens32(ii,:,:)).*bodymask32;
-end
-%sens32 = sens32(:,4:27,3:26);
-xyDim = size(sens32,2);
-
-% get k-locations
-disp 'defining trajectories'
-
-switch traj
-    case 'cartesian' % uniform sampling
-        kpos = -xyDim/(2*FOV):1/FOV:xyDim/(2*FOV)-1/FOV;
-        [kxPos,kyPos]=meshgrid(kpos); % don't need this if doing traj
-%%%%% Martin %%%%%% I don't think you have shift them by falf a k-voxel??
-% shift them by half a k-voxel,
-%%%%% Martin %%%%%% I don't think you have truncated anything?
-% truncate to neighborhood around DC (which is the target point)
-        kxTraj = kxPos(1:accfactor:end,:); % shift grid by half a sampling point,
-        kyTraj = kyPos(1:accfactor:end,:); % relative to original grid
-    case 'spiral' % constant angular rate spiral
-        kpos = -xyDim/(2*FOV):1/FOV:xyDim/(2*FOV)-1/FOV;
-        [kxPos,kyPos]=meshgrid(kpos);
-        nK = xyDim^2/accfactor; % # points on trajectory
-        t = (0:nK-1)/nK;
-        kmax = xyDim/(2*FOV); % /cm, max radius in k-space
-        nTurns = kmax/(1/FOV)/accfactor; % number of turns
[…]

### 2020-09-07 code/demo_kpTx_SPINS.m

@@ -1,0 +1,419 @@
+addpath utils/
+addpath utils/VERSE/
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Problem parameters
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+mls = true;            % switch to use magnitude least-squares
+
+flipAngle = 90;
+
+genfigs = true;
+
+if_kpsce_MLS = false;
+
+ifOffRes = false;
+
+ifOpenMP = true; % IN OpemMP, number of thread has to be change in the .c file and then re-compile
+
+ifDoSpatialDesign = true;
+
+if ifOpenMP
+    if ~exist('kpTx_solve_w_OpenMP')
+        mex -largeArrayDims -lmwlapack CXXFLAGS="$CXXFLAGS -fopenmp" LDFLAGS="$LDFLAGS -fopenmp" COPTIMFLAGS="$COPTIMFLAGS -fopenmp -O2" LDOPTIMFLAGS="$LDOPTIMFLAGS -fopenmp -O2" DEFINES="$DEFINES -fopenmp" kpTx_solve_w_OpenMP.c
+    end
+    nThreads = 8;
+else
+    if ~exist('kpTx_solve_w')
+        mex -largeArrayDims -lmwlapack kpTx_solve_w.c
+    end
+    nThreads = 0;
+end
+
+%%%% Uncomment only if want OpenMP
+
+if ~exist('blochsim_optcont_mex')
+    cd utils/
+    mex -largeArrayDims -lmwlapack blochsim_optcont_mex.c
+    cd ../
+end
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Load b1 maps, k-space trajectory, target pattern
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%load('~/Dropbox/kspacePTX_data/MGH24loop_head1_128_2.mat')
+load('MGH24loop_head1_128_2.mat')
+load('Mask3dxyz128_ring.mat')
+
+undersamp=2;  %Important parameter undersampling factor for b1 maps
+b1 = B1p3dxyz128;
+mask = logical(Mask3dxyz128);
[…]

### 2020-09-07 code/kPtx.m

@@ -1,248 +1,0 @@
-function W = kPtx(b1,k,offRes_args,k_pTx_args)
-
-
-[dimb1(1),dimb1(2),dimb1(3),nCoils] = size(b1);
-
-if isempty(offRes_args)
-   ifOffRes=false;
-else
-    ifOffRes=true;
-    b0=offRes_args{1};
-    mask=offRes_args{2};
-    dt=offRes_args{3};
-    Lseg=offRes_args{4};
-end
-
-
-segWidth=k_pTx_args{1};
-nHood=k_pTx_args{2};
-Tik=k_pTx_args{3};
-kWrapBack=k_pTx_args{4};
-nThreads=k_pTx_args{5};
-
-kposx = -dimb1(1)/2:dimb1(1)/2-1;
-kposy = -dimb1(2)/2:dimb1(2)/2-1;
-kposz = -dimb1(3)/2:dimb1(3)/2-1;
-[kxPos,kyPos,kzPos]=meshgrid(kposx,kposy,kposz);  % in cycle/FOV
-
-linearInds = reshape(1:dimb1(1)*dimb1(2)*dimb1(3),[dimb1(1) dimb1(2) dimb1(3)]);
-[xI,yI,zI] = ndgrid(1:dimb1(1),1:dimb1(2),1:dimb1(3));
-
-segCenters = linearInds(1:segWidth:end,1:segWidth:end,1:segWidth:end); % center indices of segments
-
-
-kxTraj=k(:,1);
-kyTraj=k(:,2);
-kzTraj=k(:,3);
-
-
-if kWrapBack
-    % tile the trajectory around the center to find traj points circulantly
-    kxTrajTile = zeros(length(kxTraj(:)),27);
-    kyTrajTile = zeros(length(kyTraj(:)),27);
-    kzTrajTile = zeros(length(kzTraj(:)),27);
-
-    for ii = 1:3
-      for jj = 1:3
-          for kk=1:3
-        kxTrajTile(:,(ii-1)*3+jj+(kk-1)*9) = kxTraj + (ii-2)*dimb1(1);
-        kyTrajTile(:,(ii-1)*3+jj+(kk-1)*9) = kyTraj + (jj-2)*dimb1(2);
-        kzTrajTile(:,(ii-1)*3+jj+(kk-1)*9) = kzTraj + (kk-2)*dimb1(3);
-          end
-      end
-    end
[…]

### 2020-09-07 code/kpTx.m

@@ -1,0 +1,271 @@
+function W = kpTx(b1, k, k_pTx_args, offRes_args)
+
+% k-Space Domain Parallel Transmit Pulse Design
+%
+% Solve for a sparse matrix W that relates the FT of a target excitation
+% pattern to the parallel RF pulses that produce it.
+%
+% Inputs:
+%   b1: Nx x Ny x Nz x nCoils B1+ map array
+%   k:  Nt x 3 3D excitation k-space trajectory (cycles/fov)
+%   k_pTx_args: (Optional) Structure with the following fields:
+%   offRes_args: (Optional) Structure with the following fields:
+%
+% Output:
+%   W: Nt * nCoils x Nx*Ny*Nz sparse matrix
+%
+% 2020 Martin Ma and William Grissom, Vanderbilt University
+
+[dimb1(1), dimb1(2), dimb1(3), nCoils] = size(b1);
+
+if ~exist('offRes_args', 'var')
+    ifOffRes = false;
+else
+    if ~isempty(offRes_args)
+        ifOffRes = true;
+        b0 = offRes_args{1};
+        mask = offRes_args{2};
+        dt = offRes_args{3};
+        Lseg = offRes_args{4};
+    else
+        ifOffRes = false;
+    end
+end
+
+if ~exist('k_pTx_args', 'var')
+    kWrapBack = false;
+    segWidth = 4;
+    nHood = 4;
+    Tik = 1;
+    nThreads = 1;
+else
+    segWidth = k_pTx_args{1}; % number of W matrix columns in each dimension to simultaneously solve for
+    nHood = k_pTx_args{2}; % maximum distance from any target point in the simultaneous block to any included trajectory point
+    Tik = k_pTx_args{3};
+    kWrapBack = k_pTx_args{4};
+    nThreads = k_pTx_args{5};
+end
+
+kposx = -dimb1(1)/2:dimb1(1)/2-1;
+kposy = -dimb1(2)/2:dimb1(2)/2-1;
+kposz = -dimb1(3)/2:dimb1(3)/2-1;
+[kxPos, kyPos, kzPos] = meshgrid(kposx, kposy, kposz);  % in cycles/FOV
+
+linearInds = reshape(1:dimb1(1)*dimb1(2)*dimb1(3), ...
+    [dimb1(1) dimb1(2) dimb1(3)]);
+[xI,yI,zI] = ndgrid(1:dimb1(1), 1:dimb1(2), 1:dimb1(3));
+
[…]

### 2020-09-07 code/spins_kspace_clean.m

@@ -1,468 +1,0 @@
-addpath utils/
-addpath utils/VERSE/
-
-if ~exist('LS_fft_mex_clean')
-    mex -largeArrayDims -lmwlapack LS_fft_mex_clean.c
-end
-
-%%%% Uncomment only if want OpenMP
-%if ~exist('LS_fft_mex_clean_OpenMP_Calloc')
-%    mex -largeArrayDims -lmwlapack CXXFLAGS="$CXXFLAGS -fopenmp" LDFLAGS="$LDFLAGS -fopenmp" COPTIMFLAGS="$COPTIMFLAGS -fopenmp -O2" LDOPTIMFLAGS="$LDOPTIMFLAGS -fopenmp -O2" DEFINES="$DEFINES -fopenmp" LS_fft_mex_clean_OpenMP_Calloc.c
-%end
-
-if ~exist('blochsim_optcont_mex')
-    cd utils/
-    mex -largeArrayDims -lmwlapack blochsim_optcont_mex.c
-    cd ../
-end
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Problem parameters
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-mls = true;            % switch to use magnitude least-squares
-
-flipAngle = 90;
-
-genfigs = true;
-
-b1MapSelect = '24loopsMartin';
-
-kTrajSelect = 'spins';
-
-dPatternSelect = 'midSelect';
-
-if_kpsce_MLS=false;
-
-ifOffRes=false;
-
-ifOpenMP=false; % IN OpemMP, number of thread has to be change in the .c file and then re-compile
-
-ifDoSpatialDesign=false;
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Load b1 maps, k-space trajectory, target pattern
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-switch(b1MapSelect)       
-        
-    case '24loopsMartin'
-
-        %load('~/Dropbox/kspacePTX_data/MGH24loop_head1_128_2.mat')
-        load('MGH24loop_head1_128_2.mat')
-        load('Mask3dxyz128_ring.mat')
-        
[…]

### 2020-09-07 Manuscript/Method.tex
wag methods and figure edits

@@
+%!TEX root = kPtx_paper.tex
 \section*{Methods}
@@
 with comparisons to the spatial-domain method of Ref. \cite{Grissom:2006:MRM}.
-RF pulses were designed for a simulated 24-channel loop transmit array (Figure \ref{fig:Coil}) that is under construction for a 7 Tesla scanner optimized
+RF pulses were designed for a simulated 24-channel loop transmit array (Figure \ref{fig:Coil}) that is being built for a 7 Tesla scanner optimized
 for imaging the human cortex.  
@@
 Ansys High Frequency Structure Simulator (Canonsburg, PA, USA) with 1.5 mm isotropic resolution. 
-All pulse designs used a SPINS excitation k-space trajectory \cite{malik2012tailored} (Figures \ref{fig:Target}b\&c) with 5 mm max resolution. 
-The SPINS trajectories were first designed analytically and the final gradient and excitation k-space trajectories were designed from them 
-using the minimum-time gradient waveform design method \cite{lustig2008fast}, 
-for a 15 {\textmu}s dwell time and subject to the scanner's gradient amplitude and slew rate constraints of 200 mT/m and 700 T/m/s, respectively. 
-The SPINS trajectory comprised three segments, with radii ranging between 1-0.625, 0.625-0.375, and 0.375-0 /cm, respectively.
-The number of polar and azimuthal rotations were 15.5/2.125, 20.66/2.833, 15.5/2.125, respectively, for each segment.
-The durations the segments after minimum-time gradient design were 4.174, 4.326, and 1.5 ms, respectively.
-With the exception of the simulations across undersampling factors, all pulse designs used the 10 ms trajectory shown in Figures \ref{fig:Target}b\&c.
+Figure \ref{fig:Target}a shows the target pattern for all pulse designs which comprised an ellipse centered on the ventricles with AP/HF/LR semi-axes of 4.8/3.2/3.2 cm.
+The pattern was smoothed by a Fermi filter that was applied in the frequency domain to match the target pattern's effective resolution to the excitation k-space trajectory's 5 mm resolution.
+This choice of target pattern was motivated by imaging applications for the 7 Tesla scanner 
+in which midbrain signals will be saturated for high-resolution, highly-accelerated imaging of the cortex. 
+Pulses were designed to excite the entire ellipse and achieve zero excitation in voxels in the cerebrum but outside the ellipse. 
+The smoothed target pattern and the $B_1^+$ maps were downsampled from their original 128$\times$128$\times$96 grids (1.5 mm isotropic resolution) to 
+64$\times$64$\times$48 grids (3 mm isotropic resolution),
+and RF designs were performed with the 64$\times$64$\times$48 grid size.
 
@@
 \end{figure}
+
+\par A SPINS excitation k-space trajectory \cite{malik2012tailored} (Figure \ref{fig:Target}b) with 5 mm max resolution was used for the designs. 
+The SPINS trajectory comprised three segments, with radii ranging between 1-0.625, 0.625-0.375, and 0.375-0 /cm, respectively.
+The number of polar and azimuthal rotations were 15.5/2.125, 20.66/2.833, 15.5/2.125, respectively, for each segment.
+The SPINS trajectories were first designed analytically and the final gradient waveforms and excitation k-space trajectories were designed from them 
+using the minimum-time gradient waveform design method \cite{lustig2008fast}, 
+for a 15 {\textmu}s dwell time and subject to the scanner's gradient amplitude and slew rate constraints of 200 mT/m and 700 T/m/s, respectively (Figure \ref{fig:Target}c). 
+The durations of the three segments after minimum-time gradient design were 4.174, 4.326, and 1.5 ms, respectively.
+With the exception of the simulations across undersampling factors, 
+all pulse designs used this 10 ms trajectory.
 
@@
 
-\par Figure \ref{fig:Target}a shows the target pattern for all pulse designs which comprised an ellipse centered on the ventricles with AP/HF/LR semi-axes of 4.8/3.2/3.2 cm.
-The pattern was smoothed by a Fermi filter that was applied in the frequency domain to match the target pattern's effective resolution to the excitation k-space trajectory's 5 mm resolution.
-This choice of target pattern was motivated by imaging applications for the 7 Tesla scanner 
-in which midbrain signals will be saturated for high-resolution, highly-accelerated imaging of the cortex. 
-Pulses were designed to excite the entire ellipse and achieve zero excitation in voxels in the cerebrum but outside the ellipse. 
-The smoothed target pattern and the $B_1^+$ maps were downsampled from their original 128$\times$128$\times$96 grids (1.5 mm isotropic resolution) to 
-64$\times$64$\times$48 grids (3 mm isotropic resolution),
-and RF designs were performed with the 64$\times$64$\times$48 grid size. 
-All pulse designs and simulations were performed in MATLAB (Mathworks, Natick, MA, USA).
+\par All pulse designs and Bloch equation simulations were performed in MATLAB (Mathworks, Natick, MA, USA).
 For spatial domain designs, 
@@
 as a function that takes as input the $B_1^+$ maps, 
-a normalized excitation k-space trajectory, and optional off-resonance and design parameters. 
+a normalized excitation k-space trajectory, and optional structures of algorithm and off-resonance parameters. 
 Within that function the Fourier transforms of the $B_1^+$ products are calculated,
-and a C-based MEX function is invoked to solve for the non-zero elements of each column of $\bm{W}$. 
+and a C-based MEX function is invoked to solve for the non-zero elements of each column of $\bm{W}$,
+with linear interpolation of the Fourier transforms of the $B_1^+$ map products. 
 Those elements are then inserted into a sparse $\bm{W}$ matrix, which is the single output of the main function. 
@@
 and the inclusion width was varied while holding the number of threads at 16, and the patch width at 4 and 8.
+
+\subsection*{L-Curves}
+To compare the tradeoff between excitation error and integrated RF power for spatial and k-space domain designs,
+pulse designs were repeated while varying Tikhonov regularization parameters ($\lambda$ in Equation \ref{eq:Solution}) 
+over five orders of magnitude. 
+The k-space domain designs were repeated four times to investigate the three main sources of error:
+finite patch width, finite inclusion width, and $B_1^+$ map product interpolation. 
+Specifically, a design was performed using patch and inclusion widths of four
+with interpolated $B_1^+$ map products (`Interpolated $\bm{S}^H\bm{S}$ matrices'),
+patch and inclusion widths covering the entire design grid with interpolated $B_1^+$ map products,
+patch and inclusion widths of four without $B_1^+$ map product interpolation (`Exact $\bm{S}^H\bm{S}$ matrices'; 
+$B_1^+$ maps were phase-modulated to each trajectory location before Fourier transform),
+and patch and inclusion widths covering the entire design grid without $B_1^+$ map product interpolation. 
+Note that the last case is equivalent to the original k-space domain method of Ref. \cite{Katscher:2003:Magn-Reson-Med:12509830}.
 

### 2020-09-07 Manuscript/Result.tex
wag methods and figure edits

@@
+%!TEX root = kPtx_paper.tex
 \section*{Results}
@@
 	\centering
+	\includegraphics[width=\textwidth]{ErrorMap_2}
+	\caption{\textcolor{red}{WAG: I think this is the figure that your example in Github should replicate.}
+	Normalized excitation patterns (top row) and error maps (bottom row) in central axial, sagittal and coronal slices 
+	for k-space domain (left) and spatial domain designs (right).}
+	\label{fig:ErrorMap}
+\end{figure}
+Figure \ref{fig:ErrorMap} shows simulated excitation patterns and error maps for spatial and k-space domain designs. 
+The k-space design was performed with 16 parallel threads and patch and inclusion widths of 4. 
+Both designs were performed with a 64$\times$64$\times$48 grid size (3 mm isotropic resolution), 
+and the excitation patterns were evaluated against the target pattern on a 128$\times$128$\times$96 grid size (1.5 mm iso-resolution). 
+The calculated root-mean-squared errors (RMSEs) were 2.42\% (spatial domain) and 2.68\% (k-space domain), 
+respectively. 
+For both design methods, most of the errors appeared at the edges of the transition band, and errors elsewhere were lower than 5\% of the target flip angle. 
+This indicates uniform inner volume excitation while maintaining the outer volume intact. 
+The parallelized k-space domain design required 2.9 seconds computation versus 100.9 seconds for the spatial domain method, a 97\% decrease.
+
+\begin{figure}
+	\centering
 	\includegraphics[width=\textwidth]{ComputationTime_2}
-	\caption{\textcolor{red}{WAG: Can you also run $2^0$ (most importantly) and $2^5$ patch width here?
-It would be good to show that the RMSE levels off at some point.
-Also can you change the RMSE axis to go from 0 to 6?
-That will help emphasize that even though the error is decreasing with increasing patch width,
-	the difference between patch width = 2 and patch width = something large is quite small. }
-	Studies of different parallelization parameters, where patch width is the square root of the number of $\mathbf{W}$ columns solved for simultaneously and inclusion width is the assumed range of influence of each excitation k-space location.
+	\caption{(a) k-Space design time versus number of threads, for patch and inclusion widths of 4. 
+	(b) Studies of different parallelization parameters, where patch width is the square root of the number of $\mathbf{W}$ columns solved for simultaneously and inclusion width is the assumed range of influence of each excitation k-space location.
 \textbf{(a)} Computation time vs.
@@
 	\centering
-	\includegraphics[width=\textwidth]{ErrorMap_2}
-	\caption{\textcolor{red}{WAG: I think this is the figure that your example in Github should replicate.}
-	Normalized excitation patterns (top row) and error maps (bottom row) for k-space domain design (left column) and spatial domain design (right column), with RMSE and design time indicated.}
-	\label{fig:ErrorMap}
+	\includegraphics[width=\textwidth]{L_curve}
+	\caption{L-curves for spatial domain and k-space domain pulse designs, 
+	repeated across five orders of magnitude of the methods' Tikhonov regularization parameters.
+	The k-space domain designs were repeated using patch and inclusion widths of four versus solving for the entire domain at once (`Path / Inclusion Width = 4' versus `Full Patch'),
+	and using $B_1^+$ map product interpolation versus phase modulation to each trajectory location (`Interpolated $\bm{S}^H\bm{S}$ matrices' versus
+	`Exact $\bm{S}^H\bm{S}$ matrices').}
+	\label{fig:LCurves}
 \end{figure}
-The simulated excitation patterns and error maps are shown in Fig \ref{fig:ErrorMap} for both k-space domain design (left) and spatial domain design (right), where the k-space domain design was solved with 16 parallel computing threads, patch width 4, and inclusion width 4.
-Both designs were done with the 64$\times$64$\times$48 grid size (3mm iso-resolution), and the excitation patterns were evaluated against the target pattern with the 128$\times$128$\times$96 grid size (1.5mm iso-resolution).
-grid size.
-The calculated RMSE from the k-space domain design and the spatial domain design were 2.42\% and 2.68\%, respectively, which were practically equal.
-For both design methods, most of the errors appeared at the edges of the transition band, with other errors lower than 5\% of the target flip angle.
-This indicates uniform inner volume suppression while maintaining the outer volume intact, which can in turn decrease g-factor in highly accelerated imaging.
-In practice, error near the transition band can be mitigated by ensuring the region of interest (ROI) of the cortex falls completely in the stop-band and assuming zero signal within the pass-band during undersampled reconstruction.
-More significantly, the parallelized k-space domain design method drastically reduced the mean computation time from 100.9 seconds to 2.9 seconds compared to the spatial domain design, which was a 97\% decrease.
 

### 2020-09-07 Manuscript/Result.tex
wag results edits

@@
 	\centering
-	\includegraphics[width=\textwidth]{ErrorMap_2}
+	\includegraphics[width=\textwidth]{ErrorMap}
 	\caption{\textcolor{red}{WAG: I think this is the figure that your example in Github should replicate.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{ComputationTime_2}
-	\caption{(a) k-Space design time versus number of threads, for patch and inclusion widths of 4. 
-	(b) Studies of different parallelization parameters, where patch width is the square root of the number of $\mathbf{W}$ columns solved for simultaneously and inclusion width is the assumed range of influence of each excitation k-space location.
-\textbf{(a)} Computation time vs.
-thread numbers.
-Patch width and inclusion with were kept at 4 cycle/FOV.
-\textbf{(b\&c)} Computation time (blue axis) and RMSE (red axis) vs.
-patch widths (b) and inclusion widths (c).
-Thread number were kept at 16 of for both design.
-Inclusion width was constant at 4 in (b) and patch widths were constant at 4 (solid line) and 8 (dashed line).}
+	\includegraphics[width=\textwidth]{ComputationTime}
+	\caption{(a) k-Space computation time versus number of parallel threads, for patch and inclusion widths of 4. 
+	(b) Computation time (blue axis) and RMSE (red axis) versus patch width, for an inclusion width of 4 and 16 threads. 
+	(c) Computation time (blue axis) and RMSE (red axis) versus inclusion width, for patch widths of 4 and 8 and 16 threads.}
 	\label{fig:ComputationTime}
@@
 	The k-space domain designs were repeated using patch and inclusion widths of four versus solving for the entire domain at once (`Path / Inclusion Width = 4' versus `Full Patch'),
-	and using $B_1^+$ map product interpolation versus phase modulation to each trajectory location (`Interpolated $\bm{S}^H\bm{S}$ matrices' versus
-	`Exact $\bm{S}^H\bm{S}$ matrices').}
+	and using $B_1^+$ map product interpolation versus phase modulation to each trajectory location (`Interpolated $\bm{S}^H\bm{S}$ Matrices' versus
+	`Exact $\bm{S}^H\bm{S}$ Matrices').}
 	\label{fig:LCurves}
@@
 	\centering
-	\includegraphics[width=\textwidth]{GibbsRinging_3}
+	\includegraphics[width=\textwidth]{GibbsRinging}
 	\caption{Normalized error maps and RMSE for \textbf{(a)} spatial domain design and \textbf{(c)} k-space domain design with 6 mm iso-resolution, 32$\times$32$\times$24 design grid.
@@
 	\centering
-	\includegraphics[width=\textwidth]{Acceleration_3}
-	\caption{ \textcolor{red}{We should talk about this; I don't think reviewers will like the fact that the scale starts at 0.2. Also we should probably call it `Reduction Factor' since it is 
-	really the factor by which the pulse duration is reduced, and not exactly a k-space undersampling factor, is that right?}
-	Normalized error maps and RMSE for spatial domain design (first row) and k-space domain design (second row), with excitation trajectories undersampled by different reduction factors (third row).}
+	\includegraphics[width=\textwidth]{ReductionFactor}
+	\caption{Normalized error maps and RMSE for spatial domain design (first row) and k-space domain design (second row), 
+	using excitation k-space trajectories with different reduction factors (third row).
+	The reduction factors are referenced to the 10 ms trajectory in Figure \ref{fig:Target} (second column).}
 	\label{fig:kspace_PTX_Acceleration}
@@
 	\centering
-	\includegraphics[width=\textwidth]{kspace_PTX_B0}
+	\includegraphics[width=\textwidth]{OffResonance}
 	\caption{\textcolor{red}{WAG: Update with new correction method; include compute times and errors versus number of segments}

### 2020-09-08 code/kpTx.m
Wag cleaned up a bit more of off-resonance code

@@ -103,10 +103,8 @@ if ifOffRes
     
     % apply off-resonance correction
     % embed spatial interpolators to sensitivity maps
-    CtFull = zeros(Lseg,dimb1(1),dimb1(2),dimb1(3));
-    for jj = 1:Lseg
-        CtFull(jj, mask) = Ct(:,jj);
-    end
+    CtFull = zeros([Lseg dimb1]);
+    CtFull(:, mask) = Ct.';
     CtFull = permute(CtFull, [2 3 4 1]);
     BFull = B;
     
@@ -114,21 +112,18 @@ if ifOffRes
     BFull_c = cell(1);
     BFull_c{1} = BFull;
     
-    calib = zeros(dimb1(1),dimb1(2),dimb1(3),nCoils,Lseg);
+    calib = zeros([dimb1 nCoils Lseg]);
     for ii = 1:Lseg
-        for jj = 1:nCoils
-            calib(:,:,:,jj,ii) = b1(:,:,:,jj).*CtFull(:,:,:,ii);
-        end
+        calib(:,:,:,:,ii) = bsxfun(@times, b1, CtFull(:, :, :, ii));
     end
-    
-    calib = reshape(calib,dimb1(1),dimb1(2),dimb1(3),nCoils*Lseg);
+    calib = calib(:, :, :, :);
     nCoilsLseg = nCoils*Lseg;
     
     disp 'Building FT maps'
     tic
     nComb = nCoilsLseg * (nCoilsLseg + 1) / 2;
     calib = single(calib);
-    FToversamp=1;   % Oversampling factor = 1 to save memory
+    FToversamp = 1;   % Oversampling factor = 1 to save memory
     [F_c, ~] = FFTTrick(calib, nComb, FToversamp);
     
     toc

### 2020-09-08 Manuscript/Result.tex
wag edits

@@
 	repeated across five orders of magnitude of the methods' Tikhonov regularization parameters.
-	The k-space domain designs were repeated using patch and inclusion widths of four versus solving for the entire domain at once (`Path / Inclusion Width = 4' versus `Full Patch'),
+	The k-space domain designs were repeated using patch and inclusion widths of four versus solving for the entire domain at once (`Patch / Inclusion Width = 4' versus `Full Patch'),
 	and using $B_1^+$ map product interpolation versus phase modulation to each trajectory location (`Interpolated $\bm{S}^H\bm{S}$ Matrices' versus
@@
 	\includegraphics[width=\textwidth]{OffResonance}
-	\caption{\textcolor{red}{WAG: Update with new correction method; include compute times and errors versus number of segments}
-	\textbf{(a)} Normalized off-resonance map with Gaussian distortion centered above the frontal sinus, mimicking a characteristic susceptibility induced $B_0$ inhomogeneity.
-\textbf{(b)} Normalized excitation maps and RMSE for spatial domain design with off-resonance correction (first row), k-space domain design with and without off-resonance correction (second \& third rows).}
+	\caption{
+	(a) Normalized off-resonance map containing a Gaussian distortion centered above the frontal sinus, 
+	to mimic air-tissue susceptibility difference-induced $B_0$ inhomogeneity.
+	(b) Normalized excitation maps and RMSEs for spatial domain design with off-resonance correction (first row), 
+	and k-space domain design without and with off-resonance correction (second and third rows).}
 	\label{fig:kspace_PTX_B0}

### 2020-09-09 Manuscript/Method.tex
wag edits
wag results edits

@@
 \par A SPINS excitation k-space trajectory \cite{malik2012tailored} (Figure \ref{fig:Target}b) with 5 mm max resolution was used for the designs. 
-The SPINS trajectory comprised three segments, with radii ranging between 1-0.625, 0.625-0.375, and 0.375-0 /cm, respectively.
-The number of polar and azimuthal rotations were 15.5/2.125, 20.66/2.833, 15.5/2.125, respectively, for each segment.
+The SPINS trajectory comprised three segments with radii ranging between 1-0.625, 0.625-0.375, and 0.375-0 cycles/cm, respectively.
+The number of polar and azimuthal rotations were 15.5/2.125, 20.66/2.833, 15.5/2.125 for each segment, respectively.
 The SPINS trajectories were first designed analytically and the final gradient waveforms and excitation k-space trajectories were designed from them 
@@
 all pulse designs used this 10 ms trajectory.
+With this trajectory and the 64$\times$64$\times$48 design grid size, 
+the dimensions of the $\bm{W}$ matrix were 16,632 RF pulse samples, by 196,608 target k-space locations.
 
@@
 which was accelerated by non-uniform fast Fourier transforms \cite{Fessler:2003fk}. 
+Except for the off-resonance-compensated designs described below, 
+all spatial domain designs were parallelized using 16 threads that simultaneously computed the forward and backward 
+non-uniform fast Fourier transforms across transmit coils. 
 The proposed k-space domain algorithm was implemented based on code for the non-Cartesian GRAPPA method of Ref. \cite{luo2019grappa},
@@
 and a C-based MEX function is invoked to solve for the non-zero elements of each column of $\bm{W}$,
-with linear interpolation of the Fourier transforms of the $B_1^+$ map products. 
+with linear interpolation of the Fourier transforms of the $B_1^+$ map products to obtain the entries of the $\bm{S}^H\bm{S}$ matrices. 
 Those elements are then inserted into a sparse $\bm{W}$ matrix, which is the single output of the main function. 
@@
 The number of threads were varied while holding the patch width and inclusion width both at 4 cycles/FOV.
-The patch width was varied while holding the number of threads at 16, and the inclusion width at 4,
-and the inclusion width was varied while holding the number of threads at 16, and the patch width at 4 and 8.
+The patch width was varied while holding the number of threads at 16, and the inclusion width at 4 cycles/FOV,
+and the inclusion width was varied (2, 4, 6, and 8 cycles/FOV) while holding the number of threads at 16, and the patch width at 4 and 8 cycles/FOV. 
+The sizes of the $\bm{W}$ matrices were also recorded, holding patch width constant at 4 cycles/FOV and varying the inclusion width.
 
@@
 and this model was used in both spatial domain and k-space domain designs. 
+Both spatial domain and k-space domain designs used 32 parallel threads.

### 2020-09-09 Manuscript/Result.tex
wag results edits

@@
 \end{figure}
-Figure \ref{fig:ErrorMap} shows simulated excitation patterns and error maps for spatial and k-space domain designs. 
-The k-space design was performed with 16 parallel threads and patch and inclusion widths of 4. 
-Both designs were performed with a 64$\times$64$\times$48 grid size (3 mm isotropic resolution), 
+Figure \ref{fig:ErrorMap} shows simulated excitation patterns and error maps for the reference spatial and k-space domain designs. 
+Both designs were performed with 16 parallel threads and the 64$\times$64$\times$48 grid size (3 mm isotropic resolution), 
 and the excitation patterns were evaluated against the target pattern on a 128$\times$128$\times$96 grid size (1.5 mm iso-resolution). 
+The k-space domain design used patch and inclusion widths of 4.
 The calculated root-mean-squared errors (RMSEs) were 2.42\% (spatial domain) and 2.68\% (k-space domain), 
 respectively. 
-For both design methods, most of the errors appeared at the edges of the transition band, and errors elsewhere were lower than 5\% of the target flip angle. 
+For both design methods, most of the errors appeared at the edges of the transition band, 
+and errors elsewhere were lower than 5\% of the target flip angle. 
 This indicates uniform inner volume excitation while maintaining the outer volume intact. 
-The parallelized k-space domain design required 2.9 seconds computation versus 100.9 seconds for the spatial domain method, a 97\% decrease.
+The parallelized k-space domain design required 2.9 seconds computation versus 31.8 seconds for the spatial domain method, a 91\% decrease.
 
@@
 	\includegraphics[width=\textwidth]{ComputationTime}
-	\caption{(a) k-Space computation time versus number of parallel threads, for patch and inclusion widths of 4. 
-	(b) Computation time (blue axis) and RMSE (red axis) versus patch width, for an inclusion width of 4 and 16 threads. 
-	(c) Computation time (blue axis) and RMSE (red axis) versus inclusion width, for patch widths of 4 and 8 and 16 threads.}
+	\caption{(a) k-Space computation time versus number of parallel threads, for patch and inclusion widths of 4 cycles/FOV. 
+	(b) Computation time (blue axis) and RMSE (red axis) versus patch width, for an inclusion width of 4 cycles/FOV and 16 threads. 
+	(c) Computation time (blue axis) and RMSE (red axis) versus inclusion width, for patch widths of 4 and 8 cycles/FOV, and 16 threads.}
 	\label{fig:ComputationTime}
 \end{figure}
-Figure \ref{fig:ComputationTime}a shows the mean computation time versus different thread numbers.
-The k-space design problem held the patch and inclusion width constant at 4.
-The mean computation time decreases with increasing thread numbers before 12 threads, and then plateaus due to overhead.
-The thread number was conservatively chosen to be 16 for the following studies to ensure timely solutions.
-Figure \ref{fig:ComputationTime}b shows the mean computation time and the RMSE with different patch widths.
-The computation time increases and the RMSE decreases as the patch width increases.
-This was because when patch width increases, there are more excitation trajectory points included in one instance problem, even with the same inclusion width.
-As a result, each instance problem becomes bigger and more time consuming, which cancels the advantageous fact that there are fewer instance problems in total, especially in cases with parallel computing.
-Furthermore, increasing the patch width is equivalently increasing the inclusion widths for the center target points within each patch, which makes the solutions more accurate.
-Here, we chose patch widths 4 and 8 (labeled $2^2$ and $2^3$) to balance time and accuracy for further evaluation.
-Figure \ref{fig:ComputationTime}c shows the mean computation time and the RMSE with different inclusion widths.
-The solid lines and dashed lines were obtained with patch width 4 and 8, respectively.
-Computation time increases and error decreases with increasing inclusion width.
-Particularly, increasing inclusion width is equivalent to utilizing more accurate $B_1^+$ information by truncating the $B_1^+$ map Fourier transforms to zero further out from DC.
-For both patch widths 4 and 8, 4 is the optimal inclusion width, which confirms the result in \ref{fig:ComputationTime}a , previously.
-Using an inclusion width of 4, the computation time and error are acceptable for both patch width numbers.
-Following these results,  we chose patch width 4 for the further designs.
+\subsection*{k-Space Algorithm Parameters}
+Figure \ref{fig:ComputationTime}a plots mean computation time versus number of parallel threads,
+holding the patch and inclusion widths fixed at 4 cycles/FOV. 
+The computation time decreased rapidly with increasing thread number up to 12 threads, 
+and then plateaued, likely due to the overhead involved in initiating threads after that point.
+Based on this result, the number of threads was held fixed at 16 for subsequent designs when off-resonance was not compensated.
+
+\par Figure \ref{fig:ComputationTime}b plots mean computation time and RMSE with different patch widths. 
+The computation time decreased up to a patch width of 4 cycles/FOV (corresponding to $4^3 = 64$ simultaneously solved columns of $\bm{W}$) 
+and then increased sharply for larger patch widths. 
+RMSE decreased slowly as the patch width increased since the number of excitation trajectory points included in the calculation of weights for each 
+target point increases on average (and especially for target locations in the middle of each patch) as the patch width increases, 
+even when the inclusion width stays fixed.
+Based on this result, a patch width of 4 cycles/FOV was used for subsequent designs.
+
+\par Figure \ref{fig:ComputationTime}c plots mean computation time and RMSE with different inclusion widths. 
+The solid lines and dashed lines were obtained with patch widths of 4 and 8 cycles/FOV, respectively. 
+Computation time increased and error decreased with increasing inclusion width,
+since more excitation trajectory points were included in each target location's calculation for increasing inclusion width,
+corresponding to an increased $\bm{S}^H\bm{S}$ matrix size. 
+The RMSE was only slightly lower for a patch width of 8 versus 4 cycles/FOV, 
+but the computation time was much higher for 8 cycles/FOV, across all inclusion widths. 
+The knees in the curves occurred approximately at an inclusion width of 4 cycles/FOV,
+so this value was used in subsequent designs.
+
+\par Table \ref{fig:wsize} lists the size of the final matrix $\bm{W}$ in gigabytes,
+versus inclusion width.
+As inclusion width increases, more excitation trajectory points are used in the solution of each target location,
+until the entire trajectory is used for each point (Inclusion width = $\infty$ in the table),
+corresponding to a full solution. 
+With the inclusion width of 4 cycles/FOV used here, 
+the matrix size was 98\% smaller than that of a full solution.
+
+\begin{figure}
+\centering
+\begin{tabular}{c | c}
+Inclusion Width & $\bm{W}$ Matrix Size (GB) \\
+\hline
+$\infty$ & 24.4 \\
+8 & 2.73 \\
+6 & 1.37 \\
+4 & 0.53 \\
+2 & 0.14
+\end{tabular}
+\caption{$\bm{W}$ matrix sizes in gigabytes (GB) versus inclusion width in cycles/FOV. 
+An inclusion width of $\infty$ corresponds to a full matrix solution.}
+\label{fig:wsize}
+\end{figure}
 
@@
 
+\subsection*{L-Curves}
+
 \begin{figure}
@@
 
+\subsection*{Gibbs Ringing}
 Figure \ref{fig:GibbsRing}a\&c show the results of the  low-resolution designs using k-space domain method and the spatial domain method.

### 2020-09-09 Manuscript/Result.tex
wag added W table

@@
 versus inclusion width.
-As inclusion width increases, more excitation trajectory points are used in the solution of each target location,
-until the entire trajectory is used for each point (Inclusion width = $\infty$ in the table),
+As inclusion width increases, more excitation trajectory points are used in the solution of the weights for each target location,
+until the entire trajectory is used for each location (Inclusion width = $\infty$ in the table),
 corresponding to a full solution. 

### 2020-09-10 Manuscript/Method.tex
wag further results edits

@@
 \subsection*{L-Curves}
-To compare the tradeoff between excitation error and integrated RF power for spatial and k-space domain designs,
+To compare the tradeoff between excitation error (measured by root-mean-square error)
+and integrated RF root-mean-square (RMS) amplitude for spatial and k-space domain designs,
 pulse designs were repeated while varying Tikhonov regularization parameters ($\lambda$ in Equation \ref{eq:Solution}) 
@@
 Note that the last case is equivalent to the original k-space domain method of Ref. \cite{Katscher:2003:Magn-Reson-Med:12509830}.
+For each design, flip angle RMSE (calculated using the spatial domain non-uniform fast Fourier transform) and root-mean-square RF amplitude was
+calculated.
 

### 2020-09-10 Manuscript/Result.tex
wag further results edits

@@
 \subsection*{L-Curves}
+Figure \ref{fig:LCurves} plots flip angle RMSE versus RF RMS amplitude for the spatial domain method
+and different configurations of the k-space domain method.
+The spatial domain method achieves the best overall tradeoff between error and RMS amplitude (dashed black curve),
+which is matched by the k-space domain method when all target locations are solved simultaneously with
+all excitation trajectory points included (orange curve) and exact $\bm{S}^H\bm{S}$ matrix construction. 
+When the inclusion and patch widths are limited to 4 cycles/FOV but the $\bm{S}^H\bm{S}$ 
+matrices are still constructed exactly, there is an increase in error and RMS amplitude (solid blue curve). 
+However, a larger penalty is incurred by interpolating the entries of the $\bm{S}^H\bm{S}$ matrices (dashed orange curve)
+than by limiting the inclusion and patch widths.
+Combining interpolation of the $\bm{S}^H\bm{S}$ matrix entries and patch and inclusion widths of 4 cycles/FOV yield 
+the dashed blue curve, which has a higher error and RF amplitude than when interpolation or small patch and inclusion widths are
+used alone.
+Overall, these results and the results in Figure \ref{fig:ComputationTime} and Table \ref{fig:wsize}
+show that the k-space domain method allows a tradeoff between computation time and memory usage versus
+excitation error and RMS RF amplitude.
+The dots on the spatial domain and k-space domain curves indicate the knees of of the curves corresponding to
+the $\lambda$ values used for the designs in Figures \ref{fig:ErrorMap}, \ref{fig:ComputationTime}, \ref{fig:kspace_PTX_Acceleration}, and \ref{fig:kspace_PTX_B0}.
 

### 2020-09-10 Manuscript/Method.tex
wag done with Results

@@
 over five orders of magnitude. 
-The k-space domain designs were repeated four times to investigate the three main sources of error:
-finite patch width, finite inclusion width, and $B_1^+$ map product interpolation. 
-Specifically, a design was performed using patch and inclusion widths of four
-with interpolated $B_1^+$ map products (`Interpolated $\bm{S}^H\bm{S}$ matrices'),
-patch and inclusion widths covering the entire design grid with interpolated $B_1^+$ map products,
-patch and inclusion widths of four without $B_1^+$ map product interpolation (`Exact $\bm{S}^H\bm{S}$ matrices'; 
+The k-space domain designs were repeated four times to investigate the two main sources of error:
+finite patch and inclusion widths, 
+and $B_1^+$ map product interpolation when building the $\bm{S}^H\bm{S}$ matrices. 
+Specifically, for each $\lambda$ a design was performed using patch and inclusion widths of four (`Patch/Inclusion Widths = 4')
+with interpolated $B_1^+$ map products (`Interpolated Matrices'),
+patch and inclusion widths covering the entire design grid (`Patch/Inclusion Widths = $\infty$') with interpolated $B_1^+$ map products,
+patch and inclusion widths of four without $B_1^+$ map product interpolation (`Exact Matrices'; 
 $B_1^+$ maps were phase-modulated to each trajectory location before Fourier transform),
@@
 Note that the last case is equivalent to the original k-space domain method of Ref. \cite{Katscher:2003:Magn-Reson-Med:12509830}.
-For each design, flip angle RMSE (calculated using the spatial domain non-uniform fast Fourier transform) and root-mean-square RF amplitude was
-calculated.
+For each design, flip angle RMSE (calculated using the spatial domain non-uniform fast Fourier transform) and root-mean-square RF amplitude were
+recorded.
 
@@
 resolution matched the 6 mm target pattern and $B_1^+$ map resolution. 
-Pulses were designed by the spatial domain method using both 32$\times$32$\times$24 and 64$\times$64$\times$48 grid sizes,
+Using this shorter 7.9 ms trajectory, 
+pulses were designed by the spatial domain method using both 32$\times$32$\times$24 and 64$\times$64$\times$48 grid sizes,
 and by the k-space-domain method for 32$\times$32$\times$24 grid size.
+The Tikhonov regularization parameters for the 32$\times$32$\times$24 designs were set so that the RMS RF amplitudes produced 
+by the k-space domain and spatial domain designs matched.
 The designed pulses were then evaluated against the target pattern using the 128$\times$128$\times$96 grid size,

### 2020-09-10 Manuscript/Result.tex
wag done with Results

@@
 which is matched by the k-space domain method when all target locations are solved simultaneously with
-all excitation trajectory points included (orange curve) and exact $\bm{S}^H\bm{S}$ matrix construction. 
+all excitation trajectory points included and exact $\bm{S}^H\bm{S}$ matrix construction (orange curve). 
 When the inclusion and patch widths are limited to 4 cycles/FOV but the $\bm{S}^H\bm{S}$ 
@@
 the $\lambda$ values used for the designs in Figures \ref{fig:ErrorMap}, \ref{fig:ComputationTime}, \ref{fig:kspace_PTX_Acceleration}, and \ref{fig:kspace_PTX_B0}.
+Note that the RMSE's in Figure \ref{fig:LCurves} are slightly lower for the spatial domain designs
+and slightly higher for the k-space domain designs compared to other figures,
+because the flip angle errors in Figure \ref{fig:LCurves} were calculated using 
+spatial domain non-uniform fast Fourier transforms instead of Bloch equation simulations, 
+to provide a more direct measure of the design error.
 
@@
 \subsection*{Gibbs Ringing}
-Figure \ref{fig:GibbsRing}a\&c show the results of the  low-resolution designs using k-space domain method and the spatial domain method.
-The result of the high-resolution design of the spatial domain is also shown in Figure \ref{fig:GibbsRing}b.
-All three designed were done with a excitation trajectory that matches the 6 mm iso-resolution.
-The red arrows indicate the Gibbs ringing in the low-resolution spatial domain design, that can only be suppressed with high-resolution spatial domain design.
-However, the k-space domain design, although also low-resolution, is insensitive to this problem.
-Furthermore, the ripple pattern in the low resolution k-space design matches the high-resolution spatial design.
-Looking from a spatial domain point of view, the Gibbs ringing was caused by the lack of ability to observe the ringing with low-resolution.
-Looking from a k-space domain point of view, the Gibbs ringing was due to "wrap back" of the k-space FOV.
-When the spatial resolution is low the k-space FOV is small, and therefore the RF samples at one end of the trajectory can incorrectly "reach" and affect the k-space points at the other end of the k-space FOV in a circulation shift fashion.
-However, for the k-space domain design, even with low resolution, there is no k-space "wrap back" because the incorporated trajectory points are explicitly specified.
-Particularly, for the instance problems whose patches are at the edges of the k-space FOV, the excitation trajectory points at the other ends of the k-space FOV will not be incorporated into the design.
+Figure \ref{fig:GibbsRing}a shows slices of the excitation error pattern produced by pulses designed by the spatial domain method
+on a 32$\times$32$\times$24 grid, which were Bloch-simulated on the original 128$\times$128$\times$96 grid. 
+There is significant Gibbs ringing in the pattern (indicated by the red arrows),
+and the pulses incur a higher RMSE (4.64\%) than pulses designed using either the spatial domain method with a finer 64$\times$64$\times$48 grid
+(2.66\%; Figure \ref{fig:GibbsRing}b) or the k-space domain method with a 32$\times$32$\times$24 grid (3.00\%; Figure \ref{fig:GibbsRing}c). 
+Gibbs ringing is not apparent in either the 64$\times$64$\times$48 spatial domain error pattern or the 32$\times$32$\times$24 k-space domain error pattern. 
+The RMS RF amplitudes of the low resolution designs were both 0.05. 
+Note that the error of the 64$\times$64$\times$48 spatial domain design is slightly higher than designs presented in other figures
+due to the lower-resolution excitation trajectory. 
+From a spatial domain point of view, 
+the Gibbs ringing in the low-resolution spatial domain design was caused by the design's inability to observe and limit the ringing in the low-resolution design grid. 
+From a k-space domain point of view, the Gibbs ringing in 
+Figure \ref{fig:GibbsRing}a was due to implicit circulant end conditions at the edges of excitation k-space in the low-resolution
+spatial domain design,
+which led RF samples at one edge of k-space to wrap-around and affect target locations at the opposite edge of k-space. 
+This effect is mitigated using a high-resolution spatial domain design grid, as illustrated in Figure \ref{fig:GibbsRing}b. 
+However, even for a low-resolution k-space domain design there is no wrap-around effect in excitation k-space 
+because the trajectory points that are incorporated in the weights solution for each patch of target locations are explicitly specified to be those in the immediate vicinity of 
+the target points, without circulant end conditions. 
+%Particularly, for the instance problems whose patches are at the edges of the k-space FOV, the excitation trajectory points at the other ends of the k-space FOV will not be incorporated into the design.
+
+%Due to implicit circulant end conditions in k-space for the spatial domain design, t
 
@@
 	\includegraphics[width=\textwidth]{ReductionFactor}
-	\caption{Normalized error maps and RMSE for spatial domain design (first row) and k-space domain design (second row), 
+	\caption{Normalized error maps and RMSEs for spatial domain design (first row) and k-space domain design (second row), 
 	using excitation k-space trajectories with different reduction factors (third row).
@@
 
-Figure \ref{fig:kspace_PTX_Acceleration} shows a comparison between the performance of spatial domain design (first row) and k-space domain design (second row) regarding undersampled excitation trajectories (third row) with different reduction factors.
-Both design methods had larger errors when the excitation k-space was less densely traversed.
-The k-space domain design provided similar error maps and practically equal RMSE.
-The k-space domain design had slightly larger RMSE because of the interpolation and truncation of the k-space sensitivity when building the $\mathbf{S}^{H}\mathbf{S}$ matrix, and can be improved by increasing the inclusion width.
+\subsection*{Excitation k-Space Undersampling}
+Figure \ref{fig:kspace_PTX_Acceleration} compares excitation error patterns produced by spatial domain-designed pulses (top row)
+and k-space domain-designed pulses (middle row),
+for different trajectory reduction factors which resulted in the SPINS trajectories plotted in the third row. 
+For each design the k-space domain-designed pulses had higher error, 
+but error increased smoothly with increasing reduction factor, as it did for the spatial domain designs.
 
@@
 
-Regarding 3D off-resonance patterns with the shape shown in Figure \ref{fig:kspace_PTX_B0}a and different scaling, Figure \ref{fig:kspace_PTX_B0}b shows the excitation maps of three types of designs: spatial domain design with off-resonance correction (first row), k-space domain design with and without off-resonance correction (second \& third row).
-As shown in the second row of Figure \ref{fig:kspace_PTX_B0}b, off-resonance caused false excitation outside the designated suppression region, and must be corrected.
-With 200 Hz maximum off-resonance, which is the typical range of off-resonance observed in clinical studies, k-space domain design with correction was able to fully correct the off-resonance artifacts.
-It was also able to provide excitation pattern comparable to spatial domain design with 400 Hz maximum off-resonance.
+\subsection*{Off-Resonance}
+Figure \ref{fig:kspace_PTX_B0}a shows the off-resonance maps containing a Gaussian distortion which was centered above the frontal sinus,
+and scaled to peak amplitudes of 0, 200, and 400 Hz for the pulse designs and Bloch simulations. 
+Figure \ref{fig:kspace_PTX_B0}b shows excitation error patterns and RMSEs for spatial domain designs with off-resonance compensation,
+and k-space domain designs without and with off-resonance compensation. 
+Without off-resonance compensation, 
+the k-space domain-designed pulses produced large ($>$ 10\% of $M_0$) excitation errors both inside and outside the target ellipse. 
+When the off-resonance map was incorporated in the spatial domain and k-space domain designs, 
+the distortion was nearly fully corrected when it had a peak amplitude of 200 Hz. 
+When the map was scaled to a peak of 400 Hz, some large errors remained, with the k-space domain-designed pulses achieving slightly lower RMSE. 
+%It was also able to provide excitation pattern comparable to spatial domain design with 400 Hz maximum off-resonance.
 The k-space domain design has a weaker performance with higher off-resonance due to the fact that the time segmentation approximation in Ref \cite{fessler2005toeplitz} was meant to approximate forward models from RF to excitation patterns and does not serve as an accurate approximation to the backward model as we need in the k-space domain design.

### 2020-09-10 Manuscript/Conclusion.tex
wag added preamble
Wag all done, need to move to wiley template

@@
-\section*{Discussion and Conclusions}
+%!TEX root = kPtx_paper.tex
+\section*{Discussion}
+\subsection*{Summary}
+A small-tip-angle k-space domain parallel transmit pulse design algorithm was proposed
+that divides up the calculation of a matrix relating a target excitation pattern to the pulses that produce it 
+into a set of independent problems for patches of target excitation k-space locations,
+each of which is influenced by a local neighborhood of points on the excitation k-space trajectory.
+The division of the problem into patches of target locations creates an opportunity for fine parallelization,
+while the limited neighborhood sizes lead to small problem sizes for each patch. 
+Compared to the original k-space-based algorithm of Ref. \cite{Katscher:2003:Magn-Reson-Med:12509830},
+the L-curve and matrix size results showed that 
+the new algorithm produces much smaller matrix sizes that can be calculated more quickly,
+with the tradeoff of increased excitation error or RF power. 
+Results showed that the algorithm also enables compensation of off-resonance 
+which has not previously been described in a k-space domain design. 
+Compared to widely-used spatial domain method of Ref. \cite{Grissom:2006:MRM},
+the new algorithm is non-iterative and can be finely parallelized to achieve shorter design times, 
+and results showed that it can use coarser target grid sizes while avoiding Gibbs ringing, 
+again with the tradeoff of increased excitation error or RF power.
+The performance of off-resonance-compensated spatial domain and k-space domain pulse designs was similar,
+and the methods were similarly sensitive to excitation k-space undersampling.
 
-A computationally efficient and highly parallelizable k-space domain pTx pulse design method was proposed.
-The method adapts the k-space domain formulism proposed by Katscher et al \cite{katscher2003transmit}, which does not require the computationally expensive iterative processes in the conventional spatial domain design methods.
-The method advances the work of Katscher et al \cite{katscher2003transmit} by finely parallelizing the process of finding the system matrix.
-Furthermore, a technique inspired by a rapid GRAPPA calibration method \cite{luo2019grappa} is also included to further speed up the computation of each instance.
-The proposed k-space domain design method was evaluated through simulation upon an inner volume pulse design problem for MR Corticography, which can in turn enable submillimeter whole-cortex and cortex-specific imaging.
-The optimal parallelization parameters: thread number, patch width, and inclusion width, were found for this design problem.
-The proposed method reduced the computation time by 97\% compared to the conventional spatial domain design method, while producing equal inner volume suppression performance.
-And the abilities of the proposed method to accommodate k-space undersampling and correct off-resonance were also demonstrated to be equal to conventional spatial domain design method.
+\subsection*{Applications and Extensions}
+This work was initially motivated by the observation that spatial domain parallel pulse designs can be very slow
+for 3D problems with large grid sizes, 
+requiring both many iterations and considerable computation per iteration. 
+It is anticipated that the proposed k-space domain algorithm will be most useful for these types of large $>$2D problems,
+which include 3D spatial designs \cite{malik2012tailored} and 2D and 3D spatial-spectral designs \cite{stenger2000three,yang2010four,davids2016fast}
+where full matrix construction and inversion is infeasible due to the problem size,
+and an iterative design can require several minutes to solve. 
+Furthermore, unlike an iterative spatial domain design the proposed algorithm does not need to be repeated if the target pattern changes.
+This means that it could have a considerable computational speed advantage for magnitude least-squares designs \cite{setsompop2008magnitude,malik:mrm:2015}. 
+The method could also be used to initialize spatial-domain designs to reduce the number of iterations required to reach a target cost; 
+Finally, while simple Tikhonov RF power regularization was used in the designs presented here,
+more sophisticated regularization could be incorporated to, e.g., control peak RF power via adaptive regularization,
+or to enforce array compression by projecting the weights into the null space of a compression matrix .
+In such designs, it would be beneficial to pre-compute and store the lower triangular elements of the $\bm{S}^H\bm{S}$ matrices
+so they need not be re-computed as the regularization changes over iterations.

### 2020-09-10 Manuscript/kPtx_paper.tex
WAG done with Methods
Wag all done, need to move to wiley template

@@
 \usepackage{verbatim}
+\usepackage{textcomp}
 
@@
 {\bf Purpose:}
-To improve the computational efficiency of parallel transmission pulse design. 
+To accelerate the design of multidimensional parallel transmission pulses. 
 \\[1em]
 {\bf Methods:}
-something
+A k-space domain parallel transmission pulse design algorithm was proposed that
+produces a sparse matrix relating a target excitation pattern to the pulses that produce it,
+and can be finely parallelized. 
+The algorithm was applied in simulations to the design of 3D SPINS pulses for inner volume excitation in the brain at 7 Tesla.
+It was characterized in terms of the dependence of computation time, excitation error, and required memory
+on algorithm parameters,
+and it was compared to the spatial domain pulse design method in terms computation time, excitation error,
+Gibbs ringing, and ability to compensate off-resonance.
 \\[1em]
 {\bf Results:}
-something
+The proposed algorithm achieved approximately 90\% faster pulse design compared to 
+an iterative spatial domain method, with the same number of parallel threads,
+with the tradeoff of increased excitation error and RMS RF amplitude. 
+It reduced the memory required to store the design matrix by 98\% compared to a full matrix solution.
+Even with a coarse design grid, the algorithm produced patterns that were free of Gibbs ringing.
+It was similarly sensitive to k-space undersampling as the spatial domain method,
+and was similarly capable of compensating for off-resonance.
 \\[1em]
 {\bf Conclusion:}
-something
+The proposed k-space domain algorithm accelerates and finely parallelizes parallel transmission pulse design,
+with a modest tradeoff of excitation error and RMS RF amplitude.
 \\[1em]

### 2020-09-10 Manuscript/Method.tex
wag finalizing for upload

@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=6cm]{kspace_PTX_Coil}
-	\caption{The 24-channel loop Tx array that was simulated in a human head model to obtain $B_1^+$ maps. 
-	The array has diameter 32 cm and height 28 cm. The 16 cm $\times$ 11 cm rectangular loops are arranged in 3 rows of 8.}
-	\label{fig:Coil}
-\end{figure}
-
 \par A SPINS excitation k-space trajectory \cite{malik2012tailored} (Figure \ref{fig:Target}b) with 5 mm max resolution was used for the designs. 
@@
 the dimensions of the $\bm{W}$ matrix were 16,632 RF pulse samples, by 196,608 target k-space locations.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{kSpace_PTX_Pattern_Trajectory}
-	\caption{(a) Middle axial, sagittal, and coronal slices of the target excitation pattern used for all pulse designs. 
-	(b) The SPINS trajectory used in the designs. 
-	(c) 10 ms minimum-time gradient waveforms that produce the SPINS trajectory.}
-	\label{fig:Target}
-\end{figure}
 

### 2020-09-10 Manuscript/Result.tex
Wag all done, need to move to wiley template
wag finalizing for upload

@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{ErrorMap}
-	\caption{\textcolor{red}{WAG: I think this is the figure that your example in Github should replicate.}
-	Normalized excitation patterns (top row) and error maps (bottom row) in central axial, sagittal and coronal slices 
-	for k-space domain (left) and spatial domain designs (right).}
-	\label{fig:ErrorMap}
-\end{figure}
 Figure \ref{fig:ErrorMap} shows simulated excitation patterns and error maps for the reference spatial and k-space domain designs. 
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{ComputationTime}
-	\caption{(a) k-Space computation time versus number of parallel threads, for patch and inclusion widths of 4 cycles/FOV. 
-	(b) Computation time (blue axis) and RMSE (red axis) versus patch width, for an inclusion width of 4 cycles/FOV and 16 threads. 
-	(c) Computation time (blue axis) and RMSE (red axis) versus inclusion width, for patch widths of 4 and 8 cycles/FOV, and 16 threads.}
-	\label{fig:ComputationTime}
-\end{figure}
 \subsection*{k-Space Algorithm Parameters}
@@
 
-\begin{figure}
-\centering
-\begin{tabular}{c | c}
-Inclusion Width & $\bm{W}$ Matrix Size (GB) \\
-\hline
-$\infty$ & 24.4 \\
-8 & 2.73 \\
-6 & 1.37 \\
-4 & 0.53 \\
-2 & 0.14
-\end{tabular}
-\caption{$\bm{W}$ matrix sizes in gigabytes (GB) versus inclusion width in cycles/FOV. 
-An inclusion width of $\infty$ corresponds to a full matrix solution.}
-\label{fig:wsize}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{L_curve}
-	\caption{L-curves for spatial domain and k-space domain pulse designs, 
-	repeated across five orders of magnitude of the methods' Tikhonov regularization parameters.
-	The k-space domain designs were repeated using patch and inclusion widths of four versus solving for the entire domain at once (`Patch / Inclusion Width = 4' versus `Full Patch'),
-	and using $B_1^+$ map product interpolation versus phase modulation to each trajectory location (`Interpolated $\bm{S}^H\bm{S}$ Matrices' versus
-	`Exact $\bm{S}^H\bm{S}$ Matrices').}
-	\label{fig:LCurves}
-\end{figure}
-
 \subsection*{L-Curves}
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{GibbsRinging}
-	\caption{Normalized error maps and RMSE for \textbf{(a)} spatial domain design and \textbf{(c)} k-space domain design with 6 mm iso-resolution, 32$\times$32$\times$24 design grid.
-Red arrows indicate the Gibbs ringing in low-resolution spatial domain design.
-\textbf{(b)} Normalized error map for spatial domain design with 3 mm iso-resolution, 64$\times$64$\times$48 design grid.}
-	\label{fig:GibbsRing}
-\end{figure}
-
 \subsection*{Gibbs Ringing}
@@
 Gibbs ringing is not apparent in either the 64$\times$64$\times$48 spatial domain error pattern or the 32$\times$32$\times$24 k-space domain error pattern. 
-The RMS RF amplitudes of the low resolution designs were both 0.05. 
+The RMS RF amplitudes of the low resolution designs were both 0.005. 
 Note that the error of the 64$\times$64$\times$48 spatial domain design is slightly higher than designs presented in other figures
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{ReductionFactor}
-	\caption{Normalized error maps and RMSEs for spatial domain design (first row) and k-space domain design (second row), 
-	using excitation k-space trajectories with different reduction factors (third row).
-	The reduction factors are referenced to the 10 ms trajectory in Figure \ref{fig:Target} (second column).}
-	\label{fig:kspace_PTX_Acceleration}
-\end{figure}
-
 \subsection*{Excitation k-Space Undersampling}
@@
 but error increased smoothly with increasing reduction factor, as it did for the spatial domain designs.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{OffResonance}
-	\caption{
-	(a) Normalized off-resonance map containing a Gaussian distortion centered above the frontal sinus, 
-	to mimic air-tissue susceptibility difference-induced $B_0$ inhomogeneity.
-	(b) Normalized excitation maps and RMSEs for spatial domain design with off-resonance correction (first row), 
-	and k-space domain design without and with off-resonance correction (second and third rows).}
-	\label{fig:kspace_PTX_B0}
-\end{figure}
 

### 2020-09-10 Manuscript/kPtx_paper.tex
wag finalizing for upload

@@
 \begin{flushleft}
+\vspace{-0.5cm}
 $^1$Vanderbilt University Institute of Imaging Science, Nashville, TN, United States\\
@@
 \par
-Word Count: Approximately 3550 \\
+Word Count: Approximately 5500 \\
 *Corresponding author: \\
@@
 
-\bibliographystyle{unsrt}  % cse doesn't work
+\bibliographystyle{cse}  % cse doesn't work
 \bibliography{kPtx_paper}
@@
 \pagebreak
+%(Please see main document for caption with intended math typesetting)
+
+\begin{figure}
+	\centering
+	%\includegraphics[width=\textwidth]{kspace_PTX_Patch}
+	\caption{(a) A target point $\vec{k}_j$ and the nearby trajectory points that are included when calculating 
+	RF pulse weight contributions from this point.
+	Inclusion width is defined as the distance from each target location $\vec{k}_j$ within which 
+	which all trajectory points are considered when solving for the $j$-th column of the design ($\bm{W}$) matrix.
+	(b) Calculation of the $\bm{W}$ matrix can be performed column-by-column for each target location $\vec{k}_j$,
+	or patches of target points can be solved for jointly. 
+	Here the 16 columns of $\bm{W}$ for a 4 $\times$ 4 patch of target points are solved together,
+	and an inclusion width of 4 cycles/FOV dictates that all trajectory points within a 12 $\times$ 12 region
+	centered on the patch are considered in the calculation.}
+	\label{fig:Patch}
+\end{figure}
+
+\begin{figure}
+	\centering
+	%\includegraphics[width=6cm]{kspace_PTX_Coil}
+	\caption{The 24-channel loop Tx array that was simulated in a human head model to obtain $B_1^+$ maps. 
+	The array has diameter 32 cm and height 28 cm. The 16 cm $\times$ 11 cm rectangular loops are arranged in 3 rows of 8.}
+	\label{fig:Coil}
+\end{figure}
+
+\begin{figure}
+	\centering
+	%\includegraphics[width=\textwidth]{kSpace_PTX_Pattern_Trajectory}
+	\caption{(a) Middle axial, sagittal, and coronal slices of the target excitation pattern used for all pulse designs. 
+	(b) The SPINS trajectory used in the designs. 
+	(c) 10 ms minimum-time gradient waveforms that produce the SPINS trajectory.}
+	\label{fig:Target}
+\end{figure}
+
+\begin{figure}
+	\centering
+	%\includegraphics[width=\textwidth]{ErrorMap}
+	\caption{ %\textcolor{red}{WAG: I think this is the figure that your example in Github should replicate.}
+	Normalized excitation patterns (top row) and error maps (bottom row) in central axial, sagittal and coronal slices 
+	for k-space domain (left) and spatial domain designs (right).}
+	\label{fig:ErrorMap}
+\end{figure}
+
+\begin{figure}
+	\centering
+	%\includegraphics[width=\textwidth]{ComputationTime}
+	\caption{(a) k-Space computation time versus number of parallel threads, for patch and inclusion widths of 4 cycles/FOV. 
+	(b) Computation time (blue axis) and RMSE (red axis) versus patch width, for an inclusion width of 4 cycles/FOV and 16 threads. 
+	(c) Computation time (blue axis) and RMSE (red axis) versus inclusion width, for patch widths of 4 and 8 cycles/FOV, and 16 threads.}
+	\label{fig:ComputationTime}
+\end{figure}
+
+\begin{figure}
+\centering
+%\begin{tabular}{c | c}
+%Inclusion Width & $\bm{W}$ Matrix Size (GB) \\
+%\hline
+%$\infty$ & 24.4 \\
+%8 & 2.73 \\
+%6 & 1.37 \\
+%4 & 0.53 \\
+%2 & 0.14
+%\end{tabular}
+\caption{$\bm{W}$ matrix sizes in gigabytes (GB) versus inclusion width in cycles/FOV. 
+An inclusion width of $\infty$ corresponds to a full matrix solution.}
+\label{fig:wsize}
+\end{figure}
+
+\begin{figure}
+	\centering
+	%\includegraphics[width=\textwidth]{L_curve}
+	\caption{L-curves for spatial domain and k-space domain pulse designs, 
+	repeated across five orders of magnitude of the methods' Tikhonov regularization parameters.
+	The k-space domain designs were repeated using patch and inclusion widths of four versus solving for the entire domain at once (`Patch / Inclusion Widths = 4' versus `Patch / Inclusion Widths = $\infty$'),
+	and using $B_1^+$ map product interpolation versus phase modulation to each trajectory location (`Interpolated Matrices' versus
+	`Exact Matrices').}
+	\label{fig:LCurves}
+\end{figure}
+
+\begin{figure}
+	\centering
+	%\includegraphics[width=\textwidth]{GibbsRinging}
+	\caption{Normalized error maps and RMSEs for 
+	(a) pulses designed using a trajectory that reaches 6 mm isotropic resolution
+	and the spatial domain algorithm with a 32$\times$32$\times$24 grid, 
+	(b) pulses designed using the same trajectory and the spatial domain algorithm with a 64$\times$64$\times$48 grid,  
+	and (c) pulses designed using the same trajectory and the k-space domain algorithm with a 32$\times$32$\times$24 design grid. 
+	Red arrows indicate Gibbs ringing in the 32$\times$32$\times$24 spatial domain design.}
+	\label{fig:GibbsRing}
+\end{figure}
+
+\begin{figure}
+	\centering
+	%\includegraphics[width=\textwidth]{ReductionFactor}
+	\caption{Normalized error maps and RMSEs for spatial domain design (first row) and k-space domain design (second row), 
+	using excitation k-space trajectories with different reduction factors (third row).
+	The reduction factors are referenced to the 10 ms trajectory in Figure \ref{fig:Target} (second column).}
+	\label{fig:kspace_PTX_Acceleration}
+\end{figure}
+
+\begin{figure}
+	\centering
+	%\includegraphics[width=\textwidth]{OffResonance}
+	\caption{
+	(a) Normalized off-resonance map containing a Gaussian distortion centered above the frontal sinus, 
+	to mimic air-tissue susceptibility difference-induced $B_0$ inhomogeneity.
+	(b) Normalized excitation maps and RMSEs for spatial domain design with off-resonance correction (first row), 
+	and k-space domain design without and with off-resonance correction (second and third rows).}
+	\label{fig:kspace_PTX_B0}
+\end{figure}
 

### 2020-09-10 Manuscript/kPtx_paper.tex
wag brought bib into main doc

@@
 \usepackage{ulem}
-\usepackage{verbatim}
+%\usepackage{verbatim}
 \usepackage{textcomp}
+\usepackage{hyperref}
+\hypersetup{colorlinks=false,urlcolor=blue,linkcolor=blue}
+\usepackage{caption}
 
@@
 
-\usepackage[noend]{algpseudocode}
+%\usepackage[noend]{algpseudocode}
 
@@
 
-\usepackage{todonotes}
+%\usepackage{todonotes}
 
-\graphicspath{{Figure/}}
+%\graphicspath{{Figure/}}
 
@@
 
-\bibliographystyle{cse}  % cse doesn't work
-\bibliography{kPtx_paper}
+\bibliographystyle{cse}
+%\bibliography{kPtx_paper}
+
+\begin{thebibliography}{10}
+\providecommand{\url}[1]{\texttt{#1}}
+\providecommand{\urlprefix}{URL }
+
+\bibitem{Katscher:2003:Magn-Reson-Med:12509830}
+Katscher U, B{\"o}rnert P, Leussler C, van~den Brink JS.
+\newblock Transmit {SENSE}.
+\newblock Magn Reson Med 2003;\hspace{0pt}49:144--150.
+
+\bibitem{zhu2004parallel}
+Zhu Y.
+\newblock Parallel excitation with an array of transmit coils.
+\newblock Magn Reson Med 2004;\hspace{0pt}51:775--784.
+
+\bibitem{malik:mrm:2015}
+Malik SJ, Hajnal JV.
+\newblock Phase relaxed localized excitation pulses for inner volume fast spin
+  echo imaging.
+\newblock Magn Reson Med 2016;\hspace{0pt}76:848--861.
+
+\bibitem{mooiweer:2016}
+Mooiweer R, Sbrizzi A, Raaijmakers AJE, Van~den Berg CAT, Luijten PR, Hoogduin
+  H.
+\newblock Combining a reduced field of excitation with {SENSE}-based parallel
+  imaging for maximum imaging efficiency.
+\newblock Magn Reson Med 2016;\hspace{0pt}78:88--96.
+
+\bibitem{Zhang:2007:Magn-Reson-Med:16526012}
+Zhang Z, Yip CY, Grissom W, Noll DC, Boada FE, Stenger VA.
+\newblock Reduction of transmitter {B1} inhomogeneity with transmit {SENSE}
+  slice-select pulses.
+\newblock Magn Reson Med 2007;\hspace{0pt}57:842--847.
+
+\bibitem{cloos:kpstd:2012}
+Cloos MA, Boulant N, Luong M, Ferrand G, Giacomini E, Le~Bihan D, Amadon A.
+\newblock {$k_T$}-{Points}: {Short} three-dimensional tailored {RF} pulses for
+  flip-angle homogenization over an extended volume.
+\newblock Magn Reson Med 2011;\hspace{0pt}67:72--80.
+
+\bibitem{deng:2009}
+Deng W, Yang C, Alagappan V, Wald LL, Boada FE, Stenger VA.
+\newblock Simultaneous z-shim method for reducing susceptibility artifacts with
+  multiple transmitters.
+\newblock Magn Reson Med 2009;\hspace{0pt}61:255--259.
+
+\bibitem{Grissom:2006:MRM}
+Grissom WA, Yip CY, Zhang Z, Stenger VA, Fessler JA, Noll DC.
+\newblock Spatial domain method for the design of {RF} pulses in multicoil
+  parallel excitation.
+\newblock Magn Reson Med 2006;\hspace{0pt}56:620--9.
+
+\bibitem{malik2012tailored}
+Malik SJ, Keihaninejad S, Hammers A, Hajnal JV.
+\newblock Tailored excitation in {3D} with spiral nonselective {(SPINS) RF}
+  pulses.
+\newblock Magn Reson Med 2012;\hspace{0pt}67:1303--1315.
+
+\bibitem{davids2016fast}
+Davids M, Schad LR, Wald LL, Guerin B.
+\newblock Fast three-dimensional inner volume excitations using parallel
+  transmission and optimized k-space trajectories.
+\newblock Magn Reson Med 2016;\hspace{0pt}76:1170--1182.
+
+\bibitem{orzada:2019}
+Orzada S, Solbach K, Gratz M, Brunheim S, Fiedler TM, Johst S, Bitz AK,
+  Shooshtary S, Abuelhaija A, Voelker MN, Rietsch SHG, Kraff O, Maderwald S,
+  Fl\"oser M, Oehmigen M, Quick HH, Ladd ME.
+\newblock A 32-channel parallel transmit system add-on for 7t mri.
+\newblock PLOS ONE 2019;\hspace{0pt}14:1--20.
+
+\bibitem{deng:2011}
+Deng W, Yang C, Stenger VA.
+\newblock Accelerated multidimensional radiofrequency pulse design for parallel
+  transmission using concurrent computation on multiple graphics processing
+  units.
+\newblock Magn Reson Med 2011;\hspace{0pt}65:363--369.
+
+\bibitem{setsompop2008magnitude}
+Setsompop K, Wald L, Alagappan V, Gagoski B, Adalsteinsson E.
+\newblock Magnitude least squares optimization for parallel radio frequency
+  excitation design demonstrated at 7 {Tesla} with eight channels.
+\newblock Magn Reson Med 2008;\hspace{0pt}59:908--915.
+
+\bibitem{brunner2010optimal}
+Brunner DO, Pruessmann KP.
+\newblock Optimal design of multiple-channel {RF} pulses under strict power and
+  {SAR} constraints.
+\newblock Magn Reson Med 2010;\hspace{0pt}63:1280--1291.
+
+\bibitem{hoyos:tmi:2014}
+Hoyos-Idrobo A, Weiss P, Massire A, Amadon A, Boulant N.
+\newblock On variant strategies to solve the magnitude least squares
+  optimization problem in parallel transmission pulse design under strict {SAR}
+  and power constraints.
+\newblock IEEE Trans Med Imag 2014;\hspace{0pt}33:739--748.
+
+\bibitem{fessler2005toeplitz}
+Fessler JA, Lee S, Olafsson VT, Shi HR, Noll DC.
+\newblock Toeplitz-based iterative image reconstruction for {MRI} with
+  correction for magnetic field inhomogeneity.
+\newblock IEEE Trans Sig Proc 2005;\hspace{0pt}53:3393--3402.
+
+\bibitem{grissom:ismrm18}
+Grissom WA.
+\newblock {k-Space} domain parallel transmit pulse design.
+\newblock In Proceedings 26th Scientific Meeting, International Society for
+  Magnetic Resonance in Medicine, Paris. 2018;\hspace{0pt} p. 3396.
+
+\bibitem{luo2019grappa}
+Luo T, Noll DC, Fessler JA, Nielsen JF.
+\newblock A {GRAPPA} algorithm for arbitrary {2D/3D} non-{Cartesian} sampling
+  trajectories with rapid calibration.
+\newblock Magn Reson Med 2019;\hspace{0pt}82:1101--1112.
+
+\bibitem{lustig2008fast}
+Lustig M, Kim SJ, Pauly JM.
+\newblock A fast method for designing time-optimal gradient waveforms for
+  arbitrary k-space trajectories.
+\newblock {IEEE} Trans Med Imag 2008;\hspace{0pt}27:866--873.
+
+\bibitem{Fessler:2003fk}
+Fessler JA, Sutton BP.
+\newblock Nonuniform fast {Fourier} transforms using min-max interpolation.
+\newblock IEEE Trans Sig Proc 2003;\hspace{0pt}51:560--574.
+
+\bibitem{stenger2000three}
+Stenger VA, Boada FE, Noll DC.
+\newblock Three-dimensional tailored {RF} pulses for the reduction of
+  susceptibility artifacts in {$T_2^*$}-weighted functional {MRI}.
+\newblock Magn Reson Med 2000;\hspace{0pt}44:525--531.
+
+\bibitem{yang2010four}
+Yang C, Deng W, Alagappan V, Wald LL, Stenger VA.
+\newblock Four-dimensional spectral-spatial {RF} pulses for simultaneous
+  correction of {B1+} inhomogeneity and susceptibility artifacts in
+  {T2*}-weighted {MRI}.
+\newblock Magn Reson Med 2010;\hspace{0pt}64:1--8.
+
+\end{thebibliography}
 

### 2020-10-01 Manuscript_r1/Conclusion.tex
wag started r1

--- 2020-09-10 Manuscript/Conclusion.tex
@@
 Finally, while simple Tikhonov RF power regularization was used in the designs presented here,
-more sophisticated regularization could be incorporated to, e.g., control peak RF power via adaptive regularization,
-or to enforce array compression by projecting the weights into the null space of a compression matrix .
+more sophisticated regularization could be incorporated to, e.g., control peak RF power via adaptive regularization \cite{Yip:2005:Magn-Reson-Med:16155881},
+or to enforce array compression by projecting the weights into the null space of a compression matrix \cite{cao2016array}.
 In such designs, it would be beneficial to pre-compute and store the lower triangular elements of the $\bm{S}^H\bm{S}$ matrices
 so they need not be re-computed as the regularization changes over iterations.
+
+\section*{Conclusion}
+The proposed k-space domain algorithm accelerates and finely parallelizes parallel transmission pulse design,
+with a modest tradeoff of excitation error and RMS RF amplitude.

### 2020-10-01 Manuscript_r1/coverletter/coverletter.tex
wag started r1

\documentclass[11pt]{article}

\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{marvosym}
\usepackage{fancyhdr}
\usepackage{ifpdf}
\ifpdf
  \usepackage[pdftex]{graphicx}
\else
  \usepackage[dvips]{graphicx}\fi

\textwidth 6.6in
%\textheight 9in
%\headheight 2in
\voffset 0.65in
\headheight 3in

\pagestyle{fancy}
\rhead{\includegraphics[width=3in]{vu02a.pdf}}
\chead{}
\lhead{\includegraphics[width=0.7in]{New_VUIIS_Logo.png}}
\lfoot{}
\cfoot{\small 1161 21st Ave South, AA-3114 MCN, Nashville, TN 37232-2310    Tel: (919) 649 4699  Fax: (615) 322 0734}
\rfoot{}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

\usepackage[scale=0.775]{geometry}
\setlength{\parindent}{0pt}
\addtolength{\parskip}{6pt}

\def\firstname{William A.}
\def\familyname{Grissom, Ph.D.}
\def\FileAuthor{\firstname \familyname}
\def\FileTitle{\firstname \familyname's Cover Letter}
\def\FileSubject{Support Letter}
\def\FileKeyWords{\firstname \familyname, Cover Letter}

\renewcommand{\ttdefault}{pcr}

\usepackage{url}
\urlstyle{tt}
\ifpdf
  \usepackage[pdftex,pdfborder=0,breaklinks,baseurl=http://,pdfpagemode=None,pdfstartview=XYZ,pdfstartpage=1]{hyperref}
  \hypersetup{
    pdfauthor   = \FileAuthor,%
    pdftitle    = \FileTitle,%
    pdfsubject  = \FileSubject,%
    pdfkeywords = \FileKeyWords,%
    pdfcreator  = \LaTeX,%
    pdfproducer = \LaTeX}
\else
  \usepackage[dvips]{hyperref}
\fi

\begin{document}
\sffamily   % for use with a résumé using sans serif fonts;
%\rmfamily  % for use with a résumé using serif fonts;
%\hfill%
%\begin{minipage}[t]{.6\textwidth}
\raggedright%
{\bfseries \firstname~\familyname}\\[.35ex]
\small{\itshape%
Associate Professor of Biomedical Engineering\\
Institute of Imaging Science\\
Vanderbilt University\\}
\Letter~\href{mailto:will.grissom@vanderbilt.edu}{will.grissom@vanderbilt.edu}\\[2em]
{\bfseries Prof. Peter Jezzard}\\[.35ex]
\small{\itshape
Editor in Chief\\
Magnetic Resonance in Medicine\\[1em]}
%\end{minipage}
%
%\begin{minipage}[t]{.51\textwidth}
%\raggedright%
%{\bfseries Chair of Graduate Admissions \\ 
%Center for Biomedical Engineering \\
%University of Kentucky}\\[.35ex]
%\end{minipage}
%\hfill % US style
%\\[1em] % UK style
\large
\hfill\begin{minipage}[t]{\textwidth} % was 0.4\textwidth when addressee was there
\raggedleft % US style
\today
%April 6, 2006 % US informal style
%05/04/2006 % UK formal style
\end{minipage}\\[2em]
\raggedright
Dear Dr. Jezzard,\\[1.5em]
%
I would like to submit the manuscript `k-Space Domain Parallel Transmit Pulse Design' to be considered
for publication as a Full Paper in Magnetic Resonance in Medicine. 
It describes a new k-space-based algorithm for designing parallel transmission pulses that can be finely parallelized
and may be especially useful for designing $>$ 2D dimensional pulses with large numbers of transmit channels
for ultra-high field MRI.

\par Thank you very much for considering this manuscript. 
Please do not hesitate to contact me if you have any questions.\\[1.5em]
% 
%Yours sincerely,\\[2em] % if the opening is "Dear Mr(s) Doe,"
Sincerely,\\[1.5em] % if the opening is "Dear Sir or Madam,"
%
%\vspace{3cm}
%\includegraphics[scale=0.2]{/Users/guille/Documents/signature.png}\\[1.5em]
{\bfseries Will Grissom}\\
%
\vfill%
%{\slshape Enclosure}

\end{document}

### 2020-10-01 Manuscript_r1/response_to_reviews.tex
wag added response doc

\documentclass[11pt]{article}
\usepackage{booktabs,ulem,cite,caption,amsmath,graphicx,wrapfig,sidecap,datetime,fancyhdr,bm}
\usepackage{array,color,multirow,colortbl}

\usepackage{hyperref}
\hypersetup{colorlinks=false,urlcolor=blue,linkcolor=black,citecolor=black}

\usepackage[numbers,sort&compress]{natbib}
\usepackage{url}

\providecommand{\shadeRow}{\rowcolor[rgb]{0.75, 0.75, 0.75}}

\renewcommand{\familydefault}{\sfdefault}
\renewcommand{\rmdefault}{phv} % Arial
\renewcommand{\sfdefault}{phv} % Arial

\frenchspacing % no extra space after periods (check wikipedia, this is an old battle that latex is on the wrong side of!)

\raggedbottom		% Don't add any random white space (annoying!)
\clubpenalty=10000 	% Absolutely no orphans.
\widowpenalty=10000	% Absolutely no widows.

\newcommand{\dg}{$^\circ$}
\newcommand{\by}{$\times$ }
\newcommand{\bonep}{$B_1^+$}
\newcommand{\bzero}{$B_0$}

%
\newcommand{\mywrapfig}[6][-5mm]                % Wrapped figure.
        {
        \begin{wrapfigure}{#2}{#4}
                \begin{center}
                \vspace{-10mm}
		\includegraphics[width=#4]{figures/#6}
                \end{center}
                \vspace{-4mm}
                \caption{\textit{#5}}
                \label{fig:#3}
                \vspace{#1}
        \end{wrapfigure}
	}

\newcommand{\myfig}[2][placeholder]	% \myfig[position]{file}{caption}
	{
	\begin{figure}[htb]
	\begin{center}
	\vspace{-4mm}
	\includegraphics[width=0.95\columnwidth]{figures/#1}
	\caption{\textit{#2}}
	\label{fig:#1}
	\end{center}
	\vspace{-8mm}
	\end{figure}
	}

% -- Simple side caption (SC) Figure command
\newcommand{\myscfig}[4][0.7]     % [1] ratio of caption to figure
				  % {2} width of figure
				  % {3} filename
				  % {4} caption
        {
        \begin{SCfigure}[#1][h]
        \centering
        \includegraphics[width=#2]{figures/#3}
        \caption{\textit{#4}}
        \label{fig:#3}
        \centering
        \end{SCfigure}
        }

\newcommand{\pagebreaksubmit}	 
	{\newpage \clearpage}		% Uncomment in final submission.
	%{ }

%
% what is  a jot? 2ex!
%
\jot 2ex

%
% page/column layout
%
\markright{plain}
\headsep 0in
\topmargin 0.5in
\headheight 0in
\hoffset -0.5in
\voffset -1in
%\headheight 0in
\oddsidemargin 0in%-.31in
\evensidemargin 0in%-.31in
\textwidth 7.5in
\textheight 10in
\marginparsep 0in
%\columnsep 15pt
%\columnsep 20pt
\intextsep 18pt
\setcounter{tocdepth}{4} 
\setcounter{secnumdepth}{3}

%
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\z@}%
                                    {0.75ex \@plus1ex \@minus0.0ex}%
                                    {-1em}%
                                    {\reset@font\normalsize\bfseries}}

\renewcommand{\subparagraph}{\@startsection{paragraph}{5}{\z@}%
                                    {0.75ex \@plus1ex \@minus0.0ex}%
                                    {-1em}%
                                    {\reset@font\normalsize\itshape}}

% ---- Reduce the space after sections. ------

\newcommand{\mysection}[1]{\vspace{-3mm}\section{#1}\vspace{-6mm}}
\newcommand{\mysectionstar}[1]{\vspace{0mm}\section*{#1}\vspace{0mm}}
\newcommand{\mysubsectionstar}[1]{\vspace{0mm}\subsection*{#1}\vspace{0mm}}
\newcommand{\mysubsection}[1]{\vspace{-3mm}\subsection{#1}\vspace{-3mm}}

\newcommand{\mysubsubsection}[1]{\vspace{-2mm}\subsubsection{#1}\vspace {-3mm}}
\newcommand{\mysubsubsectionstar}[1]{\vspace{0mm}\subsubsection*{#1}\vspace{-3mm}}
\newcommand{\myparagraph}[1]{\vspace{-2mm}\paragraph{#1: }}
\newcommand{\mysubparagraph}[1]{\underline{#1:} }
\newcommand{\mystudyparagraph}[1]{\vspace{-2mm}\underline{#1:} }

\setlength{\parindent}{0.5in}

\makeatother

%
% make the bibliography skip smaller
%
\def\thebibliography#1{ \list
  {[\arabic{enumi}]}{\settowidth\labelwidth{[#1]}
    \leftmargin\labelwidth
    \setlength{\itemsep}{2pt}
    \setlength{\parsep}{1pt}
    \advance\leftmargin\labelsep
    \usecounter{enumi}}
    \def\newblock{\hskip .11em plus .33em minus -.07em}
    \sloppy
    \sfcode`\.=1000\relax}

%
%  Alphabetic section numbers
%
\renewcommand{\thesection}{\Alph{section}}

%
% caption: smaller font, bold face "Figure X"
%
\renewcommand{\captionsize}{\small}
\renewcommand{\captionlabelfont}{\bf}
\setlength{\abovecaptionskip}{0pt}
\setlength{\belowcaptionskip}{12pt}

\linespread{1.05}

\begin{document}

%\raggedright

%\pagestyle{myheadings}
\markboth{1-}{}	% Second field hacked out in annotate-page.sty

\onecolumn

%\setlength{\parsep}{5pt}
\setlength{\parskip}{0pt}

\clearpage
\newpage
				% To turn off page numbering, uncomment!
\pagestyle{empty}		% No page numbers!

\footskip 15pt

\mysubsectionstar{Response to Reviewer Critiques}
We appreciate the reviewers' enthusiasm for the work and their constructive criticism and helpful suggestions to improve the manuscript.
Below we have numbered each specific critique and provide our responses.

%\\[0.2em]
%\indent{\it \textcolor{red}{TODO: Note that we add validation of integrated power.}}
%\\[1.2em]
\mysubsectionstar{Referee 1}
{\bf R1.1:} P2L26. Please replace ``three'' with ``four''.
\\[0.2em] 
\indent{\it \textcolor{blue}{Done.}}
\\[1.2em]
{\bf R1.2:} P14L37. Please remove ``B1+ SVT''
\\[0.2em]
\indent{\it \textcolor{blue}{Done.}}

\mysubsectionstar{Referee 2}
{\bf R2.1:} Upon rereading the manuscript, however, I did realize one potential pitfall of the proposed matrix implementation shown in Fig. 1. Using a simple concatenation of power splitters, attenuators and phase shifters will significantly (possibly dramatically) reduce the efficiency of the virtual coil. This means that although fewer parallel transmit pathways could be used, the driving amplifiers need to be significantly more powerful (more then N times, where N is the coil compression factor) to compensate for the power dissipated in the attenuation stage of the matrix. On top of that, there will be losses in the various matrix components and connections. Although a bigger amplifier would probably still be more cost efficient than duplicating the entire RF-chain, most current 7T systems are equipped with only relatively small simplifiers (Typically 8kW in total). For some applications, especially in body imaging, the full 8kW is already considered a limiting factor.
\par In my opinion it is not critical, but I think it may be worthwhile to highlight this particular aspect in the discussion. I would like to leave it to the authors discretion if they would like to incorporate this final observation.
\\[0.2em]
\indent{\it \textcolor{blue}{We agree that due to losses in the coil compression network, more RF
power will be required to create a given RF field strength compared to a full set of RF power amplifiers
driving the same coil array. At this early stage it is rather unclear just what those losses will be,
but we have added a statement to the Discussion that there will be some power loss so the total RF power requirements will
be increased.}}

\end{document}

### 2020-10-02 Manuscript_r1/Conclusion.tex
wag cleaned up off-resonance section, added some citations

@@
 so they need not be re-computed as the regularization changes over iterations.  
+\textcolor{blue}{Peak power could also be controlled in k-space domain designs using pTx VERSE \cite{Lee:2011:MRM} or the iterative re-VERSEit technique \cite{lee2009tod}.} \revbox{R2.X}
+\textcolor{blue}{It may also be possible to use the k-space domain method to rapidly design large-tip-angle pulses via the direct linear class of large-tip-angle pulses method \cite{Xu:2008aa} or the additive angle methods \cite{grissom:mrm:2008};
+the latter method alternates between small-tip-angle designs that could be solved by the k-space method and Bloch simulations to update the target pattern.} \revbox{R2.X}
 

### 2020-10-02 Manuscript_r1/Theory.tex
wag cleaned up off-resonance section, added some citations

--- 2020-08-31 Manuscript/Theory.tex
@@
+%!TEX root = kPtx_paper.tex
 \section*{Theory}
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{kspace_PTX_Patch}
-	\caption{(a) A target point $\vec{k}_j$ and the nearby trajectory points that are included when calculating 
-	RF pulse weight contributions from this point.
-	Inclusion width is defined as the distance from each target location $\vec{k}_j$ within which 
-	which all trajectory points are considered when solving for the $j$-th column of the design ($\bm{W}$) matrix.
-	(b) Calculation of the $\bm{W}$ matrix can be performed column-by-column for each target location $\vec{k}_j$,
-	or patches of target points can be solved for jointly. 
-	Here the 16 columns of $\bm{W}$ for a 4 $\times$ 4 patch of target points are solved together,
-	and an inclusion width of 4 cycles/FOV dictates that all trajectory points within a 12 $\times$ 12 region
-	centered on the patch are considered in the calculation.}
-	\label{fig:Patch}
-\end{figure}
-
 \subsection*{Efficient $\bm{S}^H\bm{S}$ matrix construction}
@@
 Mathematically, the time-segmented model is given by:
+\textcolor{blue}{
 \begin{equation}
-e^{\imath \Delta\omega_j (t_i-T) }\approx\sum_{l=1}^{L} g_l(t_i) e^{\imath \Delta\omega_j \breve{t}_l},
+e^{\imath \Delta\omega(\vec{x}_j) (t_i-T) }\approx\sum_{l=1}^{L} b_l(t_i) h_{l}(\vec{x}_j) ,
 \end{equation}
-where $\Delta\omega_j$ is the off-resonance frequency at location $\vec{x}_j$, 
+where $\Delta\omega(\vec{x}_j)$ is the off-resonance frequency at $\vec{x}_j$, 
 $i$ indexes time points in the pulse, 
@@
 and $l$ indexes the $L$ time segments, where $L$ is typically between 4 and 8. 
-$g_{il}=b_{l}(t_i)$ are the temporal interpolators that multiply into the RF samples,
-and $h_{lj}=e^{\imath \Delta\omega_j\breve{t}_l}$ are the off-resonance phase shifts 
+The $b_{l}(t_i)$ functions are temporal interpolators that multiply into the RF samples and are determined by
+numerical optimization as described in Ref. \cite{fessler2005toeplitz},
+and $h_{l}(\vec{x}_j) = e^{\imath \Delta\omega(\vec{x}_j)\breve{t}_l}$ are the off-resonance phase shifts 
 applied to the excitation patterns produced by the RF pulse time segments centered at time points $\{\breve{t}_l: l = 1, \dots, L\}$.
@@
 \begin{equation}
-	\delta(\vec{k}-\vec{k}_j)=\sum_{l = 1}^L \sum_{i=1}^{N_t}\sum_{c=1}^{N_c} w_c(\vec{k}_i) g_l(t_i) \tilde{s}_{cl} (\vec{k}-\vec{k}_i), 
+	\delta(\vec{k}-\vec{k}_j)=\sum_{l = 1}^L \sum_{i=1}^{N_t}\sum_{c=1}^{N_c} w_c(\vec{k}_i) b_l(t_i) \tilde{s}_{cl} (\vec{k}-\vec{k}_i), 
 \end{equation}
 where $\tilde{s}_{cl}(\vec{k})$ is the Fourier transform of the product of channel $c$'s $B_1^+$ map and time segment $l$'s 
-off-resonance phase exponential. 
+off-resonance phase shift $h_l(\vec{x}_j)$. 
 We can then write the equivalent of Equation \ref{eq:MatrixForm} with the off-resonance model:
 \begin{equation}
-	\sum_{l=1}^L \bm{S}_l \textrm{diag}(g_{il}) \bm{w}_j = \bm{\delta}_j,
+	\sum_{l=1}^L \bm{S}_l \textrm{diag}(b_{l}(t_i)) \bm{w}_j = \bm{\delta}_j,
 \end{equation} 
-where the matrix $\bm{S}_l$ is now formed from the $N_c  L$ Fourier transforms of the $B_1^+$ map and off-resonance
-phase exponential products.  
+where the matrix $\bm{S}_l$ is now formed from the $N_c  L$ Fourier transforms of the $B_1^+$ map and $h_l(\vec{x}_j)$ products.} \revbox{R1.X}  
 Efficient construction of the $\bm{S}^{H}\bm{S}$ matrix follows much the same procedure as without

### 2020-10-02 Manuscript_r1/kPtx_paper.tex
wag cleaned up off-resonance section, added some citations

--- 2020-09-10 Manuscript/kPtx_paper.tex
@@
 
+\bibitem{Yip:2005:Magn-Reson-Med:16155881}
+Yip CY, Fessler JA, Noll DC.
+\newblock Iterative {RF} pulse design for multidimensional, small-tip-angle
+  selective excitation.
+\newblock Magn Reson Med 2005;\hspace{0pt}54:908--917.
+
+\bibitem{cao2016array}
+Cao Z, Yan X, Grissom WA.
+\newblock Array-compressed parallel transmit pulse design.
+\newblock Magn Reson Med 2016;\hspace{0pt}76:1158--1169.
+
+\bibitem{Lee:2011:MRM}
+D.~Lee, W.~A. Grissom, M.~Lustig, A.~B. Kerr, P.~P. Stang, and J.~M. Pauly.
+\newblock {VERSE}-guided numerical {RF} pulse design: A fast method for peak
+  {RF} power control.
+\newblock Magn Reson Med 2012; 67:353--362.
+
+\bibitem{lee2009tod}
+D.~Lee, M.~Lustig, W.~A. Grissom, and J.~M. Pauly.
+\newblock Time-optimal design for multidimensional and parallel transmit
+  variable-rate selective excitation.
+\newblock Magn Reson Med 2009, 61(6):1471--1479.
+
+\bibitem{Xu:2008aa}
+D.~Xu, K.~F. King, Y.~Zhu, G.~C. McKinnon, and Z.-P. Liang.
+\newblock Designing multichannel, multidimensional, arbitrary flip angle {RF}
+  pulses using an optimal control approach.
+\newblock Magn Reson Med 2008, 59(3):547--560.
+
+\bibitem{grissom:mrm:2008}
+W.~A. Grissom, C.~Y. Yip, S.~M. Wright, J.~A. Fessler, and D.~C. Noll.
+\newblock Additive angle method for fast large-tip-angle {RF} pulse design in
+  parallel excitation.
+\newblock Magn Reson Med 2008, 59(4):779--87.
+
 \end{thebibliography}

### 2020-10-02 Manuscript_r1/Conclusion.tex
wag R1 stuff

--- 2020-10-01 Manuscript_r1/Conclusion.tex
@@
 It is anticipated that the proposed k-space domain algorithm will be most useful for these types of large $>$2D problems,
-which include 3D spatial designs \cite{malik2012tailored} and 2D and 3D spatial-spectral designs \cite{stenger2000three,yang2010four,davids2016fast}
-where full matrix construction and inversion is infeasible due to the problem size,
+which include 3D spatial designs \cite{malik2012tailored,davids2016fast} and \textcolor{blue}{2D and 3D spatial-spectral designs \cite{stenger2000three,setsompop2009,Malik:2010aa,yang2010four}
+where full matrix construction and inversion is infeasible due to the problem size, }\revbox{R1.X}
 and an iterative design can require several minutes to solve. 
@@
 so they need not be re-computed as the regularization changes over iterations.  
+\textcolor{blue}{Peak power could also be controlled in k-space domain designs using pTx VERSE \cite{Lee:2011:MRM} or the iterative re-VERSEit technique \cite{lee2009tod}.} \revbox{R2.X}
+\textcolor{blue}{It may also be possible to use the k-space domain method to rapidly design large-tip-angle pulses via the direct linear class of large-tip-angle pulses method \cite{Xu:2008aa} or the additive angle method \cite{grissom:mrm:2008};
+the latter alternates between small-tip-angle designs that could be solved by the k-space method and Bloch simulations to update the target pattern.} \revbox{R2.X}
 

### 2020-10-02 Manuscript_r1/Introduction.tex
wag R1 stuff

--- 2020-08-17 Manuscript/Introduction.tex
@@
+%!TEX root = kPtx_paper.tex
 \section* {Introduction}
@@
 or using an iterative method.
+% While under certain conditions the original k-space and spatial domain methods are equivalent \cite{Grissom:2006:MRM},
+% 
 The spatial domain method is mathematically straightforward 
@@
 it can have prohibitive computational requirements when the number of coils and the number of dimensions become large, 
-for example in three-dimensional \cite{malik2012tailored,davids2016fast} or spectral-spatial pulse designs, 
+for example in three-dimensional \cite{malik2012tailored,davids2016fast} or spectral-spatial pulse designs \cite{stenger2000three,setsompop2009,Malik:2010aa,yang2010four}, 
 when there is a large number of coils \cite{orzada:2019},
@@
 The results show how computation time and accuracy depend on the parameters of the patch-wise parallelization,
-and how well the algorithm accommodates undersampling of excitation k-space undersampling and compensates pulses for off-resonance.
+and how well the algorithm accommodates \textcolor{blue}{excitation k-space undersampling}\revbox{R1.X} and compensates pulses for off-resonance.
 An early account of this work was provided in Ref. \cite{grissom:ismrm18}.

### 2020-10-02 Manuscript_r1/Method.tex
wag R1 stuff

--- 2020-09-10 Manuscript/Method.tex
@@
 With this trajectory and the 64$\times$64$\times$48 design grid size, 
-the dimensions of the $\bm{W}$ matrix were 16,632 RF pulse samples, by 196,608 target k-space locations.
+the dimensions of the $\bm{W}$ matrix were 16,632 RF pulse samples, 
+by 196,608 target k-space locations.
 
@@
 as a function that takes as input the $B_1^+$ maps, 
-a normalized excitation k-space trajectory, and optional structures of algorithm and off-resonance parameters. 
+a normalized excitation k-space trajectory, \textcolor{blue}{and optional MATLAB structures of algorithm parameters such as the Tikhonov regularization parameter
+and inclusion and patch widths, and off-resonance parameters such as the off-resonance field map, the time vector and the number of time segments.}\revbox{R1.X} 
 Within that function the Fourier transforms of the $B_1^+$ products are calculated,
-and a C-based MEX function is invoked to solve for the non-zero elements of each column of $\bm{W}$,
+and a C-based \textcolor{blue}{MATLAB Executable (MEX)}\revbox{R1.X} function is invoked to solve for the non-zero elements of each column of $\bm{W}$,
 with linear interpolation of the Fourier transforms of the $B_1^+$ map products to obtain the entries of the $\bm{S}^H\bm{S}$ matrices. 
 Those elements are then inserted into a sparse $\bm{W}$ matrix, which is the single output of the main function. 
-Parallelization was implemented across patches within the C-based MEX function using OpenMP. 
+Parallelization was implemented across patches within the C-based MEX function using the \textcolor{blue}{Open Multi-Processing (OpenMP)}\revbox{R1.X} library. 
 The final pulses are calculated by multiplying the sparse $\bm{W}$ matrix into the Fourier transform of the target pattern. 

### 2020-10-02 Manuscript_r1/Result.tex
wag R1 stuff

--- 2020-09-10 Manuscript/Result.tex
@@
 excitation error and RMS RF amplitude.
-The dots on the spatial domain and k-space domain curves indicate the knees of of the curves corresponding to
+The dots on the spatial domain and k-space domain curves indicate the knees \textcolor{blue}{of}\revbox{R1.X} the curves corresponding to
 the $\lambda$ values used for the designs in Figures \ref{fig:ErrorMap}, \ref{fig:ComputationTime}, \ref{fig:kspace_PTX_Acceleration}, and \ref{fig:kspace_PTX_B0}.

### 2020-10-02 Manuscript_r1/kPtx_paper.tex
wag R1 stuff

@@
 {\bf Purpose:}
-To accelerate the design of multidimensional parallel transmission pulses. 
+To accelerate the design of \textcolor{blue}{(under- or oversampled)}\revbox{R1.X} multidimensional parallel transmission pulses. 
 \\[1em]
@@
 
+\bibitem{setsompop2009}
+K.~Setsompop, V.~Alagappan, B.~A. Gagoski, A.~Potthast, F.~Hebrank, U.~Fontius,
+  F.~Schmitt, L.~L. Wald, and E.~Adalsteinsson.
+\newblock Broadband slab selection with $b_1^+$ mitigation at 7{T} via parallel
+  spectral-spatial excitation.
+\newblock Magn Reson Med 2009; 61:493--500.
+
+\bibitem{Malik:2010aa}
+S.~J. Malik, D.~J. Larkman, D.~P. O'Regan, and J.~V. Hajnal.
+\newblock Subject-specific water-selective imaging using parallel transmission.
+\newblock Magn Reson Med 2010; 63(4):988--997.
+
+\bibitem{stenger2000three}
+Stenger VA, Boada FE, Noll DC.
+\newblock Three-dimensional tailored {RF} pulses for the reduction of
+  susceptibility artifacts in {$T_2^*$}-weighted functional {MRI}.
+\newblock Magn Reson Med 2000;\hspace{0pt}44:525--531.
+
+\bibitem{yang2010four}
+Yang C, Deng W, Alagappan V, Wald LL, Stenger VA.
+\newblock Four-dimensional spectral-spatial {RF} pulses for simultaneous
+  correction of {B1+} inhomogeneity and susceptibility artifacts in
+  {T2*}-weighted {MRI}.
+\newblock Magn Reson Med 2010;\hspace{0pt}64:1--8.
+
 \bibitem{orzada:2019}
@@
 \newblock IEEE Trans Sig Proc 2003;\hspace{0pt}51:560--574.
-
-\bibitem{stenger2000three}
-Stenger VA, Boada FE, Noll DC.
-\newblock Three-dimensional tailored {RF} pulses for the reduction of
-  susceptibility artifacts in {$T_2^*$}-weighted functional {MRI}.
-\newblock Magn Reson Med 2000;\hspace{0pt}44:525--531.
-
-\bibitem{yang2010four}
-Yang C, Deng W, Alagappan V, Wald LL, Stenger VA.
-\newblock Four-dimensional spectral-spatial {RF} pulses for simultaneous
-  correction of {B1+} inhomogeneity and susceptibility artifacts in
-  {T2*}-weighted {MRI}.
-\newblock Magn Reson Med 2010;\hspace{0pt}64:1--8.
 

### 2020-10-03 Manuscript_r1/Conclusion.tex
wag working more on R1

@@
 Furthermore, unlike an iterative spatial domain design the proposed algorithm does not need to be repeated if the target pattern changes.
-This means that it could have a considerable computational speed advantage for magnitude least-squares designs \cite{setsompop2008magnitude,malik:mrm:2015}. 
-The method could also be used to initialize spatial-domain designs to reduce the number of iterations required to reach a target cost; 
+\textcolor{blue}{This means that while the k-space design method requires the user to specify a complex-valued (not just magnitude) target pattern,
+it could have a considerable computational speed advantage for Gerchberg-Saxton magnitude least-squares designs \cite{setsompop2008magnitude,malik:mrm:2015}
+which alternate between designing pulses and updating a complex-valued target pattern. }\revbox{R1.X}
+The method could also be used to initialize spatial-domain designs to reduce the number of iterations required to reach a target cost. 
 Finally, while simple Tikhonov RF power regularization was used in the designs presented here,
-more sophisticated regularization could be incorporated to, e.g., control peak RF power via adaptive regularization \cite{Yip:2005:Magn-Reson-Med:16155881},
-or to enforce array compression by projecting the weights into the null space of a compression matrix \cite{cao2016array}.
+more sophisticated regularization could be incorporated to, 
+e.g., control peak RF power via adaptive regularization \cite{Yip:2005:Magn-Reson-Med:16155881},
+or to enforce array compression by projecting the weights into the null space of a compression matrix \cite{cao2016array},
+\textcolor{blue}{among other applications \cite{padormo:2016,deniz:2019}.} \revbox{R1.X}
 In such designs, it would be beneficial to pre-compute and store the lower triangular elements of the $\bm{S}^H\bm{S}$ matrices

### 2020-10-03 Manuscript_r1/Introduction.tex
wag working more on R1

@@
 The algorithm produces a sparse k-space-domain pseudoinverse pulse design matrix 
-that directly relates the Fourier transform of the target excitation pattern to the RF pulses that produce it.
+that directly relates the Fourier transform \textcolor{blue}{of a complex-valued}\revbox{R1.X} target excitation pattern to the RF pulses that produce it.
 Once the matrix is built, 

### 2020-10-03 Manuscript_r1/Method.tex
wag working more on R1

@@
 Ansys High Frequency Structure Simulator (Canonsburg, PA, USA) with 1.5 mm isotropic resolution. 
-Figure \ref{fig:Target}a shows the target pattern for all pulse designs which comprised an ellipse centered on the ventricles with AP/HF/LR semi-axes of 4.8/3.2/3.2 cm.
+Figure \ref{fig:Target}a shows the target pattern for all pulse designs which comprised an ellipse centered on the ventricles with AP/HF/LR semi-axes of 4.8/3.2/3.2 cm,
+\textcolor{blue}{with zero phase.}\revbox{R1.X} 
 The pattern was smoothed by a Fermi filter that was applied in the frequency domain to match the target pattern's effective resolution to the excitation k-space trajectory's 5 mm resolution.

### 2020-10-03 Manuscript_r1/Result.tex
wag working more on R1

@@
 As inclusion width increases, more excitation trajectory points are used in the solution of the weights for each target location,
-until the entire trajectory is used for each location (Inclusion width = $\infty$ in the table),
+until the entire trajectory is used for each location (inclusion width = $\infty$ in the table),
 corresponding to a full solution. 

### 2020-10-03 Manuscript_r1/Theory.tex
wag working more on R1

@@
 and $\mathcal{F}(\bm{d})$ is a length-$N_s$ vector containing the 
-Fourier transform of the desired k-space excitation pattern $\bm{d}$.
+Fourier transform of the \textcolor{blue}{complex-valued}\revbox{R1.X} target k-space excitation pattern $\bm{d}$.
 $\bm{W}$ has dimensions $N_t  N_c \times N_s$.

### 2020-10-03 Manuscript_r1/kPtx_paper.tex
wag working more on R1

@@
 A k-space domain parallel transmission pulse design algorithm was proposed that
-produces a sparse matrix relating a target excitation pattern to the pulses that produce it,
+produces a sparse matrix relating a \textcolor{blue}{complex-valued}\revbox{R1.X} target excitation pattern to the pulses that produce it, 
 and can be finely parallelized. 
@@
 
+\bibitem{padormo:2016}
+F.~Padormo, A.~Beqiri, J.~V. Hajnal, and S.~J. Malik.
+\newblock Parallel transmission for ultrahigh-field imaging.
+\newblock {NMR} Biomed 2016; 29(9):1145--1161.
+
+\bibitem{deniz:2019}
+C.~M. Deniz.
+\newblock Parallel transmission for ultrahigh field {MRI}.
+\newblock Top Magn Reson Imaging 2019; 28(3):159--171.
+
 \bibitem{Lee:2011:MRM}
@@
 \pagebreak
+
+\section*{Table Captions}
+
+\begin{table}[!h]
+\centering
+%\begin{tabular}{c | c}
+%Inclusion Width & $\bm{W}$ Matrix Size (GB) \\
+%\hline
+%$\infty$ & 24.4 \\
+%8 & 2.73 \\
+%6 & 1.37 \\
+%4 & 0.53 \\
+%2 & 0.14
+%\end{tabular}
+\caption{$\bm{W}$ matrix sizes in gigabytes (GB) versus inclusion width in cycles/FOV. 
+An inclusion width of $\infty$ corresponds to a full matrix solution.}
+\label{fig:wsize}
+\end{table}
+
+\pagebreak
 %(Please see main document for caption with intended math typesetting)
 
-\begin{figure}
+\section*{Figure Captions}
+
+\begin{figure}[!h]
 	\centering
@@
 
-\begin{figure}
+\begin{figure}[!h]
 	\centering
@@
 
-\begin{figure}
-\centering
-%\begin{tabular}{c | c}
-%Inclusion Width & $\bm{W}$ Matrix Size (GB) \\
-%\hline
-%$\infty$ & 24.4 \\
-%8 & 2.73 \\
-%6 & 1.37 \\
-%4 & 0.53 \\
-%2 & 0.14
-%\end{tabular}
-\caption{$\bm{W}$ matrix sizes in gigabytes (GB) versus inclusion width in cycles/FOV. 
-An inclusion width of $\infty$ corresponds to a full matrix solution.}
-\label{fig:wsize}
-\end{figure}
-
-\begin{figure}
+\begin{figure}[!h]
 	\centering

### 2020-10-03 Manuscript_r1/Conclusion.tex
wag finished with R1

@@
 and the methods were similarly sensitive to excitation k-space undersampling. 
+\textcolor{blue}{While all the pulse designs in this work used 3D SPINS trajectories,
+the method can be applied in any number of dimensions and with any excitation k-space trajectory.
+The MATLAB implementation described can be used for any two- or three-dimensional pulse design without modification.}\revbox{R1.X}
 
@@
 and an iterative design can require several minutes to solve. 
-Furthermore, unlike an iterative spatial domain design the proposed algorithm does not need to be repeated if the target pattern changes.
-\textcolor{blue}{This means that while the k-space design method requires the user to specify a complex-valued (not just magnitude) target pattern,
-it could have a considerable computational speed advantage for Gerchberg-Saxton magnitude least-squares designs \cite{setsompop2008magnitude,malik:mrm:2015}
-which alternate between designing pulses and updating a complex-valued target pattern. }\revbox{R1.X}
+\textcolor{blue}{Furthermore, unlike an iterative spatial domain design the proposed algorithm does not need to be repeated if the target pattern changes.
+This means it could have a considerable computational speed advantage for Gerchberg-Saxton magnitude least-squares pulse designs \cite{setsompop2008magnitude,malik:mrm:2015}
+which alternate between designing pulses and updating a complex-valued target pattern.
+Such a design method would allow the user to specify only the magnitude of the target pattern, 
+rather than magnitude and phase as was required in this work.}\revbox{R1.X}
 The method could also be used to initialize spatial-domain designs to reduce the number of iterations required to reach a target cost. 
@@
 \textcolor{blue}{It may also be possible to use the k-space domain method to rapidly design large-tip-angle pulses via the direct linear class of large-tip-angle pulses method \cite{Xu:2008aa} or the additive angle method \cite{grissom:mrm:2008};
-the latter alternates between small-tip-angle designs that could be solved by the k-space method and Bloch simulations to update the target pattern.} \revbox{R2.X}
+the latter alternates between small-tip-angle designs that could be solved by the k-space method, 
+and Bloch simulations to update the target pattern.} \revbox{R2.X}
 

### 2020-10-05 Manuscript_r1/Conclusion.tex
wag did some R2 work

@@
 which has not previously been described in a k-space domain design. 
-Compared to widely-used spatial domain method of Ref. \cite{Grissom:2006:MRM},
+Compared to a spatial domain design,
 the new algorithm is non-iterative and can be finely parallelized to achieve shorter design times, 
@@
 It is anticipated that the proposed k-space domain algorithm will be most useful for these types of large $>$2D problems,
-which include 3D spatial designs \cite{malik2012tailored,davids2016fast} and \textcolor{blue}{2D and 3D spatial-spectral designs \cite{stenger2000three,setsompop2009,Malik:2010aa,yang2010four}
+which include 3D spatial designs \cite{malik2012tailored,davids2016fast} 
+and \textcolor{blue}{2D and 3D spatial-spectral designs \cite{stenger2000three,setsompop2009,Malik:2010aa,yang2010four}
 where full matrix construction and inversion is infeasible due to the problem size, }\revbox{R1.X}
@@
 so they need not be re-computed as the regularization changes over iterations.  
-\textcolor{blue}{Peak power could also be controlled in k-space domain designs using pTx VERSE \cite{Lee:2011:MRM} or the iterative re-VERSEit technique \cite{lee2009tod}.} \revbox{R2.X}
+\textcolor{blue}{Peak power could also be controlled in k-space domain designs using parallel transmission 
+VERSE \cite{Lee:2011:MRM} or the iterative re-VERSEit technique \cite{lee2009tod}.} \revbox{R2.X}
+\textcolor{blue}{It is not yet clear whether or how hard constraints on SAR and 
+peak- and integrated-power could be directly incorporated in the k-space method, as in Refs \cite{brunner2010optimal} and \cite{hoyos:tmi:2014}. }\revbox{R2.X}
 \textcolor{blue}{It may also be possible to use the k-space domain method to rapidly design large-tip-angle pulses via the direct linear class of large-tip-angle pulses method \cite{Xu:2008aa} or the additive angle method \cite{grissom:mrm:2008};

### 2020-10-05 Manuscript_r1/Introduction.tex
wag did some R2 work

@@
 and the use of non-uniform fast Fourier transforms to accelerate matrix multiplies.
-Since its introduction, nearly all parallel transmission studies have used the spatial domain method.
+Since its introduction, 
+\textcolor{blue}{nearly all small-tip-angle parallel transmission studies have been formulated in the spatial domain \cite{padormo:2016,deniz:2019}.} \revbox{R2.X}
 
-\par Despite the spatial domain method's strengths, 
+\par Despite the advantages of the spatial domain approach, 
 it can have prohibitive computational requirements when the number of coils and the number of dimensions become large, 
@@
 $N_c$ is the number of transmit channels, and $N_t$ is the number of time points in the pulse.
-Typically values for $N_s$ range from 1,000 for 2D designs to 250,000 for 3D designs,
+\textcolor{blue}{Typical values for $N_s$ range from 1,000 for 2D designs to 250,000 for 3D designs,
 the number of coils varies from 8 to 32 on ultra-high field scanners,
-and the number of time points is typically between 1,000 and 10,000. 
-Overall, for a 3D design the spatial domain system matrix can occupy up to 150 gigabytes of memory,
-making it infeasible to construct and invert on most modern computers.
+and the number of time points varies from 500 to 2,500. 
+Overall, for a 3D design the spatial domain system matrix can occupy upwards of 120 gigabytes of memory,
+making it infeasible to construct and invert on most modern computers. } \revbox{R2.X}
 Explicit matrix storage and inversion can be avoided using non-uniform fast Fourier transforms to evaluate matrix multiplies,

### 2020-10-05 Manuscript_r1/Method.tex
wag did some R2 work

@@
 Simulations were performed to validate and characterize the proposed k-space domain parallel transmit pulse design method,
-with comparisons to the spatial-domain method of Ref. \cite{Grissom:2006:MRM}.
+with comparisons to a least-squares spatial-domain design \cite{Grissom:2006:MRM}.
 RF pulses were designed for a simulated 24-channel loop transmit array (Figure \ref{fig:Coil}) that is being built for a 7 Tesla scanner optimized
@@
 For spatial domain designs, 
-RF pulses were solved using an iterative least-squares conjugate-gradient descent method \cite{Grissom:2006:MRM} with 35 iterations,
+RF pulses were solved using an iterative least-squares conjugate-gradient descent method with 35 iterations,
 which was accelerated by non-uniform fast Fourier transforms \cite{Fessler:2003fk}. 
@@
 the number of polar and azimuthal rotations were increased and reduced relative to the reference design described above, 
-for reduction factors of 0.5, 2, 3, and 4.
+for reduction factors of 0.5, 2, 3, and 4, 
+\textcolor{blue}{where the factor 0.5 trajectory comprised X additional segments for approximately 2$\times$-denser sampling of excitation k-space.} \revbox{2.X}
 

### 2020-10-05 Manuscript_r1/Theory.tex
wag did some R2 work

@@
 In this work `inclusion width' is defined as the distance, 
-in cycles per excitation field-of-view (cycles/FOV), 
+in \textcolor{blue}{phase cycles per excitation field-of-view (cycles/FOV), }\revbox{R1.X} 
 from each target location $\vec{k}_j$ within which which all trajectory points are accrued into $\mathbb{N}$.

### 2020-10-05 Manuscript_r1/response_to_reviews.tex
response to reviews

@@
 \mysubsectionstar{Referee 1}
-{\bf R1.1:} P2L26. Please replace ``three'' with ``four''.
+{\bf R1.1:} Please clarify from the beginning that your method is designed for a complex target pattern, i.e., specifying magnitude and phase and not only magnitude as in e.g.
+[13].
+As you are certainly aware, this feature has severe consequences for the method.
+Thus also the phase pattern in the simulation setup has to be specified (page 10, I assume phase demand is simply constant).
+Some sentences in the discussion how you would extend your method to magnitude-only patterns would also be appreciated.
 \\[0.2em] 
@@
 \\[1.2em]
-{\bf R1.2:} P14L37. Please remove ``B1+ SVT''
+
+{\bf R1.2:} It is not directly clear how far your method is specific for the chosen SPINS trajectory (e.g.
+by defining the inclusion width as cycles/FOV).
+Please discuss how far your method is applicable to arbitrary trajectories, or how the method needs to be adapted if other trajectories are used.
+\\[0.2em]
+\indent{\it \textcolor{blue}{Done.}}
+\\[1.2em]
+
+{\bf R1.3:} Description of off-resonance compensation seems to be slightly less diligent as rest of theory.
+(a) Equation 7 contains $g_l$ (one index) but you define $g_{il}$ (two indices), then $g_l$ is used again in Eq 8 and $g_{il}$ in Eq 9, (b) the definition of $g_l$ is based on $b_l$ but I do not find definition of $b_l$, (c) shortly after you introduce $h_{lj}$, but $h_{lj}$ seems to be never used.
 \\[0.2em]
@@
 
+{\bf R1.4:} It is not directly clear how far your method is specific for the chosen SPINS trajectory (e.g.
+by defining the inclusion width as cycles/FOV).
+Please discuss how far your method is applicable to arbitrary trajectories, or how the method needs to be adapted if other trajectories are used.
+\\[0.2em]
+\indent{\it \textcolor{blue}{Done.}}
+\\[1.2em]
+
+{\bf R1.5:} Abstract, purpose: To underline that this paper is about acceleration of design of RF pulses and not about acceleration of RF pulses itself (which might be intuitively expected by some readers) I suggest to add a bracket like this: „To accelerate the design of (under- or oversampled) multidimensional parallel transmission pulses“
+\\[0.2em]
+\indent{\it \textcolor{blue}{Done.}}
+\\[1.2em]
+
+{\bf R1.6:} page 11, row 32: „optional structures of algorithm and off-resonance parameters“: please be more specific or skip this remark
+\\[0.2em]
+\indent{\it \textcolor{blue}{Done.}}
+\\[1.2em]
+
+{\bf R1.7:} page 11, „MEX“ and „OpenMP“: the editor might decide if these terms need some explanation, or can be taken as known
+\\[0.2em]
+\indent{\it \textcolor{blue}{Done.}}
+\\[1.2em]
+
+{\bf R1.8:} page 19, rows 25-30: there are numerous studies on various types of power regularization for parallel transmission (e.g.
+Hamburg/Graesslin, London/Malik, Zurich/Brunner, Paris/Boulant).
+You might reference some of these, or reference at least a review paper on this topic like Padormo F NBM 2016, Deniz CM TMRI 2020 etc.
+\\[0.2em]
+\indent{\it \textcolor{blue}{Done.}}
+\\[1.2em]
+
+{\bf R1.9:} More privately, I am curious which text editor you use, which obviously removed all typos (I did not find a single typo) but does not seem to be able to show doublings:
+- page 6, row 48: double "row"
+- page 16, row 30: double "of"
+- page 5, row 12: double "undersampling"
+\\[0.2em]
+\indent{\it \textcolor{blue}{Done.}}
+\\[1.2em]
+
 \mysubsectionstar{Referee 2}
-{\bf R2.1:} Upon rereading the manuscript, however, I did realize one potential pitfall of the proposed matrix implementation shown in Fig.
-1.
-Using a simple concatenation of power splitters, attenuators and phase shifters will significantly (possibly dramatically) reduce the efficiency of the virtual coil.
-This means that although fewer parallel transmit pathways could be used, the driving amplifiers need to be significantly more powerful (more then N times, where N is the coil compression factor) to compensate for the power dissipated in the attenuation stage of the matrix.
-On top of that, there will be losses in the various matrix components and connections.
-Although a bigger amplifier would probably still be more cost efficient than duplicating the entire RF-chain, most current 7T systems are equipped with only relatively small simplifiers (Typically 8kW in total).
-For some applications, especially in body imaging, the full 8kW is already considered a limiting factor.
-\par In my opinion it is not critical, but I think it may be worthwhile to highlight this particular aspect in the discussion.
-I would like to leave it to the authors discretion if they would like to incorporate this final observation.
+{\bf R2.1:} The weakest point of the manuscript in my opinion is that the single test case (target region-wise) and the underlying 10 ms trajectory (the longest (?), non-accelerated one) is rather benign for the claimed problem they are seeking to solve.
+
+For example they claim 3D pTx pulse design may use from 1,000 to 10,000 time points (per channel), for 8 to 32 channels, and up to 250,000 spatial points.
+These values, they claim need a lot of memory.
+
+They have a dwell time of 15 µs and thus 666 time samples per channel.
+They study a setup with 24 channels.
+They consider 196,000 spatial points.
+
+Channel-wise it is fair they consider 24 channels that match their array, but otherwise all three circumstances they investigate are lower than the initial problem they claim exist.
+
+They do produce a rather good compression of the design problem by the new method.
+I wonder why they don't stress test it better, going towards the troublesome criteria and beyond.
+What results would they obtain if they reached the claimed limits?
+How far can they go?
 \\[0.2em]
-\indent{\it \textcolor{blue}{We agree that due to losses in the coil compression network, more RF
-power will be required to create a given RF field strength compared to a full set of RF power amplifiers
-driving the same coil array. At this early stage it is rather unclear just what those losses will be,
-but we have added a statement to the Discussion that there will be some power loss so the total RF power requirements will
-be increased.}}
+\indent{\it \textcolor{blue}{Done.}}
+\\[1.2em]
+
+{\bf R2.2:} Their stress tests demonstrate finely the methods application towards the off-resonance handling, pulse acceleration, RF power regularization and RMSE of excitation patterns etc.
+
+For a completely numerical paper however, I believe the stress testing should target not only what they have done, but also going to the extreme -- if they claim it is a problem they can solve....
+Otherwise they should reduce their claim and state they can fix the problem partly by this proposed method.
+
+For example, how does the proposed method handle the problem at the point, where the spatial domain method becomes infeasible.
+
+I'm sure lots of pulse design will use the algorithm for other target regions (more detailed ones requiring higher resolution).
+
+I couldn't quite find out what the 0.5-undersampling reduction factor meant in terms of pulse duration.
+If it translates to 666*2 time samples then again we are not near the 10,000 samples still.
+But maybe this should be described in more detail...
+\\[0.2em]
+\indent{\it \textcolor{blue}{Done.}}
+\\[1.2em]
+
+{\bf R2.3:} It is somewhat weakening that they only compare their method to another one of their methods, since a lot has been done since 2006.
+
+p3 l 32: "...nearly all parallel transmission studies have used the spatial domain method":
+
+For sure a lot of pTx designs use the spatial domain method of Grissom.
+
+But stating "nearly all" is somewhat a guess and should be backed up by numbers. What do you mean by nearly all? It must be quite provoking for those who use another one to be diminished.
+
+We can agree that most pTx design function in the spatial domain, but to state that they are also based on the method of Grissom should be backed up.
+\\[0.2em]
+\indent{\it \textcolor{blue}{Done.}}
+\\[1.2em]
+
+{\bf R2.4:} As discussed below, another reason to include mentions of even more pulse designs is that they tackle problems the proposed method does not.
+Similar to Hoyos-Idrobos [15] and Brunners [14] please discuss how the proposed method will handle if at all possible hard constraints.
+Is it possible?
+
+I can only imagine that local SAR constraints will be quite comfortable to have with 24 channels.
+It is good that achieving the target profile is now faster with the proposed method, but how will the k-space domain method( and the spatial domain method for matter), handle local SAR?
+If you have 24 amplifiers tied together, are you all set to just rely on pulse (adaptive) regularisation or would you really desire to have hard peak and even average power constraints?
+
+One can accept to only witness a comparison to the 2006 method, if the limitations of that and the proposed method are clearly labelled.
+
+Yes, other methods might be much slower, but they handle problems you don't.
+\\[0.2em]
+\indent{\it \textcolor{blue}{Done.}}
+\\[1.2em]
+
+{\bf R2.5:}As a new pulse design method, I think the introduction should include a much broader review of other pulse designs existing already.
+Otherwise it paints a false picture of what has happened in the period where Grissom introduced the method they are comparing to.
+
+It is also an overall narrow scope they used for review. The latest pulse design method papers referenced are from 2016, and their own ISMRM abstract from 2018.
+
+New pulse design methods have appeared in more recent years.
+Within, all the years from 2006 to now, there are several pulse designs demonstrated for other applications than 3D pTx, but have features that translate readily to a 3D application.
+The Grissom-2006 method did not include a 3D pTx application.
+Hence, the sought-for referencing can also include pulse design with other applications and with design features that solves problems that the proposed method does not solve, even if it was not for 3D pTx.
+\\[0.2em]
+\indent{\it \textcolor{blue}{Done.}}
+\\[1.2em]
 

### 2020-10-05 code/demo_kpTx_SPINS.m
Fix figures

@@ -14,7 +14,7 @@ if_kpsce_MLS = false;
 
 ifOffRes = false;
 
-ifOpenMP = true; % IN OpemMP, number of thread has to be change in the .c file and then re-compile
+ifOpenMP = false; % IN OpemMP, number of thread has to be change in the .c file and then re-compile
 
 ifDoSpatialDesign = true;
 
@@ -189,6 +189,7 @@ toc
 
 
 %%
+if if_kpsce_MLS
 b1 = permute(sens,[4 1 2 3]);b1 = b1(:,:).';
 
 J = [6 6 6]; % # of neighnors used
@@ -210,7 +211,7 @@ end
 m = zeros(dimb1);m(mask) = A*rf(:);
 err = norm(col(mask.*(abs(m)-abs(d))))/norm(col(d.*mask))
 
-if if_kpsce_MLS
+
     m2=m;
     for ii=1:3
         pDes2=fftshift(fftn(fftshift(abs(d).*exp(1i*angle(m2)))));
@@ -225,88 +226,6 @@ end
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % Display final results
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-mask_ring=mask;
-%err = norm(col(mask_ring.*(abs(m)-abs(d))))/norm(col(d.*mask_ring))
-
-d_plot=d.*mask_ring;
-m_plot=m.*mask_ring;
-
-if genfigs
-    maxamp = max(abs([d_plot(:);m_plot(:)]));
-    figure
-    subplot(221)
-    im(abs(d_plot),[0 maxamp]);axis image;colorbar
-    title 'Desired pattern'
-    subplot(222)
-    im(abs(m),[0 maxamp]);axis image;colorbar
-    caxis([0 1.1])
-    title(sprintf('Final pattern',Nc));
-    subplot(223)
-    im(permute(abs(abs(m_plot)-abs(d_plot)),[1 3 2]));axis image;colorbar
-    caxis([0 0.1])
-    subplot(221)
-    im(permute(abs(abs(m_plot)-abs(d_plot)),[2 3 1]));axis image;colorbar
-    caxis([0 0.1])
-    subplot(224)
[…]

### 2020-10-05 Manuscript_r1/response_to_reviews.tex
further r1 edits

@@
 Below we have numbered each specific critique and provide our responses.
+For each addition we have made, we have trimmed out other text, and now stand at a word count of \textcolor{red}{X words.} 
+\textcolor{red}{In addition, we have removed the $R = 3$ result from Figure 9 (now Figure 8), to improve readability. 
+We kept the powers-of-two reduction factors.}
 
@@
 \\[0.2em] 
-\indent{\it \textcolor{blue}{Done.}}
+\indent{\it \textcolor{blue}{We have added statements throughout the manuscript to clarify that the target pattern is complex-valued,
+and that the target phase we used in our simulated designs was zero.
+We also added discussion that to achieve a magnitude-least-squares design with the k-space method, 
+it could be used in a Gerchberg-Saxton-like magnitude-least-squares algorithm,
+where it would have the advantage (compared to an iterative spatial domain design) that the matrix $\bm{W}$ 
+would not need to be recomputed as the target pattern changes over iterations.}}
 \\[1.2em]
 
-{\bf R1.2:} It is not directly clear how far your method is specific for the chosen SPINS trajectory (e.g.
+\noindent{\bf R1.2:} It is not directly clear how far your method is specific for the chosen SPINS trajectory (e.g.
 by defining the inclusion width as cycles/FOV).
@@
 \\[0.2em]
-\indent{\it \textcolor{blue}{Done.}}
+\indent{\it \textcolor{blue}{The algorithm makes no assumptions about the specific trajectory used, 
+and we have clarified this in the Discussion.
+The code we provide should work for any 2D or 3D trajectory, and could be extended to any number of dimensions. 
+We have also clarified in the Theory section that by `cycles/FOV' we mean phase cycles over the excitation FOV;
+this is a general measure that is not specific to the SPINS trajectory.}}
 \\[1.2em]
 
-{\bf R1.3:} Description of off-resonance compensation seems to be slightly less diligent as rest of theory.
+\noindent{\bf R1.3:} Description of off-resonance compensation seems to be slightly less diligent as rest of theory.
 (a) Equation 7 contains $g_l$ (one index) but you define $g_{il}$ (two indices), then $g_l$ is used again in Eq 8 and $g_{il}$ in Eq 9, (b) the definition of $g_l$ is based on $b_l$ but I do not find definition of $b_l$, (c) shortly after you introduce $h_{lj}$, but $h_{lj}$ seems to be never used.
 \\[0.2em]
-\indent{\it \textcolor{blue}{Done.}}
-
-{\bf R1.4:} It is not directly clear how far your method is specific for the chosen SPINS trajectory (e.g.
-by defining the inclusion width as cycles/FOV).
-Please discuss how far your method is applicable to arbitrary trajectories, or how the method needs to be adapted if other trajectories are used.
-\\[0.2em]
-\indent{\it \textcolor{blue}{Done.}}
+\indent{\it \textcolor{blue}{Thank you for noticing the inconsistencies in this section; we agree and have revised the section to simplify and clarify it.}}
 \\[1.2em]
 
-{\bf R1.5:} Abstract, purpose: To underline that this paper is about acceleration of design of RF pulses and not about acceleration of RF pulses itself (which might be intuitively expected by some readers) I suggest to add a bracket like this: „To accelerate the design of (under- or oversampled) multidimensional parallel transmission pulses“
+\noindent{\bf R1.4:} Abstract, purpose: To underline that this paper is about acceleration of design of RF pulses and not about acceleration of RF pulses itself (which might be intuitively expected by some readers) I suggest to add a bracket like this: „To accelerate the design of (under- or oversampled) multidimensional parallel transmission pulses“
 \\[0.2em]
-\indent{\it \textcolor{blue}{Done.}}
+\indent{\it \textcolor{blue}{We agree and have made this addition.}}
 \\[1.2em]
 
-{\bf R1.6:} page 11, row 32: „optional structures of algorithm and off-resonance parameters“: please be more specific or skip this remark
+\noindent{\bf R1.5:} page 11, row 32: „optional structures of algorithm and off-resonance parameters“: please be more specific or skip this remark
 \\[0.2em]
-\indent{\it \textcolor{blue}{Done.}}
+\indent{\it \textcolor{blue}{We have skipped this remark to save word count.}}
 \\[1.2em]
 
-{\bf R1.7:} page 11, „MEX“ and „OpenMP“: the editor might decide if these terms need some explanation, or can be taken as known
+\noindent{\bf R1.6:} page 11, „MEX“ and „OpenMP“: the editor might decide if these terms need some explanation, or can be taken as known
 \\[0.2em]
-\indent{\it \textcolor{blue}{Done.}}
+\indent{\it \textcolor{blue}{We have defined each of these acronyms.}}
 \\[1.2em]
 
-{\bf R1.8:} page 19, rows 25-30: there are numerous studies on various types of power regularization for parallel transmission (e.g.
+\noindent{\bf R1.7:} page 19, referencing spatial-spectral designs, please add corresponding studies using parallel transmission: Setsompop K MRM 2009 and Malik S MRM 2010
+\\[0.2em]
+\indent{\it \textcolor{blue}{We have added those citations, in both the Conclusion and Introduction.}}
+\\[1.2em]
+
+\noindent{\bf R1.8:} page 19, rows 25-30: there are numerous studies on various types of power regularization for parallel transmission (e.g.
 Hamburg/Graesslin, London/Malik, Zurich/Brunner, Paris/Boulant).
@@
 \\[0.2em]
-\indent{\it \textcolor{blue}{Done.}}
+\indent{\it \textcolor{blue}{We apologize; there were some references we intended to include there but missed in the initial submission.
+In response to this and R2.2 and R2.3, we have added citations to the two review articles you mention, and also explicitly state that it is unclear at this time how and
+whether hard constraints could be built in to the method.}}
 \\[1.2em]
 
-{\bf R1.9:} More privately, I am curious which text editor you use, which obviously removed all typos (I did not find a single typo) but does not seem to be able to show doublings:
+\noindent{\bf R1.9:} More privately, I am curious which text editor you use, which obviously removed all typos (I did not find a single typo) but does not seem to be able to show doublings:
 - page 6, row 48: double "row"
@@
 \\[0.2em]
-\indent{\it \textcolor{blue}{Done.}}
+\indent{\it \textcolor{blue}{We used TexShop on the Mac - thanks for finding the doublings! 
+We found and fixed the ``of'' and ``undersampling'' ones but could not locate the ``row'' one.}}
 \\[1.2em]
@@
 How far can they go?
-\\[0.2em]
-\indent{\it \textcolor{blue}{Done.}}
-\\[1.2em]
 
-{\bf R2.2:} Their stress tests demonstrate finely the methods application towards the off-resonance handling, pulse acceleration, RF power regularization and RMSE of excitation patterns etc.
+Their stress tests demonstrate finely the methods application towards the off-resonance handling, pulse acceleration, RF power regularization and RMSE of excitation patterns etc.
 
@@
 \\[0.2em]
-\indent{\it \textcolor{blue}{Done.}}
+\indent{\it \textcolor{red}{TODO: Clarify how the trajectory changed between the different $R$ factors. 
+We have updated the numbers in the Introduction to slightly more realistic values. 
+We will report the design times across $R$ factors.}}
 \\[1.2em]
 
-{\bf R2.3:} It is somewhat weakening that they only compare their method to another one of their methods, since a lot has been done since 2006.
+\noindent {\bf R2.2:} It is somewhat weakening that they only compare their method to another one of their methods, since a lot has been done since 2006.
 
@@
 We can agree that most pTx design function in the spatial domain, but to state that they are also based on the method of Grissom should be backed up.
-\\[0.2em]
-\indent{\it \textcolor{blue}{Done.}}
-\\[1.2em]
 
-{\bf R2.4:} As discussed below, another reason to include mentions of even more pulse designs is that they tackle problems the proposed method does not.
+As discussed below, another reason to include mentions of even more pulse designs is that they tackle problems the proposed method does not.
 Similar to Hoyos-Idrobos [15] and Brunners [14] please discuss how the proposed method will handle if at all possible hard constraints.
@@
 \\[0.2em]
-\indent{\it \textcolor{blue}{Done.}}
+\indent{\it \textcolor{blue}{We agree that we need to tone down the language here.
+We have revised wording to indicate that nearly all parallel transmission studies have been formulated in the spatial domain, rather than being explicitly derived directly from the spatial domain method.
+We have also added in the Discussion that it is not clear at this time whether or how hard power or SAR constraints could be directly built in to the method,
+though the method would be compatible with parallel transmit VERSE methods.}}
 \\[1.2em]
 
-{\bf R2.5:}As a new pulse design method, I think the introduction should include a much broader review of other pulse designs existing already.
+\noindent {\bf R2.3:} As a new pulse design method, I think the introduction should include a much broader review of other pulse designs existing already.
 Otherwise it paints a false picture of what has happened in the period where Grissom introduced the method they are comparing to.
@@
 \\[0.2em]
-\indent{\it \textcolor{blue}{Done.}}
+\indent{\it \textcolor{blue}{While we are above our word count and cannot add a broad overview of different parallel transmit pulse design methods
+to the Introduction,
+we have added 10 more citations to the work including two review articles on parallel transmission (Deniz 2019 and Padormo 2015).
+We also added brief Discussion on possible extensions of the method for large-tip-angle and VERSE parallel transmit pulse designs.}}
 \\[1.2em]

### 2020-10-05 Manuscript_r1/Conclusion.tex
further r1 edits

@@
 the method can be applied in any number of dimensions and with any excitation k-space trajectory.
-The MATLAB implementation described can be used for any two- or three-dimensional pulse design without modification.}\revbox{R1.X}
+The MATLAB implementation described can be used for any two- or three-dimensional pulse design without modification.}\revbox{R1.2}
 
@@
 and \textcolor{blue}{2D and 3D spatial-spectral designs \cite{stenger2000three,setsompop2009,Malik:2010aa,yang2010four}
-where full matrix construction and inversion is infeasible due to the problem size, }\revbox{R1.X}
+where full matrix construction and inversion is infeasible due to the problem size, }\revbox{R1.7}
 and an iterative design can require several minutes to solve. 
@@
 Such a design method would allow the user to specify only the magnitude of the target pattern, 
-rather than magnitude and phase as was required in this work.}\revbox{R1.X}
+rather than magnitude and phase as was required in this work.}\revbox{R1.1}
 The method could also be used to initialize spatial-domain designs to reduce the number of iterations required to reach a target cost. 
@@
 or to enforce array compression by projecting the weights into the null space of a compression matrix \cite{cao2016array},
-\textcolor{blue}{among other applications \cite{padormo:2016,deniz:2019}.} \revbox{R1.X}
+\textcolor{blue}{among other applications \cite{padormo:2016,deniz:2019}.} \revbox{R1.8}
 In such designs, it would be beneficial to pre-compute and store the lower triangular elements of the $\bm{S}^H\bm{S}$ matrices
@@
 \textcolor{blue}{Peak power could also be controlled in k-space domain designs using parallel transmission 
-VERSE \cite{Lee:2011:MRM} or the iterative re-VERSEit technique \cite{lee2009tod}.} \revbox{R2.X}
+VERSE \cite{Lee:2011:MRM} or the iterative re-VERSEit technique \cite{lee2009tod}.} \revbox{R1.8, R2.2}
 \textcolor{blue}{It is not yet clear whether or how hard constraints on SAR and 
-peak- and integrated-power could be directly incorporated in the k-space method, as in Refs \cite{brunner2010optimal} and \cite{hoyos:tmi:2014}. }\revbox{R2.X}
+peak- and integrated-power could be directly incorporated in the k-space method, as in Refs \cite{brunner2010optimal} and \cite{hoyos:tmi:2014}. }\revbox{R1.8, R2.2}
 \textcolor{blue}{It may also be possible to use the k-space domain method to rapidly design large-tip-angle pulses via the direct linear class of large-tip-angle pulses method \cite{Xu:2008aa} or the additive angle method \cite{grissom:mrm:2008};
 the latter alternates between small-tip-angle designs that could be solved by the k-space method, 
-and Bloch simulations to update the target pattern.} \revbox{R2.X}
+and Bloch simulations to update the target pattern.} \revbox{R2.3}
 

### 2020-10-05 Manuscript_r1/Introduction.tex
further r1 edits

@@
 Since its introduction, 
-\textcolor{blue}{nearly all small-tip-angle parallel transmission studies have been formulated in the spatial domain \cite{padormo:2016,deniz:2019}.} \revbox{R2.X}
+\textcolor{blue}{nearly all small-tip-angle parallel transmission studies have been formulated in the spatial domain \cite{padormo:2016,deniz:2019}.} \revbox{R2.2}
 
@@
 The algorithm produces a sparse k-space-domain pseudoinverse pulse design matrix 
-that directly relates the Fourier transform \textcolor{blue}{of a complex-valued}\revbox{R1.X} target excitation pattern to the RF pulses that produce it.
+that directly relates the Fourier transform \textcolor{blue}{of a complex-valued}\revbox{R1.1} target excitation pattern to the RF pulses that produce it.
 Once the matrix is built, 
@@
 The results show how computation time and accuracy depend on the parameters of the patch-wise parallelization,
-and how well the algorithm accommodates \textcolor{blue}{excitation k-space undersampling}\revbox{R1.X} and compensates pulses for off-resonance.
+and how well the algorithm accommodates \textcolor{blue}{excitation k-space undersampling}\revbox{R1.9} and compensates pulses for off-resonance.
 An early account of this work was provided in Ref. \cite{grissom:ismrm18}.

### 2020-10-05 Manuscript_r1/Method.tex
further r1 edits

@@
 Figure \ref{fig:Target}a shows the target pattern for all pulse designs which comprised an ellipse centered on the ventricles with AP/HF/LR semi-axes of 4.8/3.2/3.2 cm,
-\textcolor{blue}{with zero phase.}\revbox{R1.X} 
+\textcolor{blue}{with zero phase.}\revbox{R1.1} 
 The pattern was smoothed by a Fermi filter that was applied in the frequency domain to match the target pattern's effective resolution to the excitation k-space trajectory's 5 mm resolution.
@@
 The proposed k-space domain algorithm was implemented based on code for the non-Cartesian GRAPPA method of Ref. \cite{luo2019grappa},
-as a function that takes as input the $B_1^+$ maps, 
-a normalized excitation k-space trajectory, \textcolor{blue}{and optional MATLAB structures of algorithm parameters such as the Tikhonov regularization parameter
-and inclusion and patch widths, and off-resonance parameters such as the off-resonance field map, the time vector and the number of time segments.}\revbox{R1.X} 
+as a function that takes as input the $B_1^+$ maps and a normalized excitation k-space trajectory.
+%, \textcolor{blue}{and optional MATLAB structures of algorithm parameters such as the Tikhonov regularization parameter
+%and inclusion and patch widths, and off-resonance parameters such as the off-resonance field map, the time vector and the number of time segments.}\revbox{R1.X} 
 Within that function the Fourier transforms of the $B_1^+$ products are calculated,
-and a C-based \textcolor{blue}{MATLAB Executable (MEX)}\revbox{R1.X} function is invoked to solve for the non-zero elements of each column of $\bm{W}$,
+and a C-based \textcolor{blue}{MATLAB Executable (MEX)}\revbox{R1.6} function is invoked to solve for the non-zero elements of each column of $\bm{W}$,
 with linear interpolation of the Fourier transforms of the $B_1^+$ map products to obtain the entries of the $\bm{S}^H\bm{S}$ matrices. 
 Those elements are then inserted into a sparse $\bm{W}$ matrix, which is the single output of the main function. 
-Parallelization was implemented across patches within the C-based MEX function using the \textcolor{blue}{Open Multi-Processing (OpenMP)}\revbox{R1.X} library. 
+Parallelization was implemented across patches within the C-based MEX function using the \textcolor{blue}{Open Multi-Processing (OpenMP)}\revbox{R1.6} library. 
 The final pulses are calculated by multiplying the sparse $\bm{W}$ matrix into the Fourier transform of the target pattern. 
@@
 the number of polar and azimuthal rotations were increased and reduced relative to the reference design described above, 
-for reduction factors of 0.5, 2, 3, and 4, 
+for reduction factors of 0.5, 2, and 4, 
 \textcolor{blue}{where the factor 0.5 trajectory comprised X additional segments for approximately 2$\times$-denser sampling of excitation k-space.} \revbox{2.X}

### 2020-10-05 Manuscript_r1/Result.tex
wag did some R2 work
further r1 edits

@@
 excitation error and RMS RF amplitude.
-The dots on the spatial domain and k-space domain curves indicate the knees \textcolor{blue}{of}\revbox{R1.X} the curves corresponding to
+The dots on the spatial domain and k-space domain curves indicate the knees \textcolor{blue}{of}\revbox{R1.9} the curves corresponding to
 the $\lambda$ values used for the designs in Figures \ref{fig:ErrorMap}, \ref{fig:ComputationTime}, \ref{fig:kspace_PTX_Acceleration}, and \ref{fig:kspace_PTX_B0}.
@@
 For each design the k-space domain-designed pulses had higher error, 
-but error increased smoothly with increasing reduction factor, as it did for the spatial domain designs.
+but error increased smoothly with increasing reduction factor, 
+as it did for the spatial domain designs.
 

### 2020-10-05 Manuscript_r1/Theory.tex
further r1 edits

--- 2020-10-02 Manuscript_r1/Theory.tex
@@
 and $\mathcal{F}(\bm{d})$ is a length-$N_s$ vector containing the 
-Fourier transform of the desired k-space excitation pattern $\bm{d}$.
+Fourier transform of the \textcolor{blue}{complex-valued}\revbox{R1.1} target k-space excitation pattern $\bm{d}$.
 $\bm{W}$ has dimensions $N_t  N_c \times N_s$.
@@
 In this work `inclusion width' is defined as the distance, 
-in cycles per excitation field-of-view (cycles/FOV), 
+in \textcolor{blue}{phase cycles over the excitation field-of-view (cycles/FOV), }\revbox{R1.2} 
 from each target location $\vec{k}_j$ within which which all trajectory points are accrued into $\mathbb{N}$.
@@
 \end{equation} 
-where the matrix $\bm{S}_l$ is now formed from the $N_c  L$ Fourier transforms of the $B_1^+$ map and $h_l(\vec{x}_j)$ products.} \revbox{R1.X}  
+where the matrix $\bm{S}_l$ is now formed from the $N_c  L$ Fourier transforms of the $B_1^+$ map and $h_l(\vec{x}_j)$ products.} \revbox{R1.3}  
 Efficient construction of the $\bm{S}^{H}\bm{S}$ matrix follows much the same procedure as without

### 2020-10-05 Manuscript_r1/kPtx_paper.tex
wag did some R2 work
further r1 edits

@@
 {\bf Purpose:}
-To accelerate the design of \textcolor{blue}{(under- or oversampled)}\revbox{R1.X} multidimensional parallel transmission pulses. 
+To accelerate the design of \textcolor{blue}{(under- or oversampled)}\revbox{R1.4} multidimensional parallel transmission pulses. 
 \\[1em]
@@
 A k-space domain parallel transmission pulse design algorithm was proposed that
-produces a sparse matrix relating a \textcolor{blue}{complex-valued}\revbox{R1.X} target excitation pattern to the pulses that produce it, 
+produces a sparse matrix relating a \textcolor{blue}{complex-valued}\revbox{R1.1} target excitation pattern to the pulses that produce it, 
 and can be finely parallelized. 
@@
 
+\bibitem{padormo:2016}
+F.~Padormo, A.~Beqiri, J.~V. Hajnal, and S.~J. Malik.
+\newblock Parallel transmission for ultrahigh-field imaging.
+\newblock {NMR} Biomed 2016; 29(9):1145--1161.
+
+\bibitem{deniz:2019}
+C.~M. Deniz.
+\newblock Parallel transmission for ultrahigh field {MRI}.
+\newblock Top Magn Reson Imaging 2019; 28(3):159--171.
+
 \bibitem{malik2012tailored}
@@
   Fl\"oser M, Oehmigen M, Quick HH, Ladd ME.
-\newblock A 32-channel parallel transmit system add-on for 7t mri.
+\newblock A 32-channel parallel transmit system add-on for {7T MRI}.
 \newblock PLOS ONE 2019;\hspace{0pt}14:1--20.
@@
 \newblock Magn Reson Med 2016;\hspace{0pt}76:1158--1169.
-
-\bibitem{padormo:2016}
-F.~Padormo, A.~Beqiri, J.~V. Hajnal, and S.~J. Malik.
-\newblock Parallel transmission for ultrahigh-field imaging.
-\newblock {NMR} Biomed 2016; 29(9):1145--1161.
-
-\bibitem{deniz:2019}
-C.~M. Deniz.
-\newblock Parallel transmission for ultrahigh field {MRI}.
-\newblock Top Magn Reson Imaging 2019; 28(3):159--171.
 

### 2020-10-05 code/demo_kpTx_SPINS.m
wag merged

@@ -14,7 +14,7 @@ if_kpsce_MLS = false;
 
 ifOffRes = false;
 
-ifOpenMP = false; % IN OpemMP, number of thread has to be change in the .c file and then re-compile
+ifOpenMP = false; % Use openMP to parallelize kpTx computations
 
 ifDoSpatialDesign = true;
 

### 2020-10-09 Manuscript_r1/response_to_reviews.tex
added k-traj figure to code, reduction factor descriptions

@@
 \\[0.2em]
-\indent{\it \textcolor{red}{TODO: Clarify how the trajectory changed between the different $R$ factors. 
-We have updated the numbers in the Introduction to slightly more realistic values. 
-We will report the design times across $R$ factors.}}
+\indent{\it \textcolor{blue}{The pulse design problem we evaluated in this work
+did lead to very long compute times for the spatial domain designs and very large matrix sizes for an explicit pseudoinverse design,
+so we believe the problem does represent a challenging but practical design scenario with which to evaluate the new method. 
+At the same time, we have revised the max number of time points we cite in the Introduction from 10,000 down to 2,500, 
+since even for the finest RF sampling time we know of on a major vendor scanner (4 us on GE), a 2,500 time point pulse is fairly long at 10 ms. 
+We have added description to clarify how the SPINS trajectory was undersampled,
+which was by reducing (or increasing, in the reduction factor 0.5 case) the number of cycles in each of the three trajectory segments.
+We also now list the pulse durations for each reduction factor. 
+To increase the paper's rigor we also added measured design times for the spatial domain method and the new k-space method
+across reduction factors.}}
 \\[1.2em]
@@
 \\[0.2em]
-\indent{\it \textcolor{blue}{We agree that we need to tone down the language here.
+\indent{\it \textcolor{blue}{We agree that we needed to tone down the language here.
 We have revised wording to indicate that nearly all parallel transmission studies have been formulated in the spatial domain, rather than being explicitly derived directly from the spatial domain method.

### 2020-10-09 Manuscript_r1/Introduction.tex
added k-traj figure to code, reduction factor descriptions

@@
 Overall, for a 3D design the spatial domain system matrix can occupy upwards of 120 gigabytes of memory,
-making it infeasible to construct and invert on most modern computers. } \revbox{R2.X}
+making it infeasible to construct and invert on most modern computers. } \revbox{R2.1}
 Explicit matrix storage and inversion can be avoided using non-uniform fast Fourier transforms to evaluate matrix multiplies,

### 2020-10-09 Manuscript_r1/Method.tex
added k-traj figure to code, reduction factor descriptions

@@
 An important application of parallel transmission is the reduction of multidimensional pulse durations by excitation k-space undersampling.
-To compare the spatial domain and k-space domain methods across undersampling factors,
-the number of polar and azimuthal rotations were increased and reduced relative to the reference design described above, 
-for reduction factors of 0.5, 2, and 4, 
-\textcolor{blue}{where the factor 0.5 trajectory comprised X additional segments for approximately 2$\times$-denser sampling of excitation k-space.} \revbox{2.X}
+\textcolor{blue}{To compare the spatial domain and k-space domain methods across undersampling factors,
+the number of polar and azimuthal rotations in each segment of the SPINS trajectory were increased and reduced relative to the reference design described above, 
+by factors of 0.5, 2, and 4. 
+That is, for a reduction factor of 0.5, the number of polar and azimuthal rotations in the trajectory were doubled for each of the three segments,
+and they were halved for a reduction factor of 2.
+This yielded pulse durations of 20.5 ms (reduction factor 0.5), 5.3 ms (reduction factor 2), and 2.6 ms (reduction factor 4).} \revbox{R2.1}
 

### 2020-10-09 code/demo_kpTx_SPINS.m

@@ -77,7 +77,7 @@ end
 [dimb1(1),dimb1(2),dimb1(3),Nc] = size(b1);
 
 %% Design SPINS Trajectory
-k_accelerate=1;
+k_accelerate = 1; % reduction factor
 
 kmax = 0.75/2; % cycles/cm, max k-space loc
 T = 5; % ms, duration of pulse
@@ -93,8 +93,6 @@ kx = kr.*cos(ktheta).*sin(kphi);
 ky = kr.*sin(ktheta).*sin(kphi);
 kz = kr.*cos(kphi);
 k = [kx(:) ky(:)  kz(:) ];
-Nt = size(k,1);
-NN = [Nt 0];
 
 T2=5;
 t2=0:dt:T2-dt;
@@ -109,8 +107,6 @@ ky2 = kr.*sin(ktheta).*sin(kphi);
 kz2 = kr.*cos(kphi);
 k2 = [kx2(:) ky2(:)  kz2(:) ];
 k=cat(1,k2(1:end-1,:),k);
-Nt = size(k,1);
-t = 0:dt:Nt*dt-dt;
 
 T3=5;
 t3=0:dt:T3-dt;
@@ -126,7 +122,6 @@ kz3 = kr.*cos(kphi);
 k3 = [kx3(:) ky3(:)  kz3(:) ];
 k=cat(1,k3(1:end-1,:),k);
 Nt = size(k,1);
-t = 0:dt:Nt*dt-dt;
 
 g=-flip(diff([zeros(1,3);flip(k)],1,1))/(1000*42.58*(dt/1000)/100);%mT/m
 g=g/10; %mT/m to G/cm
@@ -142,6 +137,9 @@ Nt= size(k,1);
 
 NN = [Nt 0];
 
+figure;plot3(k(:, 1), k(:, 2), k(:, 3));
+xlabel 'k_x (1/cm)', ylabel 'k_y (1/cm)', zlabel 'k_z (1/cm)'
+title(sprintf('SPINS Trajectory, R = %d, %0.1f ms', k_accelerate, Nt * dt));
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 d_ori=d;

### 2020-10-10 Manuscript_r1/response_to_reviews.tex
final r1 submission

@@
 Below we have numbered each specific critique and provide our responses.
-For each addition we have made, we have trimmed out other text, and now stand at a word count of \textcolor{red}{X words.} 
-\textcolor{red}{In addition, we have removed the $R = 3$ result from Figure 9 (now Figure 8), to improve readability. 
-We kept the powers-of-two reduction factors.}
+We have trimmed out other text to accommodate requested additions, 
+and now stand at a word count of 5630. 
+In addition, we have removed the $R = 3$ result from Figure 9 (now Figure 8) to improve readability,
+while retaining the powers-of-two reduction factors.
 
@@
 \\[0.2em]
-\indent{\it \textcolor{blue}{Thank you for noticing the inconsistencies in this section; we agree and have revised the section to simplify and clarify it.}}
+\indent{\it \textcolor{blue}{Thank you for noticing the inconsistencies in this section; we agree and have revised the section to simplify and clarify it. It is now also a bit shorter.}}
 \\[1.2em]
@@
 \indent{\it \textcolor{blue}{We used TexShop on the Mac - thanks for finding the doublings! 
-We found and fixed the ``of'' and ``undersampling'' ones but could not locate the ``row'' one.}}
+We found and fixed the ``of'' doubling, 
+and we removed the sentence containing the doubled ``undersampling'' to reduce word count, 
+but we could not locate the ``row'' doubling.}}
 \\[1.2em]
@@
 so we believe the problem does represent a challenging but practical design scenario with which to evaluate the new method. 
-At the same time, we have revised the max number of time points we cite in the Introduction from 10,000 down to 2,500, 
-since even for the finest RF sampling time we know of on a major vendor scanner (4 us on GE), a 2,500 time point pulse is fairly long at 10 ms. 
+At the same time, we appreciate that the paper would be strengthened by adding information about how the k-space method's 
+performance depends on problem size,
+so we now report computation time for spatial and k-space domain designs for each reduction factor in Figure 8. 
+We have also revised the max number of time points we cite in the Introduction from 10,000 down to 2,500, 
+since even for the finest RF sampling time we know of on a major vendor scanner (4 us on GE), 
+a 2,500-time point pulse is fairly long at 10 ms. 
 We have added description to clarify how the SPINS trajectory was undersampled,
 which was by reducing (or increasing, in the reduction factor 0.5 case) the number of cycles in each of the three trajectory segments.
-We also now list the pulse durations for each reduction factor. 
-To increase the paper's rigor we also added measured design times for the spatial domain method and the new k-space method
-across reduction factors.}}
+We also now list the pulse durations for each reduction factor.}}
 \\[1.2em]
@@
 \\[0.2em]
-\indent{\it \textcolor{blue}{We agree that we needed to tone down the language here.
-We have revised wording to indicate that nearly all parallel transmission studies have been formulated in the spatial domain, rather than being explicitly derived directly from the spatial domain method.
+\indent{\it \textcolor{blue}{We agree that we needed to tone down the language here. We have revised wording to indicate that most
+parallel transmission studies have been formulated in the spatial domain, rather than being explicitly derived directly from the spatial domain method.
 We have also added in the Discussion that it is not clear at this time whether or how hard power or SAR constraints could be directly built in to the method,

### 2020-10-10 Manuscript_r1/Introduction.tex
final r1 submission

@@
 In that method, a dense system matrix was constructed by applying a Fourier transform to each transmit coil's $B_1^+$ map,
-forming a 2D convolution matrix for each coil, and then concatenating the coils' convolution matrices.
+forming a convolution matrix for each coil, and then concatenating the coils' convolution matrices.
 The pulses were solved by multiplying the 
@@
 and enables flexible modeling and compensation of effects such as off-resonance, 
-incorporation of regions of interest,
-and the use of non-uniform fast Fourier transforms to accelerate matrix multiplies.
+and incorporation of regions of interest.
 Since its introduction, 
-\textcolor{blue}{nearly all small-tip-angle parallel transmission studies have been formulated in the spatial domain \cite{padormo:2016,deniz:2019}.} \revbox{R2.2}
+\textcolor{blue}{most small-tip-angle parallel transmission studies have been formulated in the spatial domain \cite{padormo:2016,deniz:2019}.} \revbox{R2.2}
 
@@
 Overall, for a 3D design the spatial domain system matrix can occupy upwards of 120 gigabytes of memory,
-making it infeasible to construct and invert on most modern computers. } \revbox{R2.1}
-Explicit matrix storage and inversion can be avoided using non-uniform fast Fourier transforms to evaluate matrix multiplies,
+making it infeasible to construct and invert on most computers.} \revbox{R2.1}
+Explicit matrix storage and inversion can be avoided using non-uniform fast Fourier transforms (NUFFTs) to evaluate matrix multiplies,
 combined with iterative conjugate gradient solvers. 
-In such designs, parallelization can be applied across coils or across time segments in off-resonance-compensated designs,
+In such designs, parallelization can be applied across coils, % or across time segments in off-resonance-compensated designs,
 and GPU-based pulse designs have been described \cite{deng:2011}. 
 However, parallelization cannot be applied across iterations;
-hundreds of iterations are commonly used for 3D designs and thousands of iterations can be required for 
+several tens of iterations are commonly used for 3D designs and thousands of iterations can be required for 
 magnitude least-squares \cite{setsompop2008magnitude} 
 or constrained pulse designs \cite{brunner2010optimal,hoyos:tmi:2014}. 
-Furthermore, non-uniform fast Fourier transforms can require significant computation for the repeated gridding steps; 
-in image reconstruction these can be eliminated since the Gram matrix is Toeplitz and can therefore be multiplied using fast Fourier transforms \cite{fessler2005toeplitz},
-but this does not apply to parallel transmit pulse design since the Gram matrix is not Toeplitz. 
+%Furthermore, NUFFTs can require significant computation for the repeated gridding steps; 
+%in image reconstruction these can be eliminated since the Gram matrix is Toeplitz and can therefore be multiplied using fast Fourier transforms \cite{fessler2005toeplitz},
+%but this does not apply to parallel transmit pulse design since the Gram matrix is not Toeplitz. 
 A further challenge for parallel transmit pulse design is that pulses must be computed for each subject,
@@
 and introduce a patch-wise parallelization that provides control over the size and accuracy of each subproblem. 
-We further accelerate the solution of each subproblem by proposing an efficient method to construct a required
+We describe an efficient method to construct a required
 matrix of $B_1^+$ map inner products while maintaining accuracy. 
 A method to incorporate off-resonance correction is also described. 
-The algorithm was characterized and validated in terms of accuracy (measured by Bloch equation simulations) 
+The algorithm was characterized and validated in terms of excitation error 
 and computation time, with comparisons to spatial domain designs using 
-non-uniform fast Fourier transforms and the conjugate gradient algorithm.
+NUFFTs and the conjugate gradient algorithm.
 The application for the designs was a three-dimensional inner-volume excitation using a simulated 24-channel transmit array
 and a SPINS trajectory \cite{malik2012tailored}.
-The results show how computation time and accuracy depend on the parameters of the patch-wise parallelization,
-and how well the algorithm accommodates \textcolor{blue}{excitation k-space undersampling}\revbox{R1.9} and compensates pulses for off-resonance.
+%The results show how computation time and accuracy depend on the parameters of the patch-wise parallelization,
+%and how well the algorithm accommodates \textcolor{blue}{excitation k-space undersampling}\revbox{R1.9} and compensates pulses for off-resonance.
 An early account of this work was provided in Ref. \cite{grissom:ismrm18}.

### 2020-10-10 Manuscript_r1/Method.tex
final r1 submission

@@
 RF pulses were solved using an iterative least-squares conjugate-gradient descent method with 35 iterations,
-which was accelerated by non-uniform fast Fourier transforms \cite{Fessler:2003fk}. 
+which was accelerated by NUFFTs \cite{Fessler:2003fk}. 
 Except for the off-resonance-compensated designs described below, 
 all spatial domain designs were parallelized using 16 threads that simultaneously computed the forward and backward 
-non-uniform fast Fourier transforms across transmit coils. 
+NUFFTs across transmit coils. 
 The proposed k-space domain algorithm was implemented based on code for the non-Cartesian GRAPPA method of Ref. \cite{luo2019grappa},
@@
 Note that the last case is equivalent to the original k-space domain method of Ref. \cite{Katscher:2003:Magn-Reson-Med:12509830}.
-For each design, flip angle RMSE (calculated using the spatial domain non-uniform fast Fourier transform) and root-mean-square RF amplitude were
+For each design, flip angle RMSE (calculated using the spatial domain NUFFT) and root-mean-square RF amplitude were
 recorded.

### 2020-10-11 code/kpTx.m
add dummy runs for openMP in kpTx.m

@@ -203,6 +203,21 @@ idgrid = single(1./dgrid);
 shSolve=-[kySolve(:) kxSolve(:) kzSolve(:)];
 shSolve=single(shSolve);
 
+% Dummy runs for openMP, so big matrices can be properly passed.
+if  nThreads ~=0
+    shift_c_mex_dummy=cell(1);
+    shift_c_mex_dummy{1}=single([1;1;1]);
+    if ifOffRes
+        kTrajInds_ii_dummy=cell(1);
+        kTrajInds_ii_dummy{1}=single(1);
+        w_coeffs_dummy = kpTx_solve_w_OpenMP(shift_c_mex_dummy, nCoils*Lseg, Tik, ...
+                F_c, idgrid, shSolve', F_c_SensMapOnly, nCoils, BFull_c, ...
+                kTrajInds_ii_dummy, nThreads);
+    end
+    w_coeffs_dummy = kpTx_solve_w_OpenMP(shift_c_mex_dummy, nCoils, Tik, F_c, ...
+            idgrid, shSolve', F_c_SensMapOnly, nThreads);
+end
+
 % In this method, every individual column of W is solved with a same
 % regularizer Tik
 disp 'Solving for columns of W matrix'

### 2020-10-21 Manuscript_r2/Conclusion.tex
wag initialized r2 folder

--- 2020-10-05 Manuscript_r1/Conclusion.tex
@@
 for 3D problems with large grid sizes, 
-requiring both many iterations and considerable computation per iteration. 
+requiring many iterations with considerable computation per iteration. 
 It is anticipated that the proposed k-space domain algorithm will be most useful for these types of large $>$2D problems,
@@
 with a modest tradeoff of excitation error and RMS RF amplitude.
+
+\section*{Acknowledgments}
+The authors would like to thank Tianrui Luo (University of Michigan) for helpful discussions regarding Ref \cite{luo2019grappa}.

### 2020-10-21 Manuscript_r2/Theory.tex
wag initialized r2 folder

--- 2020-10-05 Manuscript_r1/Theory.tex
@@
 Once the entries of $\bm{W}$ are computed, 
-the RF design problem can be instantaneously solved by a sparse matrix multiplication, 
-without a full matrix inversion or an iterative algorithm. 
+the RF design problem can be instantaneously solved by a sparse matrix multiplication. 
+%without a full matrix inversion or an iterative algorithm. 
 Here we describe how to break down the problem of constructing $\bm{W}$ 
@@
 In this case, the vector $\bm{w}_j$ is identical to the desired RF. 
-Therefore, the problem of finding the $j$-th column $\bm{w}_j$ of $\bm{W}$ can be restated as: 
+Therefore, the problem of finding the $j$-th column $\bm{w}_j$ of $\bm{W}$ can be stated as: 
 what should the RF pulse samples be to generate a unit delta function at the location $\vec{k}_j$ in k-space, 
@@
 then there is no reduction in computation compared to a conventional pseudoinverse-based pulse design.
-However, because $B_1^+$ maps are compact in excitation k-space and localized near DC,
+However, because $B_1^+$ maps are localized near $\vec{k} = 0$ in excitation k-space,
 only a small number ($\ll N_t$) of trajectory points near the target location $\vec{k}_j$ can contribute significantly
@@
 but this introduces large errors. 
-Instead, inspired by the rapid GRAPPA calibration method for arbitrary 2D/3D non-Cartesian trajectories of Ref \cite{luo2019grappa}, 
+Instead, inspired by the non-Cartesian GRAPPA method of Ref \cite{luo2019grappa}, 
 we propose to construct the Hermitian $\bm{S}^{H}\bm{S}$ matrix directly via interpolation of the Fourier transforms
@@
 The storage size is also much smaller, 
-and the potentially large matrix multiplication between $\bm{S}^H$ and $\bm{S}$ is avoided.
-An alternative strategy would be to construct $\bm{S}$ by Fourier transforming each channel's $B_1^+$ map 
-and then interpolating it to be centered at each trajectory location, 
-but this again requires multiplication of the $\bm{S}^{H}$ and $\bm{S}$ matrices,
-which further involves the multiplication of interpolated values. 
-We have found empirically that this strategy introduces higher error
-than interpolating the inner product values. 
+and the matrix multiplication between $\bm{S}^H$ and $\bm{S}$ is avoided.
+%An alternative strategy would be to construct $\bm{S}$ by Fourier transforming each channel's $B_1^+$ map 
+%and then interpolating it to be centered at each trajectory location, 
+%but this again requires multiplication of the $\bm{S}^{H}$ and $\bm{S}$ matrices,
+%which further involves the multiplication of interpolated values. 
+%We have found empirically that this strategy introduces higher error
+%than interpolating the inner product values. 
 %Furthermore, to calculate each element of $\bm{S}^{H}\bm{S}$, there are $2N_s$ number of interpolations involved with this sub-optimal strategy.
@@
 but has not been previously implemented in a k-space-domain design.
-Spatial domain designs based on non-uniform fast Fourier transforms make use of an approximate time-segmented
+Spatial domain designs based on NUFFTs make use of an approximate time-segmented
 model for the off-resonance term \cite{fessler2005toeplitz},
 which decouples the space- and time-dependence of off-resonant phase accrual into the product of 
-space- and time-dependent terms, which are applied on either side of the non-uniform fast Fourier transform operator. 
-Here we show that a time-segmented off-resonance model can be incorporated in the proposed k-space-domain algorithm. 
+space- and time-dependent terms, which are applied on either side of the NUFFT operator. 
+Here we show how a time-segmented off-resonance model can be incorporated in the proposed k-space-domain algorithm. 
 Mathematically, the time-segmented model is given by:

### 2020-10-21 Manuscript_r2/kPtx_paper.tex
wag initialized r2 folder

--- 2020-10-05 Manuscript_r1/kPtx_paper.tex
@@
 \par
-Word Count: Approximately 5500 \\
+Word Count: 5630 \\
 *Corresponding author: \\
@@
 
-\bibitem{fessler2005toeplitz}
-Fessler JA, Lee S, Olafsson VT, Shi HR, Noll DC.
-\newblock Toeplitz-based iterative image reconstruction for {MRI} with
-  correction for magnetic field inhomogeneity.
-\newblock IEEE Trans Sig Proc 2005;\hspace{0pt}53:3393--3402.
-
 \bibitem{grissom:ismrm18}
@@
 \newblock Magn Reson Med 2019;\hspace{0pt}82:1101--1112.
+
+\bibitem{fessler2005toeplitz}
+Fessler JA, Lee S, Olafsson VT, Shi HR, Noll DC.
+\newblock Toeplitz-based iterative image reconstruction for {MRI} with
+  correction for magnetic field inhomogeneity.
+\newblock IEEE Trans Sig Proc 2005;\hspace{0pt}53:3393--3402.
 
@@
 
-\section*{Table Captions}
+\section*{Tables}
 
@@
 \centering
-%\begin{tabular}{c | c}
-%Inclusion Width & $\bm{W}$ Matrix Size (GB) \\
-%\hline
-%$\infty$ & 24.4 \\
-%8 & 2.73 \\
-%6 & 1.37 \\
-%4 & 0.53 \\
-%2 & 0.14
-%\end{tabular}
+\begin{tabular}{c | c}
+Inclusion Width & $\bm{W}$ Matrix Size (GB) \\
+\hline
+$\infty$ & 24.4 \\
+8 & 2.73 \\
+6 & 1.37 \\
+4 & 0.53 \\
+2 & 0.14
+\end{tabular}
 \caption{$\bm{W}$ matrix sizes in gigabytes (GB) versus inclusion width in cycles/FOV. 
@@
 	%\includegraphics[width=\textwidth]{ReductionFactor}
-	\caption{Normalized error maps and RMSEs for spatial domain design (first row) and k-space domain design (second row), 
+	\caption{Normalized error maps, RMSEs, and computation times 
+	for spatial domain design (first row) and k-space domain design (second row), 
 	using excitation k-space trajectories with different reduction factors (third row).

### 2020-10-23 Manuscript_r2/Method.tex
update text with dwell 10

--- 2020-10-10 Manuscript_r1/Method.tex
@@
 using the minimum-time gradient waveform design method \cite{lustig2008fast}, 
-for a 15 {\textmu}s dwell time and subject to the scanner's gradient amplitude and slew rate constraints of 200 mT/m and 700 T/m/s, respectively (Figure \ref{fig:Target}c). 
+for a 10 {\textmu}s dwell time and subject to the scanner's gradient amplitude and slew rate constraints of 200 mT/m and 700 T/m/s, respectively (Figure \ref{fig:Target}c). 
 The durations of the three segments after minimum-time gradient design were 4.174, 4.326, and 1.5 ms, respectively.
@@
 With this trajectory and the 64$\times$64$\times$48 design grid size, 
-the dimensions of the $\bm{W}$ matrix were 16,632 RF pulse samples, 
+the dimensions of the $\bm{W}$ matrix were 25,008 RF pulse samples, 
 by 196,608 target k-space locations.
@@
 The patch width was varied while holding the number of threads at 16, and the inclusion width at 4 cycles/FOV,
-and the inclusion width was varied (2, 4, 6, and 8 cycles/FOV) while holding the number of threads at 16, and the patch width at 4 and 8 cycles/FOV. 
+and the inclusion width was varied (2, 4, 6, and 8 cycles/FOV) while holding the number of threads at 16, and the patch width at 4 cycles/FOV. 
 The sizes of the $\bm{W}$ matrices were also recorded, holding patch width constant at 4 cycles/FOV and varying the inclusion width.
@@
 Note that the last case is equivalent to the original k-space domain method of Ref. \cite{Katscher:2003:Magn-Reson-Med:12509830}.
-For each design, flip angle RMSE (calculated using the spatial domain NUFFT) and root-mean-square RF amplitude were
+For each design, flip angle RMSE (calculated using the spatial domain non-uniform discrete Fourier transforms) and root-mean-square RF amplitude were
 recorded.
@@
 and they were halved for a reduction factor of 2.
-This yielded pulse durations of 20.5 ms (reduction factor 0.5), 5.3 ms (reduction factor 2), and 2.6 ms (reduction factor 4).} \revbox{R2.1}
+This yielded pulse durations of 20.7 ms (reduction factor 0.5), 5.2 ms (reduction factor 2), and 2.7 ms (reduction factor 4).} \revbox{R2.1}
 

### 2020-10-23 Manuscript_r2/Result.tex
update text with dwell 10

--- 2020-10-05 Manuscript_r1/Result.tex
@@
 The k-space domain design used patch and inclusion widths of 4.
-The calculated root-mean-squared errors (RMSEs) were 2.42\% (spatial domain) and 2.68\% (k-space domain), 
+The calculated root-mean-squared errors (RMSEs) were 2.13\% (spatial domain) and 2.31\% (k-space domain), 
 respectively. 
@@
 This indicates uniform inner volume excitation while maintaining the outer volume intact. 
-The parallelized k-space domain design required 2.9 seconds computation versus 31.8 seconds for the spatial domain method, a 91\% decrease.
+The parallelized k-space domain design required 6.7 seconds computation versus 30.3 seconds for the spatial domain method, a 78\% decrease.
 
@@
 \par Figure \ref{fig:ComputationTime}c plots mean computation time and RMSE with different inclusion widths. 
-The solid lines and dashed lines were obtained with patch widths of 4 and 8 cycles/FOV, respectively. 
 Computation time increased and error decreased with increasing inclusion width,
@@
 corresponding to an increased $\bm{S}^H\bm{S}$ matrix size. 
-The RMSE was only slightly lower for a patch width of 8 versus 4 cycles/FOV, 
-but the computation time was much higher for 8 cycles/FOV, across all inclusion widths. 
 The knees in the curves occurred approximately at an inclusion width of 4 cycles/FOV,
@@
 With the inclusion width of 4 cycles/FOV used here, 
-the matrix size was 98\% smaller than that of a full solution.
+the matrix size was 99\% smaller than that of a full solution.
 
@@
 which is matched by the k-space domain method when all target locations are solved simultaneously with
-all excitation trajectory points included and exact $\bm{S}^H\bm{S}$ matrix construction (orange curve). 
+all excitation trajectory points included and exact $\bm{S}^H\bm{S}$ matrix construction (solid orange curve). 
 When the inclusion and patch widths are limited to 4 cycles/FOV but the $\bm{S}^H\bm{S}$ 
@@
 because the flip angle errors in Figure \ref{fig:LCurves} were calculated using 
-spatial domain non-uniform fast Fourier transforms instead of Bloch equation simulations, 
+spatial domain non-uniform discrete Fourier transforms instead of Bloch equation simulations, 
 to provide a more direct measure of the design error.
@@
 There is significant Gibbs ringing in the pattern (indicated by the red arrows),
-and the pulses incur a higher RMSE (4.64\%) than pulses designed using either the spatial domain method with a finer 64$\times$64$\times$48 grid
-(2.66\%; Figure \ref{fig:GibbsRing}b) or the k-space domain method with a 32$\times$32$\times$24 grid (3.00\%; Figure \ref{fig:GibbsRing}c). 
+and the pulses incur a higher RMSE (4.90\%) than pulses designed using either the spatial domain method with a finer 64$\times$64$\times$48 grid
+(2.43\%; Figure \ref{fig:GibbsRing}b) or the k-space domain method with a 32$\times$32$\times$24 grid (2.96\%; Figure \ref{fig:GibbsRing}c). 
 Gibbs ringing is not apparent in either the 64$\times$64$\times$48 spatial domain error pattern or the 32$\times$32$\times$24 k-space domain error pattern. 
-The RMS RF amplitudes of the low resolution designs were both 0.005. 
+The RMS RF amplitudes of the low resolution designs were both 0.004. 
 Note that the error of the 64$\times$64$\times$48 spatial domain design is slightly higher than designs presented in other figures
@@
 the Gibbs ringing in the low-resolution spatial domain design was caused by the design's inability to observe and limit the ringing in the low-resolution design grid. 
-From a k-space domain point of view, the Gibbs ringing in 
-Figure \ref{fig:GibbsRing}a was due to implicit circulant end conditions at the edges of excitation k-space in the low-resolution
-spatial domain design,
+From a k-space domain point of view, the Gibbs ringing was due to implicit circulant end conditions at the edges of excitation k-space,
 which led RF samples at one edge of k-space to wrap-around and affect target locations at the opposite edge of k-space. 
@@
 However, even for a low-resolution k-space domain design there is no wrap-around effect in excitation k-space 
-because the trajectory points that are incorporated in the weights solution for each patch of target locations are explicitly specified to be those in the immediate vicinity of 
-the target points, without circulant end conditions. 
+because the trajectory points that are incorporated in solution for each patch are explicitly specified to be those in the immediate vicinity of 
+that patch, without circulant end conditions. 
 %Particularly, for the instance problems whose patches are at the edges of the k-space FOV, the excitation trajectory points at the other ends of the k-space FOV will not be incorporated into the design.
@@
 as it did for the spatial domain designs. 
+\textcolor{blue}{Figure \ref{fig:kspace_PTX_Acceleration} also reports mean computation time for each design.
+The spatial domain times were fairly constant across reduction factors despite the decreasing number of time samples with increasing reduction factor.
+This was because the size of the FFT operations in the NUFFTs 
+depended not on the length of the trajectory but on the size of the target pattern which did not change with reduction factor,
+and the FFT operations dominated the NUFFT computation times relative to the gridding operations. % for these three-dimensional problems,
+Conversely, the k-space domain times did decrease with reduction factor since the number and sizes of the $\bm{S}^H\bm{S}$
+matrices depend on the trajectory length.} \revbox{R2.1}
 

### 2020-10-23 Manuscript_r2/Theory.tex
update text with dwell 10

@@
 in \textcolor{blue}{phase cycles over the excitation field-of-view (cycles/FOV), }\revbox{R1.2} 
-from each target location $\vec{k}_j$ within which which all trajectory points are accrued into $\mathbb{N}$.
+from each target location $\vec{k}_j$ within which all trajectory points are accrued into $\mathbb{N}$.
 This reduced set of trajectory points reduces the column dimension of $\bm{S}$
@@
 and column indices of the sub-matrix.
-These inner products can be calculated by interpolating the Fourier transform of the inner product of 
+These inner products can be calculated by interpolating the Fourier transform of the dot product of 
 channel $i$ and channel $j$'s $B_1^+$ maps. 

### 2020-10-23 Manuscript_r2/kPtx_paper.tex
update text with dwell 10

@@
 on algorithm parameters,
-and it was compared to the spatial domain pulse design method in terms computation time, excitation error,
+and it was compared to the spatial domain pulse design method in terms of computation time, excitation error,
 Gibbs ringing, and ability to compensate off-resonance.
@@
 {\bf Results:}
-The proposed algorithm achieved approximately 90\% faster pulse design compared to 
+The proposed algorithm achieved approximately 80\% faster pulse design compared to 
 an iterative spatial domain method, with the same number of parallel threads,
 with the tradeoff of increased excitation error and RMS RF amplitude. 
-It reduced the memory required to store the design matrix by 98\% compared to a full matrix solution.
+It reduced the memory required to store the design matrix by 99\% compared to a full matrix solution.
 Even with a coarse design grid, the algorithm produced patterns that were free of Gibbs ringing.
@@
 \hline
-$\infty$ & 24.4 \\
-8 & 2.73 \\
-6 & 1.37 \\
-4 & 0.53 \\
-2 & 0.14
+$\infty$ & 78.7 \\
+8 & 4.09 \\
+6 & 2.04 \\
+4 & 0.79 \\
+2 & 0.21
 \end{tabular}
@@
 	RF pulse weight contributions from this point.
-	Inclusion width is defined as the distance from each target location $\vec{k}_j$ within which 
-	which all trajectory points are considered when solving for the $j$-th column of the design ($\bm{W}$) matrix.
+	Inclusion width is defined as the distance from each target location $\vec{k}_j$ within which all trajectory points are considered when solving for the $j$-th column of the design ($\bm{W}$) matrix.
 	(b) Calculation of the $\bm{W}$ matrix can be performed column-by-column for each target location $\vec{k}_j$,
@@
 	(b) Computation time (blue axis) and RMSE (red axis) versus patch width, for an inclusion width of 4 cycles/FOV and 16 threads. 
-	(c) Computation time (blue axis) and RMSE (red axis) versus inclusion width, for patch widths of 4 and 8 cycles/FOV, and 16 threads.}
+	(c) Computation time (blue axis) and RMSE (red axis) versus inclusion width, for patch widths of 4 cycles/FOV, and 16 threads.}
 	\label{fig:ComputationTime}

### 2020-10-23 code/demo_kpTx_SPINS.m
change dt to 10 in code

@@ -81,7 +81,7 @@ k_accelerate = 1; % reduction factor
 
 kmax = 0.75/2; % cycles/cm, max k-space loc
 T = 5; % ms, duration of pulse
-dt = 15e-3;
+dt = 10e-3;
 t = 0:dt:T-dt;
 kr = linspace(kmax,0,length(t));
 u = 2*pi/(T/31);v = 2*pi/(T/17);% for kmax=1.5,dur 10ms

### 2020-10-25 Manuscript_r2/Conclusion.tex
wag finished r2

@@
 and the methods were similarly sensitive to excitation k-space undersampling. 
-\textcolor{blue}{While all the pulse designs in this work used 3D SPINS trajectories,
+While all the pulse designs in this work used 3D SPINS trajectories,
 the method can be applied in any number of dimensions and with any excitation k-space trajectory.
-The MATLAB implementation described can be used for any two- or three-dimensional pulse design without modification.}\revbox{R1.2}
+The MATLAB implementation described can be used for any two- or three-dimensional pulse design without modification.
 
@@
 which include 3D spatial designs \cite{malik2012tailored,davids2016fast} 
-and \textcolor{blue}{2D and 3D spatial-spectral designs \cite{stenger2000three,setsompop2009,Malik:2010aa,yang2010four}
-where full matrix construction and inversion is infeasible due to the problem size, }\revbox{R1.7}
+and 2D and 3D spatial-spectral designs \cite{stenger2000three,setsompop2009,Malik:2010aa,yang2010four}
+where full matrix construction and inversion is infeasible due to the problem size, 
 and an iterative design can require several minutes to solve. 
-\textcolor{blue}{Furthermore, unlike an iterative spatial domain design the proposed algorithm does not need to be repeated if the target pattern changes.
+Furthermore, unlike an iterative spatial domain design the proposed algorithm does not need to be repeated if the target pattern changes.
 This means it could have a considerable computational speed advantage for Gerchberg-Saxton magnitude least-squares pulse designs \cite{setsompop2008magnitude,malik:mrm:2015}
@@
 Such a design method would allow the user to specify only the magnitude of the target pattern, 
-rather than magnitude and phase as was required in this work.}\revbox{R1.1}
+rather than magnitude and phase as was required in this work.
 The method could also be used to initialize spatial-domain designs to reduce the number of iterations required to reach a target cost. 
@@
 or to enforce array compression by projecting the weights into the null space of a compression matrix \cite{cao2016array},
-\textcolor{blue}{among other applications \cite{padormo:2016,deniz:2019}.} \revbox{R1.8}
+among other applications \cite{padormo:2016,deniz:2019}.
 In such designs, it would be beneficial to pre-compute and store the lower triangular elements of the $\bm{S}^H\bm{S}$ matrices
 so they need not be re-computed as the regularization changes over iterations.  
-\textcolor{blue}{Peak power could also be controlled in k-space domain designs using parallel transmission 
-VERSE \cite{Lee:2011:MRM} or the iterative re-VERSEit technique \cite{lee2009tod}.} \revbox{R1.8, R2.2}
-\textcolor{blue}{It is not yet clear whether or how hard constraints on SAR and 
-peak- and integrated-power could be directly incorporated in the k-space method, as in Refs \cite{brunner2010optimal} and \cite{hoyos:tmi:2014}. }\revbox{R1.8, R2.2}
-\textcolor{blue}{It may also be possible to use the k-space domain method to rapidly design large-tip-angle pulses via the direct linear class of large-tip-angle pulses method \cite{Xu:2008aa} or the additive angle method \cite{grissom:mrm:2008};
+Peak power could also be controlled in k-space domain designs using parallel transmission 
+VERSE \cite{Lee:2011:MRM} or the iterative re-VERSEit technique \cite{lee2009tod}.
+It is not yet clear whether or how hard constraints on SAR and 
+peak- and integrated-power could be directly incorporated in the k-space method, as in Refs \cite{brunner2010optimal} and \cite{hoyos:tmi:2014}.
+It may also be possible to use the k-space domain method to rapidly design large-tip-angle pulses via the direct linear class of large-tip-angle pulses method \cite{Xu:2008aa} or the additive angle method \cite{grissom:mrm:2008};
 the latter alternates between small-tip-angle designs that could be solved by the k-space method, 
-and Bloch simulations to update the target pattern.} \revbox{R2.3}
+and Bloch simulations to update the target pattern.
 

### 2020-10-25 Manuscript_r2/Method.tex
wag finished r2

@@
 Figure \ref{fig:Target}a shows the target pattern for all pulse designs which comprised an ellipse centered on the ventricles with AP/HF/LR semi-axes of 4.8/3.2/3.2 cm,
-\textcolor{blue}{with zero phase.}\revbox{R1.1} 
+with zero phase.
 The pattern was smoothed by a Fermi filter that was applied in the frequency domain to match the target pattern's effective resolution to the excitation k-space trajectory's 5 mm resolution.
@@
 using the minimum-time gradient waveform design method \cite{lustig2008fast}, 
-for a 10 {\textmu}s dwell time and subject to the scanner's gradient amplitude and slew rate constraints of 200 mT/m and 700 T/m/s, respectively (Figure \ref{fig:Target}c). 
+for a \textcolor{blue}{10}\revbox{R2.1} {\textmu}s dwell time and subject to the scanner's gradient amplitude and slew rate constraints of 200 mT/m and 700 T/m/s, respectively (Figure \ref{fig:Target}c).
 The durations of the three segments after minimum-time gradient design were 4.174, 4.326, and 1.5 ms, respectively.
@@
 With this trajectory and the 64$\times$64$\times$48 design grid size, 
-the dimensions of the $\bm{W}$ matrix were 25,008 RF pulse samples, 
+the dimensions of the $\bm{W}$ matrix were \textcolor{blue}{25,008}\revbox{R2.1} RF pulse samples, 
 by 196,608 target k-space locations.
@@
 Within that function the Fourier transforms of the $B_1^+$ products are calculated,
-and a C-based \textcolor{blue}{MATLAB Executable (MEX)}\revbox{R1.6} function is invoked to solve for the non-zero elements of each column of $\bm{W}$,
+and a C-based MATLAB Executable (MEX) function is invoked to solve for the non-zero elements of each column of $\bm{W}$,
 with linear interpolation of the Fourier transforms of the $B_1^+$ map products to obtain the entries of the $\bm{S}^H\bm{S}$ matrices. 
 Those elements are then inserted into a sparse $\bm{W}$ matrix, which is the single output of the main function. 
-Parallelization was implemented across patches within the C-based MEX function using the \textcolor{blue}{Open Multi-Processing (OpenMP)}\revbox{R1.6} library. 
+Parallelization was implemented across patches within the C-based MEX function using the Open Multi-Processing (OpenMP) library. 
 The final pulses are calculated by multiplying the sparse $\bm{W}$ matrix into the Fourier transform of the target pattern. 
@@
 and the inclusion width was varied (2, 4, 6, and 8 cycles/FOV) while holding the number of threads at 16, and the patch width at 4 cycles/FOV. 
-The sizes of the $\bm{W}$ matrices were also recorded, holding patch width constant at 4 cycles/FOV and varying the inclusion width.
+The sizes of the $\bm{W}$ matrices were also recorded while holding the patch width constant at 4 cycles/FOV and varying the inclusion width.
 
@@
 and $B_1^+$ map product interpolation when building the $\bm{S}^H\bm{S}$ matrices. 
-Specifically, for each $\lambda$ a design was performed using patch and inclusion widths of four (`Patch/Inclusion Widths = 4')
+Specifically, for each $\lambda$ a design was performed using patch and inclusion widths of 4 cycles/FOV (`Patch/Inclusion Widths = 4')
 with interpolated $B_1^+$ map products (`Interpolated Matrices'),
 patch and inclusion widths covering the entire design grid (`Patch/Inclusion Widths = $\infty$') with interpolated $B_1^+$ map products,
-patch and inclusion widths of four without $B_1^+$ map product interpolation (`Exact Matrices'; 
+patch and inclusion widths of 4 cycles/FOV without $B_1^+$ map product interpolation (`Exact Matrices'; 
 $B_1^+$ maps were phase-modulated to each trajectory location before Fourier transform),
@@
 An important application of parallel transmission is the reduction of multidimensional pulse durations by excitation k-space undersampling.
-\textcolor{blue}{To compare the spatial domain and k-space domain methods across undersampling factors,
+To compare the spatial domain and k-space domain methods across undersampling factors,
 the number of polar and azimuthal rotations in each segment of the SPINS trajectory were increased and reduced relative to the reference design described above, 
@@
 and they were halved for a reduction factor of 2.
-This yielded pulse durations of 20.7 ms (reduction factor 0.5), 5.2 ms (reduction factor 2), and 2.7 ms (reduction factor 4).} \revbox{R2.1}
+This yielded pulse durations of 20.7 ms (reduction factor 0.5), 5.2 ms (reduction factor 2), and 2.7 ms (reduction factor 4).
 
 \subsection*{Off-Resonance}
-To compare the off-resonance-compensated k-space domain designs with off-resonance-compensated spatial domain designs,
-we incorporated a Gaussian ($\sigma = 3$ cm) field map centered above the frontal sinus, 
-which was designed to mimic the characteristic susceptibility-induced $B_0$ inhomogeneity in this part of the human brain. 
-The field maps were than scaled so that the maximum off-resonance reached +200 Hz and +400 Hz.
+To compare off resonance-compensated k-space and spatial domain designs,
+a field map was generated with a Gaussian-shaped ($\sigma = 3$ cm) offset centered above the frontal sinus, 
+which mimicked susceptibility-induced $B_0$ inhomogeneity in this part of the human brain. 
+The field maps were then scaled so that the maximum off-resonance was +200 Hz and +400 Hz.
 A time-segmented approximate off-resonance model was calculated using the method of Ref. \cite{fessler2005toeplitz} with $L = 4$ time segments,
-and this model was used in both spatial domain and k-space domain designs. 
-Both spatial domain and k-space domain designs used 32 parallel threads.
+and this model was used in both spatial and k-space domain designs. 
+Both spatial and k-space domain designs used 32 parallel threads.

### 2020-10-25 Manuscript_r2/Theory.tex
wag finished r2

@@
 and $\mathcal{F}(\bm{d})$ is a length-$N_s$ vector containing the 
-Fourier transform of the \textcolor{blue}{complex-valued}\revbox{R1.1} target k-space excitation pattern $\bm{d}$.
+Fourier transform of the complex-valued target k-space excitation pattern $\bm{d}$.
 $\bm{W}$ has dimensions $N_t  N_c \times N_s$.
@@
 Therefore, the problem of finding the $j$-th column $\bm{w}_j$ of $\bm{W}$ can be stated as: 
-what should the RF pulse samples be to generate a unit delta function at the location $\vec{k}_j$ in k-space, 
+what should the RF pulse samples be to generate a unit delta function at $\vec{k}_j$, 
 and zeros elsewhere? 
@@
 \begin{equation}\label{eq:MatrixForm}
-\bm{Sw}_j=\bm{\delta}_j,
+\bm{Sw}_j=\bm{e}_j,
 \end{equation}
@@
 matrix containing values of $s_c(\vec{k}-\vec{k}_i)$ for all $c$ and $i$,
-and $\bm{\delta}_j$ is a vector containing a one in the entry corresponding to excitation k-space location
+and $\bm{e}_j$ is a vector containing a one in the entry corresponding to excitation k-space location
 $\vec{k}_j$, and zeros in all other entries. 
@@
 In this work `inclusion width' is defined as the distance, 
-in \textcolor{blue}{phase cycles over the excitation field-of-view (cycles/FOV), }\revbox{R1.2} 
+in phase cycles over the excitation field-of-view (cycles/FOV), 
 from each target location $\vec{k}_j$ within which all trajectory points are accrued into $\mathbb{N}$.
@@
 and column indices of the sub-matrix.
-These inner products can be calculated by interpolating the Fourier transform of the dot product of 
+These inner products can be calculated by interpolating the Fourier transform of the product of 
 channel $i$ and channel $j$'s $B_1^+$ maps. 
@@
 Via the multiplication property of the Fourier transform, 
-this convolution in k-space can be calculated from the Fourier transform of the dot product of the two spatial domain $B_1^+$ maps. 
+this convolution in k-space can be calculated from the Fourier transform of the product of the two spatial domain $B_1^+$ maps. 
 For further details, please refer to Ref. \cite{luo2019grappa}.
@@
 
-\par Since $\bm{S}^{H}\bm{S}$ and its sub-matrices are Hermitian, 
+\par Since $\bm{S}^{H}\bm{S}$ is Hermitian, 
 we only need to find the values within the lower triangle of the matrix, 
-which are the sub-matrices $\bm{S}_i^{H}\bm{S}_j$ with $i>j$ that are themselves lower triangular. 
+which are the sub-matrices $\bm{S}_i^{H}\bm{S}_j$ with $i>j$. % that are themselves lower triangular. 
 The elements of a given sub-matrix $\bm{S}_i^{H}\bm{S}_j$ 
-are interpolated from a densely sampled Fourier transform of the dot product of the spatial domain $B_1^+$ maps of the $i$-th and $j$-th channels. 
+are interpolated from a densely sampled Fourier transform of the product of the spatial domain $B_1^+$ maps of the $i$-th and $j$-th channels. 
 The $(m,n)$-th element is the value interpolated at a position $\vec{k}_m-\vec{k}_n$ away from DC,
@@
 Mathematically, the time-segmented model is given by:
-\textcolor{blue}{
 \begin{equation}
@@
 \begin{equation}
-	\sum_{l=1}^L \bm{S}_l \textrm{diag}(b_{l}(t_i)) \bm{w}_j = \bm{\delta}_j,
+	\sum_{l=1}^L \bm{S}_l \textrm{diag}(b_{l}(t_i)) \bm{w}_j = \bm{e}_j,
 \end{equation} 
-where the matrix $\bm{S}_l$ is now formed from the $N_c  L$ Fourier transforms of the $B_1^+$ map and $h_l(\vec{x}_j)$ products.} \revbox{R1.3}  
+where the matrix $\bm{S}_l$ is now formed from the $N_c  L$ Fourier transforms of the $B_1^+$ map and $h_l(\vec{x}_j)$ products.  
 Efficient construction of the $\bm{S}^{H}\bm{S}$ matrix follows much the same procedure as without

### 2020-10-25 Manuscript_r2/kPtx_paper.tex
wag finished r2

@@
 \newif\ifmarkedup
-\markeduptrue
+%\markeduptrue
 
@@
 {\bf Purpose:}
-To accelerate the design of \textcolor{blue}{(under- or oversampled)}\revbox{R1.4} multidimensional parallel transmission pulses. 
+To accelerate the design of (under- or oversampled) multidimensional parallel transmission pulses. 
 \\[1em]
@@
 A k-space domain parallel transmission pulse design algorithm was proposed that
-produces a sparse matrix relating a \textcolor{blue}{complex-valued}\revbox{R1.1} target excitation pattern to the pulses that produce it, 
+produces a sparse matrix relating a complex-valued target excitation pattern to the pulses that produce it, 
 and can be finely parallelized. 
@@
 on algorithm parameters,
-and it was compared to the spatial domain pulse design method in terms of computation time, excitation error,
+and it was compared to an iterative spatial domain pulse design method in terms of computation time, excitation error,
 Gibbs ringing, and ability to compensate off-resonance.
@@
 The proposed algorithm achieved approximately 80\% faster pulse design compared to 
-an iterative spatial domain method, with the same number of parallel threads,
+the spatial domain method with the same number of parallel threads,
 with the tradeoff of increased excitation error and RMS RF amplitude. 
@@
 	or patches of target points can be solved for jointly. 
-	Here the 16 columns of $\bm{W}$ for a 4 $\times$ 4 patch of target points are solved together,
-	and an inclusion width of 4 cycles/FOV dictates that all trajectory points within a 12 $\times$ 12 region
+	Here the 16 columns of $\bm{W}$ for a 4 $\times$ 4 (cycles/FOV)$^2$ patch of target points are solved together,
+	and an inclusion width of 4 cycles/FOV dictates that all trajectory points within a 12 $\times$ 12 (cycles/FOV)$^2$ region
 	centered on the patch are considered in the calculation.}
@@
 	(b) Computation time (blue axis) and RMSE (red axis) versus patch width, for an inclusion width of 4 cycles/FOV and 16 threads. 
-	(c) Computation time (blue axis) and RMSE (red axis) versus inclusion width, for patch widths of 4 cycles/FOV, and 16 threads.}
+	(c) Computation time (blue axis) and RMSE (red axis) versus inclusion width, for a patch width of 4 cycles/FOV, and 16 threads.}
 	\label{fig:ComputationTime}
@@
 	repeated across five orders of magnitude of the methods' Tikhonov regularization parameters.
-	The k-space domain designs were repeated using patch and inclusion widths of four versus solving for the entire domain at once (`Patch / Inclusion Widths = 4' versus `Patch / Inclusion Widths = $\infty$'),
+	The k-space domain designs were repeated using patch and inclusion widths of 4 cycles/FOV versus solving for the entire domain at once (`Patch / Inclusion Widths = 4' versus `Patch / Inclusion Widths = $\infty$'),
 	and using $B_1^+$ map product interpolation versus phase modulation to each trajectory location (`Interpolated Matrices' versus

### 2020-10-25 manuscript/Manuscript_r2/response_to_reviews.tex
wag moved manuscripts into one folder

--- 2020-10-05 Manuscript_r1/response_to_reviews.tex
@@
 Below we have numbered each specific critique and provide our responses.
-For each addition we have made, we have trimmed out other text, and now stand at a word count of \textcolor{red}{X words.} 
-\textcolor{red}{In addition, we have removed the $R = 3$ result from Figure 9 (now Figure 8), to improve readability. 
-We kept the powers-of-two reduction factors.}
+Most importantly, we have re-designed our excitation k-space trajectories with a 10 us dwell time, 
+and have repeated all computations with this dwell time and the resulting larger problem size.
 
@@
 %\\[1.2em]
-\mysubsectionstar{Referee 1}
-{\bf R1.1:} Please clarify from the beginning that your method is designed for a complex target pattern, i.e., specifying magnitude and phase and not only magnitude as in e.g.
-[13].
-As you are certainly aware, this feature has severe consequences for the method.
-Thus also the phase pattern in the simulation setup has to be specified (page 10, I assume phase demand is simply constant).
-Some sentences in the discussion how you would extend your method to magnitude-only patterns would also be appreciated.
+
+\mysubsectionstar{Referee 2}
+{\bf R2.1:} Dwell Times.
 \\[0.2em]
-\indent{\it \textcolor{blue}{We have added statements throughout the manuscript to clarify that the target pattern is complex-valued,
-and that the target phase we used in our simulated designs was zero.
-We also added discussion that to achieve a magnitude-least-squares design with the k-space method, 
-it could be used in a Gerchberg-Saxton-like magnitude-least-squares algorithm,
-where it would have the advantage (compared to an iterative spatial domain design) that the matrix $\bm{W}$ 
-would not need to be recomputed as the target pattern changes over iterations.}}
+\indent{\it \textcolor{blue}{We agree that while it does not change the interpretation of our results or conclusions,
+it would be best to perform the simulations with an actual vendor dwell time. 
+We chose 10 microseconds since the scanner targeted for these pulses is a Siemens 7T.
+All figures, error numbers and compute times have been updated with the 10 microsecond results.}}
 \\[1.2em]
 
-\noindent{\bf R1.2:} It is not directly clear how far your method is specific for the chosen SPINS trajectory (e.g.
-by defining the inclusion width as cycles/FOV).
-Please discuss how far your method is applicable to arbitrary trajectories, or how the method needs to be adapted if other trajectories are used.
+\noindent {\bf R2.2:} Figure 9 your design time is now 17 seconds with B0 compensation. Please be clear which pulse duration this for.
 \\[0.2em]
-\indent{\it \textcolor{blue}{The algorithm makes no assumptions about the specific trajectory used, 
-and we have clarified this in the Discussion.
-The code we provide should work for any 2D or 3D trajectory, and could be extended to any number of dimensions. 
-We have also clarified in the Theory section that by `cycles/FOV' we mean phase cycles over the excitation FOV;
-this is a general measure that is not specific to the SPINS trajectory.}}
+\indent{\it \textcolor{blue}{This design was with the full 10 millisecond-long trajectory, 
+which was stated in the Methods: `With the exception of the simulations across undersampling factors, 
+all pulse designs used this 10 ms trajectory.'}}
 \\[1.2em]
 
-\noindent{\bf R1.3:} Description of off-resonance compensation seems to be slightly less diligent as rest of theory.
-(a) Equation 7 contains $g_l$ (one index) but you define $g_{il}$ (two indices), then $g_l$ is used again in Eq 8 and $g_{il}$ in Eq 9, (b) the definition of $g_l$ is based on $b_l$ but I do not find definition of $b_l$, (c) shortly after you introduce $h_{lj}$, but $h_{lj}$ seems to be never used.
+\noindent {\bf R2.3:} I would have preferred citations to the wider community, for a broader embrace, rather than more self-citations and more citations to groups already cited.
+I understand that you have a word limit, but I would suggest some of the citations could be added with just a citation trailing behind other like ``...
+constrained pulse designs [20, 21, X, X ,X].'' or similar sentences.
 \\[0.2em]
-\indent{\it \textcolor{blue}{Thank you for noticing the inconsistencies in this section; we agree and have revised the section to simplify and clarify it.}}
-\\[1.2em]
-
-\noindent{\bf R1.4:} Abstract, purpose: To underline that this paper is about acceleration of design of RF pulses and not about acceleration of RF pulses itself (which might be intuitively expected by some readers) I suggest to add a bracket like this: „To accelerate the design of (under- or oversampled) multidimensional parallel transmission pulses“
-\\[0.2em]
-\indent{\it \textcolor{blue}{We agree and have made this addition.}}
-\\[1.2em]
-
-\noindent{\bf R1.5:} page 11, row 32: „optional structures of algorithm and off-resonance parameters“: please be more specific or skip this remark
-\\[0.2em]
-\indent{\it \textcolor{blue}{We have skipped this remark to save word count.}}
-\\[1.2em]
-
-\noindent{\bf R1.6:} page 11, „MEX“ and „OpenMP“: the editor might decide if these terms need some explanation, or can be taken as known
-\\[0.2em]
-\indent{\it \textcolor{blue}{We have defined each of these acronyms.}}
-\\[1.2em]
-
-\noindent{\bf R1.7:} page 19, referencing spatial-spectral designs, please add corresponding studies using parallel transmission: Setsompop K MRM 2009 and Malik S MRM 2010
-\\[0.2em]
-\indent{\it \textcolor{blue}{We have added those citations, in both the Conclusion and Introduction.}}
-\\[1.2em]
-
-\noindent{\bf R1.8:} page 19, rows 25-30: there are numerous studies on various types of power regularization for parallel transmission (e.g.
-Hamburg/Graesslin, London/Malik, Zurich/Brunner, Paris/Boulant).
-You might reference some of these, or reference at least a review paper on this topic like Padormo F NBM 2016, Deniz CM TMRI 2020 etc.
-\\[0.2em]
-\indent{\it \textcolor{blue}{We apologize; there were some references we intended to include there but missed in the initial submission.
-In response to this and R2.2 and R2.3, we have added citations to the two review articles you mention, and also explicitly state that it is unclear at this time how and
-whether hard constraints could be built in to the method.}}
-\\[1.2em]
-
-\noindent{\bf R1.9:} More privately, I am curious which text editor you use, which obviously removed all typos (I did not find a single typo) but does not seem to be able to show doublings:
-- page 6, row 48: double "row"
-- page 16, row 30: double "of"
-- page 5, row 12: double "undersampling"
-\\[0.2em]
-\indent{\it \textcolor{blue}{We used TexShop on the Mac - thanks for finding the doublings! 
-We found and fixed the ``of'' and ``undersampling'' ones but could not locate the ``row'' one.}}
-\\[1.2em]
-
-\mysubsectionstar{Referee 2}
-{\bf R2.1:} The weakest point of the manuscript in my opinion is that the single test case (target region-wise) and the underlying 10 ms trajectory (the longest (?), non-accelerated one) is rather benign for the claimed problem they are seeking to solve.
-
-For example they claim 3D pTx pulse design may use from 1,000 to 10,000 time points (per channel), for 8 to 32 channels, and up to 250,000 spatial points.
-These values, they claim need a lot of memory.
-
-They have a dwell time of 15 µs and thus 666 time samples per channel.
-They study a setup with 24 channels.
-They consider 196,000 spatial points.
-
-Channel-wise it is fair they consider 24 channels that match their array, but otherwise all three circumstances they investigate are lower than the initial problem they claim exist.
-
-They do produce a rather good compression of the design problem by the new method.
-I wonder why they don't stress test it better, going towards the troublesome criteria and beyond.
-What results would they obtain if they reached the claimed limits?
-How far can they go?
-
-Their stress tests demonstrate finely the methods application towards the off-resonance handling, pulse acceleration, RF power regularization and RMSE of excitation patterns etc.
-
-For a completely numerical paper however, I believe the stress testing should target not only what they have done, but also going to the extreme -- if they claim it is a problem they can solve....
-Otherwise they should reduce their claim and state they can fix the problem partly by this proposed method.
-
-For example, how does the proposed method handle the problem at the point, where the spatial domain method becomes infeasible.
-
-I'm sure lots of pulse design will use the algorithm for other target regions (more detailed ones requiring higher resolution).
-
-I couldn't quite find out what the 0.5-undersampling reduction factor meant in terms of pulse duration.
-If it translates to 666*2 time samples then again we are not near the 10,000 samples still.
-But maybe this should be described in more detail...
-\\[0.2em]
-\indent{\it \textcolor{red}{TODO: Clarify how the trajectory changed between the different $R$ factors. 
-We have updated the numbers in the Introduction to slightly more realistic values. 
-We will report the design times across $R$ factors.}}
-\\[1.2em]
-
-\noindent {\bf R2.2:} It is somewhat weakening that they only compare their method to another one of their methods, since a lot has been done since 2006.
-
-p3 l 32: "...nearly all parallel transmission studies have used the spatial domain method":
-
-For sure a lot of pTx designs use the spatial domain method of Grissom.
-
-But stating "nearly all" is somewhat a guess and should be backed up by numbers. What do you mean by nearly all? It must be quite provoking for those who use another one to be diminished.
-
-We can agree that most pTx design function in the spatial domain, but to state that they are also based on the method of Grissom should be backed up.
-
-As discussed below, another reason to include mentions of even more pulse designs is that they tackle problems the proposed method does not.
-Similar to Hoyos-Idrobos [15] and Brunners [14] please discuss how the proposed method will handle if at all possible hard constraints.
-Is it possible?
-
-I can only imagine that local SAR constraints will be quite comfortable to have with 24 channels.
-It is good that achieving the target profile is now faster with the proposed method, but how will the k-space domain method( and the spatial domain method for matter), handle local SAR?
-If you have 24 amplifiers tied together, are you all set to just rely on pulse (adaptive) regularisation or would you really desire to have hard peak and even average power constraints?
-
-One can accept to only witness a comparison to the 2006 method, if the limitations of that and the proposed method are clearly labelled.
-
-Yes, other methods might be much slower, but they handle problems you don't.
-\\[0.2em]
-\indent{\it \textcolor{blue}{We agree that we need to tone down the language here.
-We have revised wording to indicate that nearly all parallel transmission studies have been formulated in the spatial domain, rather than being explicitly derived directly from the spatial domain method.
-We have also added in the Discussion that it is not clear at this time whether or how hard power or SAR constraints could be directly built in to the method,
-though the method would be compatible with parallel transmit VERSE methods.}}
-\\[1.2em]
-
-\noindent {\bf R2.3:} As a new pulse design method, I think the introduction should include a much broader review of other pulse designs existing already.
-Otherwise it paints a false picture of what has happened in the period where Grissom introduced the method they are comparing to.
-
-It is also an overall narrow scope they used for review. The latest pulse design method papers referenced are from 2016, and their own ISMRM abstract from 2018.
-
-New pulse design methods have appeared in more recent years.
-Within, all the years from 2006 to now, there are several pulse designs demonstrated for other applications than 3D pTx, but have features that translate readily to a 3D application.
-The Grissom-2006 method did not include a 3D pTx application.
-Hence, the sought-for referencing can also include pulse design with other applications and with design features that solves problems that the proposed method does not solve, even if it was not for 3D pTx.
-\\[0.2em]
-\indent{\it \textcolor{blue}{While we are above our word count and cannot add a broad overview of different parallel transmit pulse design methods
-to the Introduction,
-we have added 10 more citations to the work including two review articles on parallel transmission (Deniz 2019 and Padormo 2015).
-We also added brief Discussion on possible extensions of the method for large-tip-angle and VERSE parallel transmit pulse designs.}}
+\indent{\it \textcolor{blue}{We have reviewed each category of citations in the manuscript
+and we respectfully disagree that more are required.
+Out of the manuscript's 32 citations, 
+25 are on different pulse design methods and two are review articles that cite yet more.
+We are happy to add specific citations if the referee has some in mind.}}
 \\[1.2em]

### 2020-10-25 manuscript/Manuscript_r0/Theory.tex
wag moved manuscripts into one folder

--- 2020-08-31 Manuscript/Theory.tex
@@
 %and describe an efficient method to construct the $\bm{S}^{H}\bm{S}$ matrices.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{kspace_PTX_Patch}
-	\caption{(a) A target point $\vec{k}_j$ and the nearby trajectory points that are included when calculating 
-	RF pulse weight contributions from this point.
-	Inclusion width is defined as the distance from each target location $\vec{k}_j$ within which 
-	which all trajectory points are considered when solving for the $j$-th column of the design ($\bm{W}$) matrix.
-	(b) Calculation of the $\bm{W}$ matrix can be performed column-by-column for each target location $\vec{k}_j$,
-	or patches of target points can be solved for jointly. 
-	Here the 16 columns of $\bm{W}$ for a 4 $\times$ 4 patch of target points are solved together,
-	and an inclusion width of 4 cycles/FOV dictates that all trajectory points within a 12 $\times$ 12 region
-	centered on the patch are considered in the calculation.}
-	\label{fig:Patch}
-\end{figure}
 

### 2020-10-25 manuscript/Manuscript_r1/Result.tex
wag moved manuscripts into one folder

--- 2020-10-05 Manuscript_r1/Result.tex
@@
 because the flip angle errors in Figure \ref{fig:LCurves} were calculated using 
-spatial domain non-uniform fast Fourier transforms instead of Bloch equation simulations, 
+spatial domain NUFFTs instead of Bloch equation simulations, 
 to provide a more direct measure of the design error.

### 2020-10-25 manuscript/Manuscript_r1/coverletter/coverletter.tex
wag moved manuscripts into one folder

--- 2020-10-01 Manuscript_r1/coverletter/coverletter.tex
@@
 \Letter~\href{mailto:will.grissom@vanderbilt.edu}{will.grissom@vanderbilt.edu}\\[2em]
+{\bfseries Dr. Nicolas Boulant}\\[.35ex]
+\small{\itshape
+Deputy Editor\\
+Magnetic Resonance in Medicine\\[1em]}
+
 {\bfseries Prof. Peter Jezzard}\\[.35ex]
@@
 Magnetic Resonance in Medicine\\[1em]}
+
 %\end{minipage}
@@
 \raggedright
-Dear Dr. Jezzard,\\[1.5em]
+Dear Drs. Boulant and Jezzard,\\[1.5em]
 %
-I would like to submit the manuscript `k-Space Domain Parallel Transmit Pulse Design' to be considered
+I would like to submit the revised manuscript `k-Space Domain Parallel Transmit Pulse Design' to be considered
 for publication as a Full Paper in Magnetic Resonance in Medicine. 
@@
 for ultra-high field MRI. 
+In this first revision we have addressed each of the referee's concerns through additions and clarifications to the text, 
+while removing other text to stay close to our original word count.
 

### 2020-10-25 manuscript/Manuscript_r2/Introduction.tex
wag moved manuscripts into one folder

--- 2020-10-10 Manuscript_r1/Introduction.tex
@@
 excitation k-space domain \cite{Katscher:2003:Magn-Reson-Med:12509830}.
-In that method, a dense system matrix was constructed by applying a Fourier transform to each transmit coil's $B_1^+$ map,
+In that method, a dense system matrix is constructed by applying a Fourier transform to each transmit coil's $B_1^+$ map,
 forming a convolution matrix for each coil, and then concatenating the coils' convolution matrices.
-The pulses were solved by multiplying the 
+The pulses are solved by multiplying the 
 regularized pseudoinverse of the system matrix into the target excitation pattern's Fourier transform. 
@@
 Since its introduction, 
-\textcolor{blue}{most small-tip-angle parallel transmission studies have been formulated in the spatial domain \cite{padormo:2016,deniz:2019}.} \revbox{R2.2}
+most small-tip-angle parallel transmission studies have been formulated in the spatial domain \cite{padormo:2016,deniz:2019}.
 
@@
 $N_c$ is the number of transmit channels, and $N_t$ is the number of time points in the pulse.
-\textcolor{blue}{Typical values for $N_s$ range from 1,000 for 2D designs to 250,000 for 3D designs,
+Typical values for $N_s$ range from 1,000 for 2D designs to 250,000 for 3D designs,
 the number of coils varies from 8 to 32 on ultra-high field scanners,
@@
 Overall, for a 3D design the spatial domain system matrix can occupy upwards of 120 gigabytes of memory,
-making it infeasible to construct and invert on most computers.} \revbox{R2.1}
+making it infeasible to construct and invert on most computers.
 Explicit matrix storage and inversion can be avoided using non-uniform fast Fourier transforms (NUFFTs) to evaluate matrix multiplies,
@@
 In such designs, parallelization can be applied across coils, % or across time segments in off-resonance-compensated designs,
-and GPU-based pulse designs have been described \cite{deng:2011}. 
+and graphics processing unit (GPU)-based pulse designs have been described \cite{deng:2011}. 
 However, parallelization cannot be applied across iterations;
@@
 %but this does not apply to parallel transmit pulse design since the Gram matrix is not Toeplitz. 
-A further challenge for parallel transmit pulse design is that pulses must be computed for each subject,
+A further challenge for parallel transmit pulse design is that pulses usually must be computed for each subject,
 as a pre-scan stage while the subject lies in the scanner.
@@
 \par Here we describe a single-step (non-iterative) small-tip-angle excitation k-space-domain 
-pulse design algorithm with low memory requirements, 
+pulse design algorithm with low memory requirements 
 that can be applied to large pulse design problems with fine parallelization. 
 The algorithm produces a sparse k-space-domain pseudoinverse pulse design matrix 
-that directly relates the Fourier transform \textcolor{blue}{of a complex-valued}\revbox{R1.1} target excitation pattern to the RF pulses that produce it.
+that directly relates the Fourier transform of a complex-valued target excitation pattern to the RF pulses that produce it.
 Once the matrix is built, 

### 2020-10-25 manuscript/Manuscript_r2/Result.tex
wag moved manuscripts into one folder

--- 2020-10-23 Manuscript_r2/Result.tex
@@
 
-Figure \ref{fig:ErrorMap} shows simulated excitation patterns and error maps for the reference spatial and k-space domain designs. 
+Figure \ref{fig:ErrorMap} shows simulated excitation patterns and error maps for the spatial and k-space domain designs. 
 Both designs were performed with 16 parallel threads and the 64$\times$64$\times$48 grid size (3 mm isotropic resolution), 
 and the excitation patterns were evaluated against the target pattern on a 128$\times$128$\times$96 grid size (1.5 mm iso-resolution). 
-The k-space domain design used patch and inclusion widths of 4.
-The calculated root-mean-squared errors (RMSEs) were 2.13\% (spatial domain) and 2.31\% (k-space domain), 
+The k-space domain design used patch and inclusion widths of 4 cycles/FOV.
+The calculated root-mean-squared errors (RMSEs) were \textcolor{blue}{2.13\% (spatial domain) and 2.31\% (k-space domain)}\revbox{R2.1}, 
 respectively. 
@@
 This indicates uniform inner volume excitation while maintaining the outer volume intact. 
-The parallelized k-space domain design required 6.7 seconds computation versus 30.3 seconds for the spatial domain method, a 78\% decrease.
+The parallelized k-space domain design required \textcolor{blue}{6.7 seconds computation versus 30.3 seconds for the spatial domain method, a 78\% decrease.}\revbox{R2.1}
 
@@
 With the inclusion width of 4 cycles/FOV used here, 
-the matrix size was 99\% smaller than that of a full solution.
+the matrix size was \textcolor{blue}{99\%}\revbox{R2.1} smaller than that of a full solution.
 
@@
 excitation error and RMS RF amplitude.
-The dots on the spatial domain and k-space domain curves indicate the knees \textcolor{blue}{of}\revbox{R1.9} the curves corresponding to
-the $\lambda$ values used for the designs in Figures \ref{fig:ErrorMap}, \ref{fig:ComputationTime}, \ref{fig:kspace_PTX_Acceleration}, and \ref{fig:kspace_PTX_B0}.
+The dots on the spatial domain and k-space domain curves indicate the knees of the curves corresponding to
+the $\lambda$ values used for the designs in Figures \ref{fig:ErrorMap}, 
+\ref{fig:ComputationTime}, \ref{fig:kspace_PTX_Acceleration}, and \ref{fig:kspace_PTX_B0}.
 Note that the RMSE's in Figure \ref{fig:LCurves} are slightly lower for the spatial domain designs
@@
 Figure \ref{fig:GibbsRing}a shows slices of the excitation error pattern produced by pulses designed by the spatial domain method
-on a 32$\times$32$\times$24 grid, which were Bloch-simulated on the original 128$\times$128$\times$96 grid. 
+on a 32$\times$32$\times$24 grid, 
+which were Bloch-simulated on the original 128$\times$128$\times$96 grid. 
 There is significant Gibbs ringing in the pattern (indicated by the red arrows),
-and the pulses incur a higher RMSE (4.90\%) than pulses designed using either the spatial domain method with a finer 64$\times$64$\times$48 grid
-(2.43\%; Figure \ref{fig:GibbsRing}b) or the k-space domain method with a 32$\times$32$\times$24 grid (2.96\%; Figure \ref{fig:GibbsRing}c). 
+and the pulses incur a higher RMSE \textcolor{blue}{(4.90\%)}\revbox{R2.1} than pulses designed using either the spatial domain method with a finer 64$\times$64$\times$48 grid
+(\textcolor{blue}{2.43\%}\revbox{R2.1}; Figure \ref{fig:GibbsRing}b) or the k-space domain method with a 32$\times$32$\times$24 grid (\textcolor{blue}{2.96\%}\revbox{R2.1}; Figure \ref{fig:GibbsRing}c).
 Gibbs ringing is not apparent in either the 64$\times$64$\times$48 spatial domain error pattern or the 32$\times$32$\times$24 k-space domain error pattern. 
-The RMS RF amplitudes of the low resolution designs were both 0.004. 
+The RMS RF amplitudes of the low resolution designs were both \textcolor{blue}{0.004.}\revbox{R2.1} 
 Note that the error of the 64$\times$64$\times$48 spatial domain design is slightly higher than designs presented in other figures
@@
 as it did for the spatial domain designs. 
-\textcolor{blue}{Figure \ref{fig:kspace_PTX_Acceleration} also reports mean computation time for each design.
+Figure \ref{fig:kspace_PTX_Acceleration} also reports mean computation time for each design.
 The spatial domain times were fairly constant across reduction factors despite the decreasing number of time samples with increasing reduction factor.
@@
 Conversely, the k-space domain times did decrease with reduction factor since the number and sizes of the $\bm{S}^H\bm{S}$
-matrices depend on the trajectory length.} \revbox{R2.1}
+matrices depend on the trajectory length.
 

### 2020-10-25 manuscript/Manuscript_r2/coverletter/coverletter.tex
wag moved manuscripts into one folder

--- 2020-10-25 manuscript/Manuscript_r1/coverletter/coverletter.tex
@@
 for ultra-high field MRI. 
-In this first revision we have addressed each of the referee's concerns through additions and clarifications to the text, 
-while removing other text to stay close to our original word count.
+In this second revision we have repeated all designs using a 10 microsecond RF and gradient dwell time,
+to address Referee 2's remaining critique.
 
